### 2020-10-08 appendix/appendix.tex
first commit

\documentclass[a4paper, reqno, 12pt]{article}

% Packages
\usepackage[brazilian,english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[super]{nth}
\usepackage{color, graphics, graphicx, amsmath, times, amsfonts, amssymb}
\usepackage{listings,  palatino, fancyhdr, setspace, bbm, type1cm, titletoc, dsfont}
\usepackage{amsthm, underscore, lscape, dcolumn, arydshln}
\usepackage[usenames,svgnames,dvipsnames]{xcolor}
\usepackage[sharp]{easylist}
\usepackage[a4paper,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage[font=small,format=plain,labelfont=bf,up,textfont=it,up]{caption}
\usepackage[pdftex,plainpages=false,pdfpagelabels,pagebackref = false,colorlinks=true,citecolor=DarkBlue,linkcolor=NavyBlue,urlcolor=DarkRed,filecolor=DarkBlue,bookmarksopen=true]{hyperref}
\usepackage{tabularx}
\usepackage[para,online,flushleft]{threeparttable}  
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{natbib}
\usepackage{subcaption, rotating}
\usepackage{pgf, tikz, pgfplots, mathrsfs}

\usetikzlibrary{positioning,arrows,calc,fit}

\pgfplotsset{compat=newest}

\definecolor{wrwrwr}{rgb}{0.38,0.38,0.38}
\definecolor{rvwvcq}{rgb}{0.08,0.38,0.75}

\tikzset{
block/.style={
  draw, 
  rectangle, 
  minimum height=1.5cm, 
  minimum width=3cm, align=center
  }, 
line/.style={->,>=latex'}
}

\tikzset{container/.style={draw, rectangle, dashed, inner sep=1.5em}}

\bibpunct{(}{)}{;}{a}{}{,}

\pagestyle{plain}
\renewcommand{\arraystretch}{1.2}
\sloppy

%\renewcommand{\thepage}{}
\renewcommand{\bibname}{References}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand{\wh}[1] {\widehat { #1 }}

\newcommand{\twopd}[4]{\left\{\begin{array}{ll} #1 & \text{if } #2 \\ #3 & \text{if } #4 \end{array} \right.}

\newcommand{\twopdo}[3]{\left\{\begin{array}{ll} #1 & \text{if } #2 \\ #3 & \text{otherwise} \end{array} \right.}

\newcommand{\threepd}[6]{ \left\{ \begin{array}{lll} #1 & \text{if } #2 \\ 
#3 & \text{if } #4 \\ #5 & \text{if } #6 \end{array} \right.}

\newcommand{\threepdo}[5]{ \left\{ \begin{array}{lll} #1 & \text{if } #2 \\ 
#3 & \text{if } #4 \\ #5 & \text{otherwise} \end{array} \right.}

% Bold letters
\newcommand{\X}{\mathbf{X}}
\newcommand{\Y}{\mathbf{Y}}
\newcommand{\Z}{\mathbf{Z}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathbf{I}}
\newcommand{\m}{\mathbf{m}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\e}{\mathbf{e}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\T}{\mathbf{T}}
\newcommand{\F}{\mathbf{F}}
\renewcommand{\O}{\mathbf{O}}
\renewcommand{\H}{\mathbf{H}}
\newcommand{\g}{\mathbf{g}}
\renewcommand{\r}{\mathbf{r}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\z}{\mathbf{z}}
\newcommand{\Beta}{\boldsymbol{\beta}}
\newcommand{\bveps}{\boldsymbol{\varepsilon}}
\newcommand{\bvphi}{\boldsymbol{\varphi}}
\newcommand{\btheta}{\boldsymbol{\theta}}
\newcommand{\bups}{\boldsymbol{\upsilon}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\bpi}{\boldsymbol{\pi}}
\newcommand{\arrowp}{\stackrel{p}{\rightarrow}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\nn}{\nonumber}
\newcommand{\indf}{\mathds{1}}

% Theorems
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
%\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

% Illustration
\theoremstyle{definition}
\newtheorem{example}{Example}%[subsection]
\newtheorem{hypothesis}{Hypothesis}%[subsection]

% Claims in the theorems (without numbering)
\theoremstyle{remark}
\newtheorem*{claimnn}{Claim}

% Title
\title{Supplementary Materials for Incentives for Preventive Healthcare Provision%\thanks{I would like to thank Livio DiLonardo, Guilherme Fasolin, Saad Gulzar, Cathy Hafer, Matheus Hardt, Carlo Holz, Eduardo Mello, Dimitri Landa, Guisela Pereira, Adam Przeworski, Matias Spektor, Denis Stukal, Marcos Tourinho, and Scott Tyson for their valuable comments. I also thank participants at the MPSA, NYU PE Seminar, and SPSA for their suggestions. All the remaining errors are entirely my responsibility.}
}
\author{Danilo Freire \and Umberto Mignozzetti
}

\date{}

\begin{document}
\maketitle

\doublespacing

\appendix

\tableofcontents

\doublespacing

\section{A Formal Model of the Incentives for Preventive Healthcare Provision in Teams}

XXXX

\subsection{Primitives of the Model}

XXXX

\subsection{No Performance Bonus}

XXXX

\subsection{Individual Performance Bonus}

XXXX

\subsection{Team Performance Bonus}

XXXX

\subsection{Comparative Statics}

XXXX

\subsection{Paper Example}

The Wolfram Alpha code for the paper example is the following:

\begin{verbatim}
RNoI[x_] := 0*x

RInd[x_] := 2 (x^(1/2))*(1 - x)

RCol[x_] := (2 (x^(1/2))*(1 - 2 x))/(1 - x)^2

Plot[{RNoI[x], RInd[x], RCol[x]}, {x, 0, 0.5}, 
  PlotLegends -> {"No Incentives", "Individual Incentives", 
    "Peer Incentives"}, 
  PlotLabel -> "Mechanisms' Revenues", 
  PlotStyle -> {Thickness[0.015], Thickness[0.01],
    Thickness[0.01]}, 
  AxesLabel -> {"Compensation", "Revenue"}]
\end{verbatim}

\section{APSA Experimental Section Standard Report}

\subsection{Question addressed by the experiment}

In this experiment, we study the impact of monetary incentives on the performance of health care workers in Brazil. The study aims to find which financial incentive scheme is better to improve the performance of the workers in the field.

Most of the developmental economics papers on incentives for public service providers highlight that better compensation works. However, these papers focus on services that are individually provided, such as a teacher in a classroom. In health care, rarely the efforts are undertaken independently, and this poses the question: what is the best way to improve public health care provision, when teams, rather than individuals, provide the service?

In this paper, we undertake the first effort to bridge this gap by testing whether team incentives are more effective than individual incentives to improve preventive healthcare provision in Brazil.

The Brazilian case is well suited for this test for two main reasons. First, disease borne by the Aedes aegypti is one of the leading causes of congenital disabilities, hospitalization, and casualties in the global south. Second, a pair of health care workers are responsible for visiting households and exterminate the disease in Brazil. Therefore, we could test individual versus team bonuses in a setting that is relevant to welfare.

\subsection{Hypothesis tested}

We tested which types of bonuses are better for improving the performance of health care workers in Brazil. We tested three incentive schemes: first, monetary compensation with no performance bonuses; second, individual compensation for performance above the median in the headquarter they were assigned; and third, peer bonus compensation for team performance above the median in the headquarters. Theoretically, team bonuses should be more effective, as it increases peer monitoring, diminishing the free-riding problem. However, if there are fewer complementarities, individual rewards can be more productive. This poses the question: which incentive scheme is better for community-based prevention of Aedes aegypti borne diseases in Brazil?

\section{Subjects and Context}

\subsection{Eligibility and exclusion criteria}

\subsubsection{Why was this subject pool selected?}

The subjects participating in the experiment were selected based on a Facebook recruitment Ad posted in the Municipality of Rio Verde, Goiás State, Brazil. We chose this town because we had an agreement with the mayor's office, and also because it had a considerable spike in dengue fever cases in 2018. One of the Facebook ads follows below.

\pagebreak

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/AppCrecruitment1.png}
\caption{Facebook Recruitment Ad with Pilot Participants' picture.\label{appcfbad}}
\end{figure}

The Facebook Ad redirected the participant to a Google Forms where s/he filled up a participation eligibility form. The Google form used is below.

\pagebreak

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/AppCgoogleformsrecruiting.png}
\caption{Google Form Recruitment.\label{appcgform}}
\end{figure}

After that, we send them an email, asking questions on demographics and other characteristics.

\subsubsection{Who was eligible to participate in the study?}

Adults, 18 old or older.

\subsubsection{What would result in the exclusion of a participant?}

Not showing up during the intervention date.

\subsubsection{Were any aspects of recruitment changed after the recruitment began?}

No.

\subsubsection{Procedures used to recruit and select participants}

We posted a Facebook ad in the municipality participating in the intervention. The ad invited potential participants to join the experiment and explained the compensation. If they clicked the ad, they were directed to Google Forms, where they needed to fill up their e-mails and personal information.

\subsubsection{Recruitment dates}

The online recruitment took place right after filling up the form. We send potential participants information regarding Aedes aegypti prevention and a link for a pre-treatment survey. After filled, participants were informed about the live training dates and selected preferred times to participate. They then had to show up for the two-hour training session.

The training date for the pilot was April 13, 2018. The training date for the intervention was May 4, 2018. A picture of the training day before the field follows below.

\pagebreak

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/AppCtrainingdaypic.png}
\caption{Training Day.\label{appctrday}}
\end{figure}

\subsubsection{Settings and locations where the data were collected}

There are two primary datasets used in the paper. First, we collected productivity data from the cell phones used by the participants in the field. Second, we collected governmental data on diseases transmitted by the Aedes aegypti from the Brazilian Ministry of Health diseases notification system (SINAN).

The first dataset is generated by the participants pictures in the field. The second dataset is comprised of governmental records of people that checked into hospitals and were confirmed having dengue fever. This data has the address of the person, that we then used to geolocate the case. Among the diseases transmitted by the Aedes aegypti, dengue fever is the most frequent and easy to detect.

\subsubsection{Relevant specifics about the population}

All the participants were from the municipality of Rio Verde, in the state of Goiás, in Brazil. A map of the municipality follows below:

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/AppCmap1.png}
\caption{Rio Verde, GO, Brazil Map.\label{appcmaprv}}
\end{figure}

\pagebreak

\section{Allocation Methods}

\subsection{Randomization procedure}

We generated the random assignment using block randomization applied on seven variables:

\begin{enumerate}
    \item Above median altruism
    \item Age
    \item Above median religiosity score
    \item Above median Political Engagement
    \item Above median social engagement
    \item Above two minimum wage family income
    \item Above median Facebook popularity (number of friends)
\end{enumerate}

These variables were computed from surveys that we collected prior to the intervention. To test the balance, we use F-tests on the block randomization data. The balance tests follow below.

\pagebreak

\begin{table}[!htbp] \centering 
  \caption{Covariate Balance on Individual Characteristics} 
  \label{appctabcovbalindv} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex]
Altruist &  0.63 &  0.68 &  0.62 & 0.239 & 0.788 \\ 
Age & 25.01 & 26.00 & 26.90 & 0.754 & 0.472 \\ 
Religiosity &  0.53 &  0.38 &  0.45 & 1.487 & 0.228 \\ 
Pol. Engagement &  0.69 &  0.65 &  0.68 & 0.163 & 0.849 \\ 
Soc. Engagement &  0.59 &  0.62 &  0.67 & 0.454 & 0.636 \\ 
Above 2 Min. Wage &  0.34 &  0.35 &  0.29 & 0.336 & 0.715 \\ 
FB Popularity &  0.53 &  0.56 &  0.58 & 0.175 & 0.840 \\ 
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

The treatment is balanced among the participants' covariates. For the territorial assignment, we have the following pre-treatment unweighted results:

\pagebreak

\begin{table}[!htbp] \centering 
  \caption{Covariate Balance Un-Weighted Territorial Assignment} 
  \label{appcunweightbalter} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
Number of Houses & 276.41 & 243.58 & 255.20 &  2.368 & 0.098 \\ 
Number of Households & 885.67 & 750.34 & 785.18 &  3.765 & 0.026 \\ 
Avg. Household Size &   3.21 &   3.07 &   3.07 &  6.566 & 0.002 \\ 
Log Avg. Income &   6.47 &   6.86 &   6.85 &  9.213 & 0.000 \\ 
Cases Before Treatment &  13.78 &   5.94 &   4.66 & 15.638 & 0.000 \\
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

As the territorial assignment is unbalanced, I reweighted the assignment using the census sector information. To reweight I used propensity score matching. After reweight, we have the following results.

\pagebreak

\begin{table}[!htbp] \centering 
  \caption{Covariate Balance Weighted Territorial Assignment} 
  \label{appcweightbalter} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & No Bonus & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
Number of Houses & 276.41 & 282.04 & 281.19 & 0.068 & 0.935 \\ 
Number of Households & 885.67 & 903.04 & 900.39 & 0.060 & 0.942 \\ 
Avg. Household Size &   3.21 &   3.21 &   3.20 & 0.008 & 0.992 \\ 
Log Avg. Income &   6.47 &   6.45 &   6.45 & 0.084 & 0.920 \\ 
Cases Before Treatment &  13.78 &  10.24 &  10.77 & 1.443 & 0.240 \\
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

The reweighting successfully balance the covariates around the territorial assignment.

\subsection{Random assignment}

\subsubsection{Units of randomization}

I randomized the treatment at the level of the participant.

\subsubsection{Cluster random assignment}

No cluster random assignment was used. However, in the differences-in-differences estimation, we use the census sector where the pair worked to cluster the standard errors.

\subsection{Blinding}

\subsubsection{Were participants unaware of the treatment assignment?}

Yes. They knew their incentive schemes, but not other incentive schemes. To ensure that there would be no spillovers, we divided each treatment assigned teams into three different headquarters:

\begin{enumerate}
    \item Assembleia de Deus Church (No bonus)
    \item Videiras Church (Individual reward)
    \item Sara Nossa Terra Church (Collective bonus)
\end{enumerate}

These headquarters were away from each other to avoid contact between participants.

\subsubsection{Were those administering the intervention unaware of the random assignment?}

No. The head research assistants in each group knew that different treatment would be administered in other research headquarters. This measure was taken in case the treatment spillover, and we needed to remove pairs that were disturbing the work from the field.

\subsubsection{Checked whether blind was successful?}

The single-blind was successful. We received no complaints during the intervention day. After the intervention day, participants became aware of the experiment. The post-treatment spillover made the post-treatment survey ineffective because they refused to cooperate with the researchers.

\section{Treatments}

\subsection{Descriptions of the intervention}

\subsubsection{Treatment groups}

We have three treatment groups:

\begin{enumerate}
    \item Control (no performance bonus)
    \item Individual treatment
    \item Collective treatment
\end{enumerate}

In the control group, a bonus was assigned without performance concerns.

In the individual treatment group, we explained the participants that we would rank the performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated. Participants would have their performance ranked and the ones above the median would double their monetary reward (from BRL 110.00 to BRL 220.00).

In the collective treatment group, we explained the participants that we would rank their team performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated. We would sum their individual performance with the performance of their field peers, and then rank the teams. Teams with performance above the median would double their monetary reward (from BRL 110.00 to BRL 220.00, for each person in the team).

The fieldwork was performed in pairs, to mimic the Aedes Aegypti actual practices in Brazil.

\subsubsection{Control groups}

The control group received a monetary reward with no performance requirement.

\subsubsection{Experimental instructions}

In the study day, around 5AM, we randomly assigned pairs, and send emails to the individuals directing them to each of the headquarters, based on their treatment status.

We had three study headquarters: the control headquarters (Assembleia de Deus church); the individual treatment headquarters (Videiras church); and the peer treatment headquarters (Sara Nossa Terra church). We printed set of leaflets with places that they had to administer the treatment. One example of a leaflet follows below:

\pagebreak

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/AppCsarabase1.png}
\caption{Example Working Block.\label{appcevwbl}}
\end{figure}

We handed in the cellphones and the working kits for them. An example of the working kits design follows below:

\pagebreak

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/AppCteamsclothes.jpg}
\caption{Teams Uniforms.\label{appcteamunif}}
\end{figure}

The cellphone was a Samsung, model Galaxy A1. A picture with a testing of the data collection app follows below.

\pagebreak

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figures/AppCcellphone.jpeg}
\caption{Cellphone with data collection app in test.\label{appccpdcit}}
\end{figure}

The informative leaflet distributed to households follow here:

\pagebreak

\begin{figure}
\includegraphics[width=0.8\textwidth]{figures/AppCFolder1.jpg}
\includegraphics[width=0.8\textwidth]{figures/AppCFolder2.jpg}
\caption{Example leaflet handed to households.\label{appcexhhleafl}}
\end{figure}

Then, at around 11:00am we administered the main treatments. They consisted in tell the following instructions to the participants, when we handed the leaflet with their working places:

\begin{itemize}
    \item \textbf{Control:} we told them that there would be an increase in their payment without explaining the reason. We told them about how performance would be measured, without saying anything about compensation based on performance.
    \item \textbf{Individual treatment:} we told the participants that we would measure their performances in the field, and that we would rank all the performances. The individuals with performance above the median would receive the bonus. We also explained in lay terms what was a median, and how we would measure performance.
    \item \textbf{Peer treatment:} we told the participants that we would measure their performances in the field, and that we would rank all the performances. The pairs with performance above the median would receive the bonus. We also explained in lay terms what was a median, and how we would measure performance.
\end{itemize}

\subsection{How and when manipulations were administered}

\subsubsection{Method of delivery}

The manipulations were delivered in person, by the chief headquarter RA, first to all the pairs in a speech, then to each pair in person. For each pair, we reinforced the instructions while handing in the leaflets.

\subsubsection{Software used to administer the treatment}

The randomization was performed in R. The treatment administration was done in person.

\section{Results}

\subsection{Outcome measures and covariates}

\subsubsection{Outcome measures}

There are two groups of outcomes. First, the performance outcomes that are collected from the cellphone used by each participant in the field. Second, the governmental data reported by the health care facilities in the municipality, with all dengue cases.

For the performance data we have:

\begin{enumerate}
    \item Geolocated pictures of house fronts as a proof that they visited to house.
    \item Pictures of exterminated breeding sites.
    \item Video of exterminated a. aegypti larvae.
\end{enumerate}

For governmental data, we have all the people infected by dengue fever that went to the hospital. There were no reported cases of Zika and Chikungunya, as the detection of these diseases are less standardized that Dengue. Moreover, the mayors office have no recollection of microcephaly incidence in the area during the period.

The data then corresponds to all dengue cases, with address of the infected person, date of check-in to the hospital, and the severity of the case.

\subsubsection{Covariates}

We collected information on demographics.

\subsubsection{Which outcomes and subgroup analysis were specified prior to the experiment?}

As the mayors office did not handed in the infections data prior to the intervention, we asked the neighborhoods that had higher dengue fever incidence prior to the intervention, and placed the territorial assignment in these places. However, due to absence of micro-level infectious disease data, we could not consider them prior to the intervention.

\subsubsection{Exploratory analysis}

We run a pilot with 20 pairs before main intervention. We did not administered the incentivized intervention in the pilot to avoid contamination in the main results. The pilot helped us to update the expectations regarding the productivity in the field. Previously, we projected that we should assign around 20 houses per pairs. However, in the pilot we learned that pairs could visit from 40 to 60 houses per pair. In around one-thirty of them nobody answered the door, and in most of them the yards were too small to find any breeding sites. Moreover, most of the places with dengue in the previous week were visited by the municipal health care workers.

\subsection{CONSORT}

\subsubsection{Number of subjects initially assessed for eligibility}

558 individuals filled in the Google Form. 256 showed for the training session one day before the intervention. 205 individuals showed for the intervention. 197 remained until the end of the intervention.

\subsubsection{Exclusions prior to random assignment}

From all eligible people, we excluded the ones that missed the training session. This accounts for 45.8\% of the total.

\subsubsection{Subjects initially assigned to each experimental group}

\begin{enumerate}
    \item 68 to control group.
    \item 68 to individual treatment group.
    \item 69 to peer treatment group.
\end{enumerate}

\subsubsection{Proportion received x not received intervention}

\begin{enumerate}
    \item 58 received the control intervention out of 68 in the control group.
    \item 64 received the intervention out of 68 in the individual treatment group.
    \item 75 received the intervention out of 69 in the peer treatment group.
\end{enumerate}

\subsubsection{Why did not receive intervention?}

The individuals did not received the intervention if they missed the field. They were then excluded from the data.

\subsubsection{Number subjects each group dropped experiment}

No subject were dropped from the assignment. Six subjects joined the experiment in the intervention day. We assigned them to the peer intervention group.

\section{Statistical analysis}

\subsection{Describe statistical analysis}

We run four types of statistical analysis:

\begin{enumerate}
    \item Balance tests
    \item Performance outcome analysis
    \item Disease incidence analysis
    \item Differences-in-differences analysis
\end{enumerate}

The main equations for the performance outcomes are:

\[
Y_i = \alpha + \beta D_i + \varepsilon_i
\]

Where $\beta$ is the outcome of interest, $Y_i$ is the outcome for case $i$, and $D_i$ is the treatment status for case $i$. And the code is:

\begin{verbatim}
mod <- lm(outc ~ treat, data = dataframe)
\end{verbatim}

The main equations for the disease incidence are:

\[
Y_i = \alpha + \beta D_i + \varepsilon_i
\]

Where $\beta$ is the outcome of interest, $Y_i$ is the outcome for case $i$, and $D_i$ is the treatment status for case $i$. The only difference is that the estimates are weighted using the propensity score matching. And the code is:

\begin{verbatim}
mod <- lm(outc ~ treat, 
          data = dataframe, 
          weights = dataframe$weights)
\end{verbatim}

Finally, the differences-in-differences estimator has the following form:

\[
Y_i = \alpha + \gamma Time_i + \theta Treat_i + \beta Time_i \times Treat_i + \varepsilon_i
\]

And our quantity of interest is $\beta$. The codes for the regression models I run are as follows:

\begin{verbatim}
mod <- felm(outc ~ time+treat+DID|0|0|CensusSectors, 
            data = dataframe)
\end{verbatim}

This regression uses the package \texttt{lfe}, as it facilitates the use of cluster-robust standard errors.

Table \ref{appcprodregs} shows the performance in the field estimation.

\pagebreak

\begin{table}[!htbp] \centering 
  \caption{Field Productivity} 
  \label{appcprodregs} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\ 
& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\ 
\hline \\[-1.8ex] 
 Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\ 
  & (4.906) & (4.018) & (5.251) & (0.058) \\ 
  & & & & \\ 
 Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\ 
  & (4.428) & (3.571) & (4.049) & (0.076) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 197 & 197 & 197 & 197 \\ 
Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{Robust Standard Errors in Parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

The performance regressions shows that:

\begin{enumerate}
    \item Performance bonus, regardless of the nature, lower the number of houses visited. This because to score high they needed to find breeding sites and larvae, not only visit houses.
    \item Performance bonus, regardless of the nature, increases the number of breeding sites cleaned up by the workers. The effect seems to be higher in the individual bonus group.
    \item Only collective bonus increase the chance of finding larvae. Note that the effort required to find larvae is considerably higher than the effort required to find breeding sites.
\end{enumerate}

For the disease incidence regressions, the results in Table \ref{appcregdiseaseinc1} show all null effect.

\pagebreak

\begin{table}[!htbp]
  \caption{Disease incidence in Rio Verde Census Sectors} \centering 
  \label{appcregdiseaseinc1} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & Before & 15 days & 30 days & 60 days & 90 days & 30-60 days \\ 
& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
\hline \\[-1.8ex] 
 Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
  & & & & & & \\ 
 Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{Robust Standard Error in Parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular} 
\end{table}

Finally, for the differences-in-differences models, the results are in Table \ref{appcdifindifdiseases}.

\pagebreak

\begin{table}[!htbp] \centering 
  \caption{Disease Incidence -- Differences in Differences Model} 
  \label{appcdifindifdiseases} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (indv. x collect.) \\ 
\hline \\[-1.8ex] 
 DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:} & \multicolumn{5}{r}{Robust standard error, clustered at the census-sector level, in parentheses.} \\ 
& \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Table \ref{appcdifindifdiseases} shows the following:

\begin{enumerate}
    \item There is a 10.3\% effect on the full data model.
    \item The other windows are not significant but the sign is consistent with lower disease incidence.
    \item Comparing individual and collective, collective decreases by 2.9\%, but the result is not significant.
\end{enumerate}

\subsection{Standard errors}

The robust standard errors are computed using \texttt{vcovHC} function in the package \texttt{sandwich}. The standard error is the same as the Stata's \textit{comma-robust}.

\subsection{Attrition}

\subsubsection{Missing data}

The data we have is complete, as during the intervention no pair or individual participant withdrew from the research. Between the recruitment and the training we had a considerable number of dropouts. The numbers are:

\begin{itemize}
    \item \textbf{Signed the Google Form:} 558
    \item \textbf{Filled surveys:} 407
    \item \textbf{Showed for in-person training:} 256
    \item \textbf{Participated in the experiment:} 205
\end{itemize}

\subsubsection{Analyze pre-treatment variables to check reasons}

The only variables we have for all 558 individuals that filled up the Google Form is age and gender. Comparing them with the participants in the field shows that the attrition does not seem to have a detectable pattern.

\pagebreak

\begin{table}[!htbp] \centering 
  \caption{Attrition Analysis} 
\begin{tabular}{@{\extracolsep{5pt}} lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & Attrition & No Bonus & Individual & Collective & F-Stat & P-Val \\ 
\hline \\[-1.8ex] 
Age &  26.17 & 25.04 & 26.07 & 26.00 & 0.461 & 0.710 \\ 
Female &   0.72 &  0.79 &  0.79 &  0.74 & 0.805 & 0.492 \\ 
Has Vehicle &   0.35 &  0.27 &  0.37 &  0.37 & 0.651 & 0.582 \\ 
N & 341 & 73 & 71 & 73 &  &  \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/appccasesdengue.pdf}
\caption{Disease incidence before and after.\label{appcdisincbaf}}
\end{figure}

\pagebreak

\subsubsection{Method for addressing missing data}

The missing cases generated no outcomes nor participated in the research in any way. Therefore, we excluded them from the analysis.

\section{Other information}

\subsection{IRB}

We received IRB from the New York University and Fundação Getulio Vargas.

\begin{itemize}
    \item NYU IRB number: IRB-FY2017-17
    \item FGV IRB number: IRB-01/2017
\end{itemize}

\subsection{Pre-registration}

The study was pre-registered using the EGAP pre-registry tool, by the number 20180504AA.

\subsection{Funding}

The study was funded by the FGV applied research grant officer. They had no interference on the study results.

\subsection{Replication dataset}

The replication materials is in the following website: \url{https://github.com/umbertomig/dissertationNYU}.

\subsection{Thanks}

This research benefited from the contribution of the following research assistants:

\begin{itemize}
    \item Natalia Liberato
    \item Guilherme Fasolin
    \item Phillipe Guedon
    \item Vitor Sion
    \item Fatima Portella
    \item Giovanna França
    \item Catarina Roman
    \item Larissa Santos
    \item Leticia Santana
\end{itemize}

I am very thankful for all their help before, during, and after the field. All the remaining errors are my entire responsibility.

\subsection{Some field pictures}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/AppCf12.png}
\caption{Field pictures}
\end{figure}

\pagebreak

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/AppCf14.png}
\caption{Field pictures}
\end{figure}

\pagebreak

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{figures/AppCf15.png}
\caption{Field pictures}
\end{figure}

\clearpage

% Bibliography
\singlespacing
\begin{footnotesize}
\bibliographystyle{chicago}
\bibliography{biblio.bib}
\end{footnotesize}

\end{document}

### 2020-10-08 paper/article.Rmd
first commit

---
title:  |
        | Long Article Title:
        | A Very Long Subtitle
author: 
  - Danilo Freire[^freire]
  - Umberto Mignozzetti[^mignozzetti]
date: \today
thanks: "The authors thank Professors John and Jane Doe for their helpful comments."
abstract: "This is a personal article template for RMarkdown. It uses Linux Libertine and Inconsolata fonts, British English, double-spaced text and numbered sections. The colours are personalised too: URLs are in dark blue, internal links are in mahogany and the table of contents is in black. The template also has pre-formatted entries for the abstract, keywords and JEL classification codes. You need to install `R` (and the `rmarkdown` package), `pandoc` and a `TeX` system to compile the pdf. In case you don't want to download large `TeX` binaries, I recommend you to install the great `TinyTeX R` package. A quick note: if you want to use colons in the abstract or the `thanks` entry, please don't forget to put the whole text in quotes. Otherwise, YAML might not parse it correctly. I hope you find this template useful and feel free to send me a message if you have any suggestions."
abstractspacing: double
keywords: R Markdown; pandoc; template
jelcodes: A00, B11, C22
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
if (!require("kableExtra")) {
    install.packages("kableExtra")
}
```

[^freire]: Independent Researcher,
[`danilofreire@gmail.com`](mailto:danilofreire@gmail.com),
<http://danilofreire.github.io>.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods
Department, Emory University, 532 North Kilgo Circle, 4^th^ Floor, Atlanta, GA
30322, USA,
[`umberto.mignozzetti@emory.edu`](mailto:umberto.mignozzetti@emory.edu),
<http://umbertomig.com>.

\newpage

# Introduction
\label{sec:intro}

The *Aedes aegypti* mosquito species is the major vector of several arboviral
diseases worldwide, including dengue, yellow fever, Zika, and chikungunya
[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@thangamani2016vertical]. Over the past 30 years, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
around 100 countries, causing 400 million infections and 22 thousands deaths
each year [@bhatt2013global; @cdc2020dengue; @musso2018unexpected]. Since there
are no safe vaccines for most *A. aegypti*-transmitted diseases
[@sridhar2018effect; @world2017dengue], we have seen a number of recent dengue
and Zika outbreaks in Asia, the Caribbean, South America, and the United States
[@carlson2016ecological; @leta2018global]. Chikungunya virus, which was endemic
only to Africa, has already been reported in every region of the world
[@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].

Mosquito control is the primary strategy to prevent *A. aegypti*-borne
infections [@beatty2010best; @eisen2009proactive; @ooi2006dengue]. The World
Health Organization recommends the elimination of containers and the use of
insecticide to reduce vector breeding, specially in settings where human-vector
contacts are frequent, such as schools, hospitals, and workplaces
[@WHO2012global; @world2020denguecontrol]. However, cleaning breeding sites and
insecticide spraying are labour-intensive processes and are often carried out
inconsistently [@paz2015dengue; @siddiqui2016use; @WHO2012global]. In most
endemic countries, local governments are the main responsible for providing
vector control, thus increasing the productivity of civil servants is essential
to the effectiveness of anti-mosquito programmes worldwide.

Financial incentives are crucial determinants of worker performance in public
and private organisations [@burgess2003role]. While studies indicate that
reward schemes may improve the productivity of health care providers
[@basinga2011effect; @flodgren2011overview; @ulrich2005does], it is unclear how
they affect the motivation of workers fighting *A. aegypti*. Moreover, there is
no evidence about the impact of financial incentives on patient-level arboviral
outcomes, such as virus-related hospitalisations or disease incidence
[@flodgren2011overview].

To explore how monetary incentives affect health worker motivation and patient
outcomes, we ran a randomised field experiment in the city of Rio Verde,
Brazil, which has experienced a peak in dengue infections in the last years. We
hired and trained teams of health care workers to perform simplified procedures
designed to exterminate *A. aegypti* breeding sites. Our experiment consisted
of two treatment arms plus a control condition. The control group received a
fixed compensation for completing their task, and we offered individual or
collective bonuses to those allocated in the two treatment groups. We then
measured the impact of the compensations schemes on the number of breeding
sites discovered, larvae exterminated, and city-level dengue incidence 30, 60,
and 120 days after our intervention.

We find that monetary rewards increase the number of cleaned breeding sites in
both treatment conditions (individual and team bonuses) and collective
financial incentives also improve larvae extermination. Our results show that
the control group has a high incidence of houses visited in less than two
minutes apart from each other, which suggests that workers may cheat in the
absence of financial incentives. When we combine both treatments, we also find
that the intervention decreases dengue incidence in 10.3%, but the results are
not robust. In summary, we provide experimental evidence that performance
bonuses increase productivity in public service delivery and that small
financial incentives to health workers may improve patient outcomes and reduce
hospitalisation costs in *Aedes*-endemic countries.

# Methods
\label{sec:methods}

We ran a randomised field experiment at the individual level in the municipality
of Rio Verde, Brazil, which had experienced a major dengue outbreak one year
prior to our experiment (2017). We used Facebook advertisements to recruit
potential participants. The advertisements directed applicants to a Google Forms
web page that requested their contact information, and we sent a pre-treatment
demographic questionnaire to every applicant who provided a valid email address.
At this stage, we excluded all individuals under 18 years old. We invited the
remaining applicants to our training session, which we ran on the 4^th^ of May,
2018. The meeting consisted of a lecture on *A. aegypti* vector biology and
practical instructions on how to find and exterminate mosquito breeding sites.
Those who did not attend the session were also excluded from the study.

Table \ref{tab:covbal} displays the attrition tests, the covariate balance
tests, and the territorial assignment before and after applying propensity
score matching [@dehejia2002propensity; @rosenbaum1985constructing] on census
tract characteristics. We observe no significant differences regarding
attrition rates, reinforcing that the treatment was correctly randomised.
Participants' demographics are also similar across all groups, and the matching
technique successfully balanced the territorial assignment.

\begin{table}[ht] \centering 
\small
  \caption{Covariate Balance on Individual Characteristics} 
  \label{tab:covbal} 
\begin{tabular}{@{\extracolsep{5pt}} lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & Attrition & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
& & \multicolumn{5}{l}{Panel A: Attrition Pattern Test} \\
\hline \\[-1.8ex]
Age &  26.17 & 25.04 & 26.07 & 26.00 & 0.461 & 0.710 \\ 
Female &   0.72 &  0.79 &  0.79 &  0.74 & 0.805 & 0.492 \\ 
Has Vehicle &   0.35 &  0.27 &  0.37 &  0.37 & 0.651 & 0.582 \\ 
N & 341 & 73 & 71 & 73 &  &  \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc} 
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel B: Covariate Balance on Individual Characteristics} \\
\hline \\[-1.8ex]
Altruist &  0.63 &  0.68 &  0.62 & 0.239 & 0.788 \\ 
Age & 25.01 & 26.00 & 26.90 & 0.754 & 0.472 \\ 
Religiosity &  0.53 &  0.38 &  0.45 & 1.487 & 0.228 \\ 
Pol. Engagement &  0.69 &  0.65 &  0.68 & 0.163 & 0.849 \\ 
Soc. Engagement &  0.59 &  0.62 &  0.67 & 0.454 & 0.636 \\ 
Above 2 Min. Wage &  0.34 &  0.35 &  0.29 & 0.336 & 0.715 \\ 
FB Popularity &  0.53 &  0.56 &  0.58 & 0.175 & 0.840 \\ 
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel C: Unmatched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex] 
Number of Houses & 276.41 & 243.58 & 255.20 &  2.368 & 0.098 \\ 
Number of Households & 885.67 & 750.34 & 785.18 &  3.765 & 0.026 \\ 
Avg. Household Size &   3.21 &   3.07 &   3.07 &  6.566 & 0.002 \\ 
Log Avg. Income &   6.47 &   6.86 &   6.85 &  9.213 & 0.000 \\ 
Cases Before Treatment &  13.78 &   5.94 &   4.66 & 15.638 & 0.000 \\ 
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel D: Matched Covariate Balance on Territorial Assignment} \\
\hline \\[-1.8ex] 
Number of Houses & 276.41 & 282.04 & 281.19 & 0.068 & 0.935 \\ 
Number of Households & 885.67 & 903.04 & 900.39 & 0.060 & 0.942 \\ 
Avg. Household Size &   3.21 &   3.21 &   3.20 & 0.008 & 0.992 \\ 
Log Avg. Income &   6.47 &   6.45 &   6.45 & 0.084 & 0.920 \\ 
Cases Before Treatment &  13.78 &  10.24 &  10.77 & 1.443 & 0.240 \\ 
\hline
Pairs & 34 & 34 & 35 &  &  \\ 
N & 68 & 68 & 70 &  &  \\
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

\normalsize

The intervention took place on the 5^th^ of May, 2018. We randomly assigned
subjects to three groups. To avoid spillovers, we directed each group to
separate headquarters before the intervention began. Participants worked in
pairs and were aware of other groups, but they did not know about the different
treatment conditions. In the control group ($n = 68$), we told participants
that they would receive a flat payment regardless of their performance (BRL 110
/ USD 20 per subject). In the individual treatment group ($n = 68$), we
informed subjects that we would rank individual performances, and that we would
double the compensation for all of those who performed above the sample median
(BRL 220 / USD 50 per subject). In the collective treatment group ($n = 70$),
we explained that we would rank the pair performance and double the payment for
teams who presented results better than the sample median (BRL 220 / USD 50 per
subject). The teams received a leaflet with a map of the area they should
cover. The route comprised of two to three blocks and contained around 120
houses.

A typical visit to a household consisted of the following steps. First,
participants rang the doorbell in a house and explained that the municipality
had experienced a dengue fever outbreak. They instructed dwellers on how to
lower dengue incidence and handed them a leaflet with information about dengue
prevention practices. Our subjects then requested whether they could inspect
the person's yard. If granted permission, they entered the household and
searched for clean breeding sites, such as pots filled with clear water, and
recipients containing larvae. Upon exterminating a breeding site (pouring out
the accumulated water, for example), subjects had to report their task by
taking a photo on their cellphones. When they discovered larvae, they had to
record a video showing the larvae before exterminating it. At the end of their
visit, they had to take a picture of the household to account for their
presence in the location.

The primary outcome in this study is field productivity of the health care
workers. We measure worker productivity by coding cellphone data collected
during the intervention into four indicators: 1) the number of houses visited;
2) the number of houses visited within less than two minutes; 3) the number of
breeding sites removed and cleaned; 4) the number of exterminated larvae. We
employed ordinary least squares with robust standard errors [@imbens2016robust].
We estimated the statistical power of the study assuming a treatment effect of
0.15 standard deviations.

The second outcome of interest is dengue incidence in the municipality of Rio
Verde. The Rio Verde Mayor's Office provided us with its annual health care
report, which contains the dates and personal information of patients who had
dengue fever and received hospital treatment from January to September 2018. We
georeferenced the home addresses of the patients and compared the incidence map
with the distribution of our intervention. We use a differences-in-differences
estimator to assess the impact of our experiment [@angrist2008mostly;
@card1994minimum].

We pre-registered the experiment on the Evidence in Governance and Policy
(EGAP) website (<https://osf.io/6q8vu/>) and received IRB approval from New
York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
funders of this study had no influence over the formulation, organisation,
analysis, and interpretation of the outcomes. Health care workers gave written
consent upon filling the Qualtrics questionnaire. During the intervention, the
occupants of households inspected for breeding sites and larvae gave oral
consent. For more information on the experimental design, sample
characteristics, exclusion criteria, and estimation methods, please refer to
the Supplementary Material.

# Results
\label{sec:results}

We find that providing financial incentives to health care worker significantly
increase their field productivity. Both our individual bonus and our collective
bonus treatment groups find more *A. aegypti* breeding sites and exterminate
more mosquito larvae than participants in the control condition, which did not
receive performance compensations. Our results also indicate that the
intervention decreases city-wide levels of dengue incidence, but the
coefficients only reach statistical significance when we combine the two
treatments together and contrast them with the control group. Overall, the
findings suggest that monetary payments are an effective method of improving
health worker performance, yet more research is needed to assess whether higher
labour productivity leads to fewer dengue-related hospitalisations.

## Field Productivity
\label{sub:productivity}

We have four indicators to measure health worker productivity. The first is the
number of houses visited during the intervention. The second indicator is the
number of houses in which the visits lasted for less than two minutes. The
third dependent variable is the number of *A. aegypti* breeding sites removed
and cleaned. Our fourth variable indicates the number of mosquito larvae
exterminated. Table \ref{tab:productivity} summarises the experimental results.

\begin{table}[ht] 
  \centering 
  \small
  \caption{Field Productivity} 
  \label{tab:productivity} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent Variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\ 
& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\ 
\hline \\[-1.8ex] 
 Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\ 
  & (4.906) & (4.018) & (5.251) & (0.058) \\ 
  & & & & \\ 
 Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\ 
  & (4.428) & (3.571) & (4.049) & (0.076) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 197 & 197 & 197 & 197 \\ 
Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{Robust standard errors in parentheses. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Subjects who received monetary incentives, either alone or in pairs, visited
fewer houses than those who did not earn financial rewards. While the result
may seem counter-intuitive, it actually attests the effectiveness of the
treatment. This is because we offered incentives for subjects to exterminate
larvae and find breeding sites, but not to visit a greater number of
households. As a result, participants in the two treatment groups did a
thorough job in each household, which explains the lower number of visits
during the allotted time. We find that subjects in the individual and in the
collective bonus groups visited $-9.879$ (CI: [XXX, XXX], $p-$value $= 0.XXX$)
and $-7.554$ (CI: [XXX, XXX], $p-$value $= 0.XXX$) households, respectively.

Our second indicator provides further evidence in favour of our argument. We
see that the two groups which earned performance bonuses spent more time in the
households, as their number of houses visited for less than two minutes is
significantly lower than those of the control condition. On average,
participants in the individual bonus treatment arm visited $-8.044$ (CI: [XXX,
XXX], $p-$value $= 0.XXX$) fewer houses than the control, and those in the
collective bonus group visited $-6.479$ (CI: [XXX, XXX], $p-$value $= 0.XXX$).

Incentivised teams find and clean more breeding sites than non-incentivised
ones. Individually incentivised health workers find 25.118 (CI: [XXX, XXX],
$p-$value $= 0.XXX$) more breeding sites than the non-incentivised control
group. The effect for those in the collective bonus group is 21.512 (CI: [XXX,
XXX], $p-$value $= 0.XXX$), slightly smaller than for the first treatment.

Collective incentivized teams are more effective in finding larvae. In our
study, collectively incentivized subjects have 16.3\% more chance to find
larvae than non incentivized workers. Finding larvae is harder, and the
detection chances profit from teamwork. If teams are cooperating, searching the
house becomes more natural, and they can coordinate to do a more thorough job.
Additionally, the detection tends to be excludable: one individual finding
larvae makes the chances of keep finding larvae in the household considerably
smaller. Collective bonus is not excludable within the teams, making them
cooperate more to get the reward.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

### 2020-10-08 paper/first-version.tex
first commit

\documentclass[a4paper, reqno, 12pt]{article}

% Packages
\usepackage[brazilian,english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[super]{nth}
\usepackage{color, graphics, graphicx, amsmath, times, amsfonts, amssymb}
\usepackage{listings,  palatino, fancyhdr, setspace, bbm, type1cm, titletoc, dsfont}
\usepackage{amsthm, underscore, lscape, dcolumn, arydshln}
\usepackage[usenames,svgnames,dvipsnames]{xcolor}
\usepackage[sharp]{easylist}
\usepackage[a4paper,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage[font=small,format=plain,labelfont=bf,up,textfont=it,up]{caption}
\usepackage[pdftex,plainpages=false,pdfpagelabels,pagebackref = false,colorlinks=true,citecolor=DarkBlue,linkcolor=NavyBlue,urlcolor=DarkRed,filecolor=DarkBlue,bookmarksopen=true]{hyperref}
\usepackage{tabularx}
\usepackage[para,online,flushleft]{threeparttable}  
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{natbib}
\usepackage{subcaption, rotating}
\usepackage{pgf, tikz, pgfplots, mathrsfs}

\usetikzlibrary{positioning,arrows,calc,fit}

\pgfplotsset{compat=newest}

\definecolor{wrwrwr}{rgb}{0.38,0.38,0.38}
\definecolor{rvwvcq}{rgb}{0.08,0.38,0.75}

\tikzset{
block/.style={
  draw, 
  rectangle, 
  minimum height=1.5cm, 
  minimum width=3cm, align=center
  }, 
line/.style={->,>=latex'}
}

\tikzset{container/.style={draw, rectangle, dashed, inner sep=1.5em}}

\bibpunct{(}{)}{;}{a}{}{,}

\pagestyle{plain}
\renewcommand{\arraystretch}{1.2}
\sloppy

%\renewcommand{\thepage}{}
\renewcommand{\bibname}{References}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand{\wh}[1] {\widehat { #1 }}

\newcommand{\twopd}[4]{\left\{\begin{array}{ll} #1 & \text{if } #2 \\ #3 & \text{if } #4 \end{array} \right.}

\newcommand{\twopdo}[3]{\left\{\begin{array}{ll} #1 & \text{if } #2 \\ #3 & \text{otherwise} \end{array} \right.}

\newcommand{\threepd}[6]{ \left\{ \begin{array}{lll} #1 & \text{if } #2 \\ 
#3 & \text{if } #4 \\ #5 & \text{if } #6 \end{array} \right.}

\newcommand{\threepdo}[5]{ \left\{ \begin{array}{lll} #1 & \text{if } #2 \\ 
#3 & \text{if } #4 \\ #5 & \text{otherwise} \end{array} \right.}

% Bold letters
\newcommand{\X}{\mathbf{X}}
\newcommand{\Y}{\mathbf{Y}}
\newcommand{\Z}{\mathbf{Z}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\I}{\mathbf{I}}
\newcommand{\m}{\mathbf{m}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\e}{\mathbf{e}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\T}{\mathbf{T}}
\newcommand{\F}{\mathbf{F}}
\renewcommand{\O}{\mathbf{O}}
\renewcommand{\H}{\mathbf{H}}
\newcommand{\g}{\mathbf{g}}
\renewcommand{\r}{\mathbf{r}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\z}{\mathbf{z}}
\newcommand{\Beta}{\boldsymbol{\beta}}
\newcommand{\bveps}{\boldsymbol{\varepsilon}}
\newcommand{\bvphi}{\boldsymbol{\varphi}}
\newcommand{\btheta}{\boldsymbol{\theta}}
\newcommand{\bups}{\boldsymbol{\upsilon}}
\newcommand{\bgamma}{\boldsymbol{\gamma}}
\newcommand{\bpi}{\boldsymbol{\pi}}
\newcommand{\arrowp}{\stackrel{p}{\rightarrow}}
\newcommand{\0}{\mathbf{0}}
\newcommand{\Prob}{\mathbb{P}}
\newcommand{\nn}{\nonumber}
\newcommand{\indf}{\mathds{1}}

% Theorems
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{assumption}{Assumption}
%\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

% Illustration
\theoremstyle{definition}
\newtheorem{example}{Example}%[subsection]
\newtheorem{hypothesis}{Hypothesis}%[subsection]

% Claims in the theorems (without numbering)
\theoremstyle{remark}
\newtheorem*{claimnn}{Claim}

% Title
\title{Incentives for Preventive Healthcare Provision%\thanks{I would like to thank XXXX for their valuable comments. I also thank participants at the MPSA, NYU PE Seminar, and SPSA for their suggestions. All the remaining errors are entirely my responsibility.}
}
\author{
Danilo Freire
\and
Umberto Mignozzetti
}

\date{}

\begin{document}
\maketitle

\singlespacing
\begin{abstract}
  \begin{footnotesize}
    \noindent Viral epidemics are among the leading causes of death in humans and the Zika virus in Brazil warned the world about the dangers of the \textit{Aedes aegypti} mosquito. Since teams of healthcare workers take preventive care efforts, understand how to incentivize teams is essential to improve these interventions. However, most of the literature focuses on individual nurses or teachers, overlooking team efforts, team monitoring, and peer pressure. In this chapter, I bridge this gap by running a field experiment to determine which types of monetary incentives improve teamwork in the Brazilian case. The trial consisted of hired and trained subjects that had to visit houses and help residents to exterminate mosquito breeding sites. I randomly assigned performance monetary rewards in the form of individual and peer performance bonuses. I find that bonuses increased the number of cleaned breeding sites in both treatment status, but team bonuses also improved larvae extermination. Overall, the intervention decreased the disease incidence in 10.3\%, but the results seem not to be robust. This chapter has implications for the design of preventive healthcare interventions.

    \noindent \textbf{Keywords:} XXXX.
  \end{footnotesize}
\end{abstract}

\doublespacing

\section{Introduction}

The recent SARS-COV-2 epidemic warns the world about the dangers of viral infections. In 2015, another outbreak in Brazil frightened the globe: the Zika virus epidemic. The Zika virus is a vector-borne disease, with mild effects in adults, but disastrous consequences for fetuses. The outbreak was responsible for a 500-fold increase in Brazil's congenital disabilities, only in 2015. The Zika virus is spread by the \textit{Aedes aegypti} mosquito, which is well known in tropical countries, as it is also the vector for dengue, malaria, and chikungunya. According to the CDC, these diseases together had killed more than 25 thousand people worldwide in 2016.

Despite the use of pesticides and transgenic mosquitoes, specialists agree that preventive healthcare policies are the most sustainable and effective method to fight the \textit{Aedes aegypti} \citep{eisen2009proactive}. The mosquito prevention requires teams of preventive healthcare workers to visit households, helping people to find and exterminate the mosquitoes breeding sites. To this extent, understanding how to improve the productivity of these healthcare workers is crucial for welfare.

One aspect that is often neglected by the medical literature is that better incentives may improve performance. However, the political economy literature has no clear-cut evidence in the case of healthcare workers. On the one hand, economists show that for teachers, increasing monetary compensation, paired with extensive monitoring, improve school attainments \citep{duflo2012incentives}. On the other hand, \citet{Banerjeeetal2008} showed that to incentivize overworking nurses may be ineffective, as they may be performing at their highest level. No paper has to this date investigated how to improve service provision in teams of healthcare bureaucrats. Despite this fact, teams play a significant role in healthcare: a person that goes to a hospital usually interacts with many nurses, doctors, and assistants to diagnose and treat her problem. Teamwork demands cooperative efforts of agents that have to share information and monitor each other's work to ensure an effective outcome.

In this chapter, I study how to incentivize teams of preventive healthcare workers in Brazil. I build a principal-agent model, along the lines of \citet{itoh1991incentives}, to uncover the main perils in incentivizing these teams. In the model, agents divide effort between doing their job or helping other agents to do their jobs. The principal, a healthcare governmental agency, receives a continuous probabilistic benefit from lower infection rates, which has a higher chance of happening when the agents put more effort. The healthcare agency manipulates the workers' incentives by changing the contracts offered to the workers. The principal-agent model generates three main predictions. In the baseline model, where the healthcare agency gives no individual or collective incentives, the health workers exert zero effort in equilibrium. When the healthcare agency provides individual bonuses, the health worker puts effort toward her work, but there is no effort to help each other. This improves the agency's welfare, at a limited rate, depending on the cost of exerting effort. Finally, when we promote peer incentives, the result depends on how much does it cost for workers to specialize in their jobs. In the case of \textit{Aedes aegypti} prevention, as the task is simple and health workers have no gains of specialization, giving collective bonuses increase the healthcare agency's welfare, as it raises both the subject's own and helping efforts. It should be expected more aggregated outcomes in collective bonus schemes, followed by the individual bonus schemes, and no benefits from no bonuses.

I test this theory by running a field experiment in Rio Verde, a municipality in the Brazilian state of Goias. I hired and trained teams of health workers to perform a simplified preventive healthcare task: visit households to search for potential breeding sites and \textit{Aedes aegypti} larvae. While all participants worked in pairs and have the same duties, they faced three different contractual schemes. In the control group, workers received a flat compensation, untied to their performance. In the individual treatment group, I assigned workers to a contract where workers were ranked based on their accomplishments, and subjects with performance above-median received a bonus. Finally, I assigned pairs to a collective treatment group based on the aggregated performance of the team. Pairs with performance above the median received the rewards.

To measure their performance, I looked into two primary outcomes: the workers' field production collected during the intervention, and the medical reports sent by the municipality to the Ministry of Health disease notification system. For the field outcomes, I find that subjects in the individual and collective treatment groups visited fewer households than subjects in the control group. This could be seen as paradoxical, but as the control participants had no performance incentives, they mostly walked around the neighborhood they were assigned without entering houses. Individual bonus groups eliminated 25.1 breeding sites more than the control groups, while the collective bonus groups eliminated 21.5 breeding sites more than the control group. In terms of larvae extermination, collective bonus groups perform 16.3\% better than the control group, while the individual bonus groups perform similarly to the control group. Finding larvae is the highest yield outcome for preventing \textit{Aedes aegypti}, as larvae are at the final stage of becoming a mosquito.

Using governmental data, I found weak evidence supporting that the intervention lowered the \textit{Aedes aegypti} disease in Rio Verde. Using a differences-in-differences estimator with all three treatments against a pure control of houses that have received no types of interventions, I show that the experiment lowered the disease incidence in 10.3\%. However, the results become insignificant when I consider time windows smaller than 120 days before and after the intervention. There is no effect when I disentangle each treatment individually, but the direction of the results are consistently negative in the collective bonus intervention. The null findings here highlight the difficulty of translating workers' productivity into medical outcomes.

This chapter makes three major contributions to the political economy of preventive healthcare provision literature. First, it adds to a growing scholarship on how incentives affect the efficiency of health care interventions. \citet{Lloydetal1992} and \citet{Toledo2007} show significant effects of community-based field interventions against the \textit{Aedes aegypti}. \citet{Erlanger2008} question these interventions' efficacy vis-a-vis chemical treatments and vaccines. In a recent meta-analysis, \citet{Mignozzettietal2020a} show that community interventions may have a weakly positive effect in terms of \textit{Aedes aegypti} control. In this paper, I highlight that the medical literature may have two shortcomings: first, it lacks a study of the best implementation methods for preventive health care. When the incentives are well designed, the performance in the field increases consistently; and second, the results also imply that performance maps imperfectly into improved entomological parameters, such as the number of larvae per 1000 inhabitants in a given region (Breteau Index) or the number of infections reported before and after the intervention. This can potentially signal that the interventions are ineffective even when the field productivity is high.

Second, this experiment contributes to studies about how to increase the productivity of the public sector. Most of the work about bureaucratic productivity focus on the incentives of a given bureaucrat to improve their outputs. Several papers find that increasing payment enhances the work of teachers and nurses \citep{Banerjeeetal2008, duflo2012incentives, gertler2013using, britton2016teacher, muthmainnah2017improving}. \citet{muthmainnah2017improving} review 25 articles, showing that better salaries improve productivity and the working satisfaction of nurses. \citep{Banerjeeetal2008} show that when the efforts are binding, increasing wages and monitoring of nurses is ineffective. Similarly, \citet{duflo2012incentives} demonstrate that monitor and rewarding teachers is effective in improving education outcomes. This chapter builds upon on their work by studying how to incentivize teams instead of individual workers. Teams are the most common form of working organization, and in the public sector, workers seldom provide services individually. However, different from \citet{bandiera2013team}, this paper does not allow teams to self-select members. My approach simplifies the task of isolating the effect of compensation, eliminating a sorting effect that would happen if we allow workers to choose their peers.

Finally, this research contributes to understanding how to incentivize teams of workers. Incentivizing teams is to tread carefully around the tension between cooperation and conflict. On the one hand, team effort provides a cheap way to monitor free-riding \citep{Holmstrom1982}, and it may increase complementarities of talents and coordination in actions \citep{holmstrom1990regulating, itoh1991incentives}. On the other hand, team workers can collude against the principal \citep{kofman1996optimality}, and within teams, there are also incentives for competition and sabotage \citep{lazear1995personnel}. \citet{bolton2005contract} summarizes the literature and the incentives faced by organizations. Empirically, several papers investigated the output in firms \citep{bandiera2013team}, the peer effects of implementing tasks in the same environment, where workers can witness the other workers' efforts \citep{FalkIchino2006}, and the network effects in collective production \citep{amodio2019inputs, Bursztynetal2014, Castilloetal2014}. I show that collective incentives are adequate to improve field productivity. Qualitative research during the field points that workers find it easier to help each other when their incentives are aligned. The shared risk between team workers makes them more prone to find larvae, which is considerably harder to find than breeding sites. This improves welfare, as larvae are the last stage before a disease-spreading mosquito.

\section{A Theory of Service Provision under Moral Hazard in Teams}

Consider a strategic interaction between two healthcare workers and a governmental agency. The agency hires healthcare workers to provide preventive healthcare. And the workers decide the effort they will exert, conditional on the compensation scheme they receive.

From the perspective of healthcare workers, teams perform preventive healthcare tasks. To inspect a house and eliminate mosquito breeding sites, preventive healthcare workers visit the households in pairs or triplets. This supposedly increases efficiency as it helps them cover more territory and be more careful in the parts they inspect individually. Team structure also helps in terms of lowering the free-riding and increasing the incentives for cooperative work. To capture this, I assume that a given worker $i$ divides her effort into two tasks: own work effort ($e_i$) and helping efforts ($h_i$). To capture the costs of effort, I assume that we have the following convex cost function $\dfrac{c}{2}(e_i^2 + h_i^2)$, where $c>0$ represent the changes in marginal costs of effort and help.

By the nature of the preventive care work, the policy outcome is probabilistic. Preventive healthcare aims to lower the chance of a person gets sick. For example, washing hands lower the chance of getting the flu, but from time to time, a person gets flu regardless of how many times she washes her hands. The only difference is that a person that washes hands constantly has a lower chance of getting sick and will get sick fewer times during her lifespan. For this reason, denote the probability of a successful provision of the service, by a pair $i$ and $j$ of healthcare workers, as $P(e_i, h_i, e_j, h_j)$. For simplicity, I assume that the probabilities are additively separable, with $P(e_i, h_i, e_j, h_j) = P_i(e_i, h_j) + P_j(e_j, h_i)$. To make the output more concrete, assume that a given worker $i$ has an individual probability of $P_i(e_i, h_j) = e_i(1+h_j)$ of successfully lower the disease burden with her effort ($e_i$) and the help of her peer ($h_j$).

From the perspective of the agency, the successful work grants a benefit of $B>0$. This benefit represents the social gains of lowering the disease incidence in the municipality. For example, the pay off could be the amount of money saved hospitalization or the economic benefit of fewer workers missing jobs due to diseases transmitted by the \textit{Aedes aegypti}. The agency incentivizes workers with salaries with three components: a flat salary without bonuses, individual compensation, and a bonus when the entire team achieves their collective objectives. These formulations allow me to disentangle which scheme gives the highest yield in terms of disease prevention.

The optimal scheme to improve welfare resumes into a contract where the governmental agency offers a compensation package, and the two healthcare providers choose effort accordingly. From the perspective of the worker, the expected utility of effort, provided that the compensation depends of the successful provision of the service, and that the benefit from salary is given by a concave function $u(.)$. For concreteness, I use the function $u(x) = \sqrt{x}$. The expected utility of effort is then the compensation for each scenario, times their probability. It is equal to:

\begin{eqnarray*}
    U_i(e_i, h_i; e_j, h_j) & = & P_i(e_i, h_j)P_j(e_j, h_i)u(s+w_{both}) + \\
    & & P_i(e_i, h_j)(1-P_j(e_j, h_i))u(s+w_{one}) + \\
    & & (1-P_i(e_i, h_j))P_j(e_j, h_i)u(s+w_{one}) + \\
    & & (1-P_i(e_i, h_j))(1-P_j(e_j, h_i))u(s) - \dfrac{c}{2}(e_i^2 + h_i^2)
\end{eqnarray*}

And this utility is symmetric for the worker $j$. To simplify things, consider that the compensation under an unsuccessful service provision is equal to zero: $u(s)=0$, or $s=0$. From the perspective of the governmental agency, the benefit from offering the compensation is equal to the social benefit in each provision scenario minus the compensation times the likelihood of the scenario:

\begin{eqnarray*}
    U_A(w_{both}, w_{one}, s; e_i, h_i, e_j, h_j) & = & P_i(e_i, h_j)P_j(e_j, h_i)(2B - 2w_{both}) + \\
    & & P_i(e_i, h_j)(1-P_j(e_j, h_i))(B-2w_{one}) + \\
    & & (1-P_i(e_i, h_j))P_j(e_j, h_i)(B-2w_{one})
\end{eqnarray*}

The problem is a standard contract theory problem, where we have three compensation packages: no bonus ($w_{both} = w_{one} = 0$), individual bonus ($w_{both} = w_{one} \neq 0$), and collective bonus ($w_{both} \neq w_{one}$, $w_{both} \neq 0$, and $w_{one} \neq 0$). The optimal contract is then the solution for the following constrained optimization problem:

\begin{eqnarray*}
    \max_{w_{both}, w_{one}} U_A(w_{both}, w_{one}; e_i, h_i, e_j, h_j) \text{, subject to:} \\
    & (e_i, h_i) \in \arg \max U_i(e_i, h_i; e_j, h_j, w_{both}, w_{one}) \\
    & (e_j, h_j) \in \arg \max U_j(e_j, h_j; e_i, h_i, w_{both}, w_{one})
\end{eqnarray*}

And by choosing an optimal compensation scheme, the agency can induce more effort and more cooperation among workers.

\subsection{Baseline: no incentive bonuses}

When the agency only pays a flat salary without performance incentives, the agency sets the performance compensation equals to zero: $w_{both} = w_{one} = 0$. This changes the expected utility of the agent into the following:

\begin{eqnarray*}
U_i(e_i, h_i; e_j, h_j) & = & - \dfrac{c}{2}(e_i^2 + h_i^2)
\end{eqnarray*}

In this setting, exerting effort generates only costs and no benefits. The agents exert zero effort and help in equilibrium: $e_i^* = e_j^* = 0$ and $h_i^* = h_j^* = 0$. The agency pays the minimum wage accepted by law, and in this chapter, I assume that this wage is equal to zero. Accordingly, the agency expected benefit is equal to:

$$ R_A(\text{no bonus}) \ = \ 0$$

The prediction here is that workers will exert no effort, and the agency will have only costs without accruing any benefit. This is the worst-case scenario in terms of the agency's welfare. In the experiment, it matches with the control condition.\footnote{Throughout the paper, I assume that the optimal output for the agency is equal to the welfare-maximizing for the society. Although this is not always the case, it is a reasonable simplification for the chapter purposes. Adding a difference in here would only complicate my results, providing no further insights into designing an incentive scheme to maximize welfare.}

\subsection{Performance bonus for individuals}

When the benefits are tied to the individual performance, the governmental agency compensates the workers for their effort, without tying their bonuses with helping other workers. This means that $h_i^* = h_j^* = 0$, but the optimal level of effort is always positive. Let $\alpha$ the bonus that the governmental agency offers to the workers conditional on lowering the disease incidence. Each work then evaluates the utility of the bonus as $u_i(\alpha) = \sqrt{\alpha}$, as the utility of the agent is concave, representing the risk aversion of the agent. The optimization problem, from the perspective of the agent, is to maximize her expected utility, given the bonus offered by the governmental agency upon achieving a successful provision:

\begin{eqnarray*}
\max_{e_i} U_i(e_i) & = & \max_{e_i} \left[P_i(e_i, 0)\sqrt{\alpha} - \dfrac{c}{2}(e_i^2)\right] \\
 & = & \max_{e_i} \left[e_i\sqrt{\alpha} - \dfrac{c}{2}(e_i^2)\right]
\end{eqnarray*}

Both workers face the same incentive structure, so the equilibrium is symmetric, with $e_i = e_j$. Taking the derivative, and equating it to zero, gives us the following optimal effort level: $e_i^* = e_j^* = \dfrac{\sqrt{\alpha}}{c}$. The optimal level of effort represents when the marginal benefit from the governmental agency compensation is equal to the marginal cost of effort. The benefit of a successful provision of the healthcare services is equal to, for both players, the total benefit times the chance of a successful provision, times the difference between the benefit accrued from a successful provision minus the bonus paid for the worker. To compute the optimal contract that the governmental agency have to offer in this setting, we have to choose $\alpha$ to maximize the agency's expected utility:

\begin{eqnarray*}
\max_{\alpha} R_A(e_i^*(\alpha), e_j^*(\alpha)) & = & \max_{\alpha} \left[2 \dfrac{\sqrt{\alpha}}{c} (B-\alpha)\right]
\end{eqnarray*}

The optimal bonus is equal to $\alpha^* = \dfrac{B}{3}$. Plugging the optimal bonus and the optimal effort levels in the welfare function, we find the agency's expected revenue, which in this case is equal to:

$$ R_A(\text{individual bonus}) \ = \ \dfrac{4}{c} \left[ \dfrac{B}{3} \right]^\dfrac{3}{2} $$

The revenue is always greater than zero, provided that the costs of investing effort and the social benefits of the policy are greater than zero.

\subsection{Performance bonus for teams}

When the governmental agency sets rewards for both the individual and the peer performance, healthcare workers divide their time between effort in their job ($e_i$) and help peers get their job done ($h_i$). Helping may take many forms: from simple peer pressure and monitoring to ensure the peer is doing the job well to divide tasks and exploit complementarities in their duties efficiently. From the governmental agency's perspective, incentivizing workers to help each other can potentiate the chances of getting a successful service provision. From the standpoint of the healthcare workers, the optimal effort becomes a mix of her own efforts and the helping efforts that maximize her expected utility, provided that both efforts are incentive-compatible. Incentive compatible means, in the case of healthcare workers, that both efforts are exerted to match the governmental agency's contractual incentives. The expected utility for the agent $i$ consists of the chance of getting bonus times the utility of the bonus. This iterated in each of the possible service provision scenarios.

\begin{eqnarray*}
\max_{(e_i,h_i)} U_i(e_i, h_i; e_j, h_j) & = & \max_{(e_i,h_i)} \{e_j(1+h_i)e_i(1+h_j)u(w_{ij}) + \\
& & e_j(1+h_i)(1-e_i(1+h_j))u(w_{j}) + \\
& & e_i(1+h_j)(1-e_j(1+h_i))u(w_{i}) - c\dfrac{e_i^2+h_i^2}{2}\}
\end{eqnarray*}

Again, both players are ex-ante similar in terms of their expected utilities. This allows me to solve for the Symmetric Nash Equilibrium, where:

\begin{enumerate}
    \item The effort of a given healthcare provider ($i$) is equal to the effort of the other healthcare provider ($j$): $e_i = e_j = e$.
    \item The help of one healthcare provider is equal to the help of the other healthcare provider $h_i = h_j = h$.
    \item Both agents have the same utility function, $U_i(.) = U_j(.)$.
\end{enumerate}

Maximizing the expected utility leads us to the optimal effort and help for the healthcare provider, given the contractual scheme. The optimal provision have to satisfy the following equation:

\begin{eqnarray*}
\dfrac{\partial U}{\partial e} & = & e(1+h)^2(u(w_{ij})-u(w_{i})-u(w_{j})) + (1+h)u(w_{i})-ce \\
\dfrac{\partial U}{\partial h} & = &
e^2(1+h)(u(w_{ij})-u(w_{i})-u(w_{j})) + eu(w_{j})-ch
\end{eqnarray*}

To simplify our computation, we consider contracts that vary in one dimension $\alpha$. The individual part of the contractual benefit is equal to multiples of this contract for each situation: own successful provision and the successful colleague provision.

In this example, we restrict our attention to contracts where $u(w_{i}) = u(w_{j}) = \sqrt{\alpha}$ and $u(w_{ij}) = 2u(w_{i})$. These contracts match better the conditions I set in the experiment: they represent the collective gain when recompensing the agent for peer and individual successes. The optimal effort and help becomes $e_i^* = e_j^* = \dfrac{\sqrt{c\alpha}}{c-\alpha} $ and $h_i^* = h_j^* = \dfrac{\alpha}{c-\alpha}$. The governmental agency now maximizes the bonus for the individual provision ($\alpha$), given that the collective provision is higher than it. In the appendix, we solve for contracts that vary in both dimensions. The expected revenue of the agency is equal to the chance of lowering the disease burden times the benefit minus costs of pay the healthcare provider's salaries:

\begin{eqnarray*}
\max_{\alpha} R_A(e_i^*(\alpha), h_i^*(\alpha), e_j^*(\alpha), h_i^*(\alpha)) & = & \max_{\alpha} \left[2 \dfrac{c\sqrt{c\alpha}}{(c-\alpha)^2} (B-2\alpha)\right]
\end{eqnarray*}

The derivative of this equation is the polynomial in the second degree in $\alpha$. By the intermediate value theorem, it is easy to see that it has one solution for $\alpha \in [0, B]$. To illustrate, consider the Figure \ref{figrevmax}, where I plot the expected revenue for the agency ($R_A(\alpha)$), as a function of the offered compensation $\alpha$, and the three types of contract: no productivity incentives, individual productivity incentives, and peer productivity incentives, fixing $B = c = 1$.

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figures/figrev.pdf}
\caption{Governmental Agency's Revenue in terms of Contract and Compensation}
\label{figrevmax}
\end{figure}

Therefore, the maximum benefit that the agency can achieve is higher when the agency compensates the workers for their cooperation. When the agency incentivizes the team effort, workers can on margin do better by sharing the benefit of a successful provision.\footnote{The limits for this reasoning appear when there are gains of specialization. For instance, if the costs for effort and help were such that $\dfrac{c(e+h)^2}{2}$, then diverting energy for help is costly, on margin at the same rate as the given effort provision. In this case, the compensation to stimulate cooperation has to be significantly higher, and even in this case there will be incentives for not cooperate.}

\section{Experimental Design}

In this section, I present the experimental design. I explain the intervention stages: the municipality selection, and the recruitment and training of the subjects. Then, I discuss the intervention, explaining the treatment delivery and the randomization. Finally,  I discuss the performance measurements and the municipality disease information. Although I focus only on the main details here, the Supplementary Materials in Appendix A discusses all the data in depth.

\subsection{Pre-treatment}

There were three crucial steps taken in the pre-intervention stage: municipality selection, recruitment and training, and the randomization.

In terms of municipality selection, I ran the experiment in the municipality of Rio Verde, in the State of Goias. Rio Verde is the fourth-largest municipality in the state, comprised of 229 thousand inhabitants. Its income comes chiefly from soybean exports and other agricultural produce.

In 2018, the municipality experienced a substantial increase in dengue fever cases. Among the towns I had an agreement to run the experiment, Rio Verde experienced the most substantial disease occurrence.\footnote{I had the authorization to run the experiment in Bauru and Ribeirao Preto, both in the Sao Paulo State. However, these municipalities had a very low case incidence from January to March 2018: 8 and 142.}

I used a Facebook ad to recruit potential participants in the municipality. The ad redirected participants to a Google Form that requested information about the participant and an e-mail address. Using the e-mail address, I send a Qualtrics survey with pre-treatment demographic questions. Upon completion, I sent them the date and timing for the training session held on May 4, 2018.

During the training session, my research assistants and I presented the \textit{Aedes aegypti} vector's biology and how it transmits the diseases. The meeting also taught participants how to find and exterminate the mosquito breeding sites. Participants then had to read and sign the informed consent to participate in the research.

The intervention happened the following day (May 5). After the final training meeting, I performed the randomization and directed participants to their working headquarters based on the randomization status. There was around 50 percent of attrition from the registration to the main intervention participants. Table \ref{tabcovbal1}, Panel A displays the attrition tests, Panel B presents the balance tests for the participants' demographics, and Panels C and D the territorial assignment before and after the matching on census-sector characteristics.

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Sat, Feb 01, 2020 - 17:56:00
\begin{table}[!htbp] \centering 
  \caption{Covariate Balance on Individual Characteristics} 
  \label{tabcovbal1} 
\begin{tabular}{@{\extracolsep{5pt}} lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & Attrition & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
& & \multicolumn{5}{l}{Panel A: Attrition pattern test} \\
\hline \\[-1.8ex]
Age &  26.17 & 25.04 & 26.07 & 26.00 & 0.461 & 0.710 \\ 
Female &   0.72 &  0.79 &  0.79 &  0.74 & 0.805 & 0.492 \\ 
Has Vehicle &   0.35 &  0.27 &  0.37 &  0.37 & 0.651 & 0.582 \\ 
N & 341 & 73 & 71 & 73 &  &  \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc} 
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel B: Covariate balance on individual characteristics} \\
\hline \\[-1.8ex]
Altruist &  0.63 &  0.68 &  0.62 & 0.239 & 0.788 \\ 
Age & 25.01 & 26.00 & 26.90 & 0.754 & 0.472 \\ 
Religiosity &  0.53 &  0.38 &  0.45 & 1.487 & 0.228 \\ 
Pol. Engagement &  0.69 &  0.65 &  0.68 & 0.163 & 0.849 \\ 
Soc. Engagement &  0.59 &  0.62 &  0.67 & 0.454 & 0.636 \\ 
Above 2 Min. Wage &  0.34 &  0.35 &  0.29 & 0.336 & 0.715 \\ 
FB Popularity &  0.53 &  0.56 &  0.58 & 0.175 & 0.840 \\ 
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel C: Unmatched Covariate balance on territorial assignment} \\
\hline \\[-1.8ex] 
Number of Houses & 276.41 & 243.58 & 255.20 &  2.368 & 0.098 \\ 
Number of Households & 885.67 & 750.34 & 785.18 &  3.765 & 0.026 \\ 
Avg. Household Size &   3.21 &   3.07 &   3.07 &  6.566 & 0.002 \\ 
Log Avg. Income &   6.47 &   6.86 &   6.85 &  9.213 & 0.000 \\ 
Cases Before Treatment &  13.78 &   5.94 &   4.66 & 15.638 & 0.000 \\ 
\hline \\[-1.8ex] 
& \multicolumn{5}{l}{Panel D: Matched covariate balance on territorial assignment} \\
\hline \\[-1.8ex] 
Number of Houses & 276.41 & 282.04 & 281.19 & 0.068 & 0.935 \\ 
Number of Households & 885.67 & 903.04 & 900.39 & 0.060 & 0.942 \\ 
Avg. Household Size &   3.21 &   3.21 &   3.20 & 0.008 & 0.992 \\ 
Log Avg. Income &   6.47 &   6.45 &   6.45 & 0.084 & 0.920 \\ 
Cases Before Treatment &  13.78 &  10.24 &  10.77 & 1.443 & 0.240 \\ 
\hline
Pairs & 34 & 34 & 35 &  &  \\ 
N & 68 & 68 & 70 &  &  \\
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

There were no distinct patterns on the attrition, reinforcing that it was at random. The participants' demographics are similar across the treatment status, and the matching successfully balanced the territorial assignment.

\subsection{Intervention}

I assigned participants to three types of monetary incentives: a no-performance bonus (control group), an individual performance bonus (individual treatment), and a peer performance bonus (collective treatment).

Before the primary intervention, I run a pilot three weeks earlier with twenty participants to measure the applicability of the experiment, and to calibrate the data collection. In the pilot, I find that participants could visit around sixty households during the intervention day. This is because about one-third of houses were generally empty, and the yards in the municipality are usually small, facilitating the work.

The intervention started around 11:00 AM and ended around 6:00 PM on May 5, 2018. To avoid spillover, I divided the participants into three different headquarters, away from each other, and each was applying a different treatment. The intervention was delivered around 10:30 AM after participants had received their monitoring cellphones and their working kits. The head research assistant told the participants collectively the information of each treatment status. In a one-on-one discussion, the research assistants reinforced the treatment for each of the pairs. The treatment delivery follows below:

\begin{itemize}
    \item In the control group, we told participants that we would measure their performances in the field. We also told them that the bonus would be assigned without a performance assessment.
    \item In the individual treatment group, we told participants that we would measure their performances in the field. We explained that we would rank the individual performances, and anyone reaching performance above the median would double their compensation.
    \item In the collective treatment group, we told participants that we would measure their performances in the field. I explained that I would rank the team performance, which was the sum of both participant's performances, and teams reaching performance above the median would double their compensation.
\end{itemize}

The field compensation was BRL 110.00. The participants that successfully doubled it received BRL 220.00. Each participant within a headquarter was paired randomly with another participant. The pairs received a leaflet with a map of the area they should cover. The route was comprised of two to three blocks, containing around 120 houses. The blocks were within a census sector, to facilitate the use of census data afterward.

A typical visit to a household consisted of the following steps. First, the participants' ring the doorbell in the house and explained that the municipality was experiencing a dengue fever outbreak.\footnote{Despite the widespread news coverage of Zika in the US, people have little knowledge about it in Brazil. Dengue, on the other hand, has news coverage in Brazil since the 1980s. In Brazil, the \textit{Aedes aegypti} is referred by households as the Dengue mosquito.} They instructed dwellers on how to lower the disease incidence, protect their families, and handed in a leaflet with information about it.

Then, they requested households to enter their houses and inspect their yards. When granted permission, they had to check the yard to find clean breeding sites and exterminate larvae. Upon cleaning a breeding site, they had to report it with their cellphones by taking a picture. When they discovered larvae, they had to record a video with the larvae before exterminating it. At the end of their visit, they had to take a picture of the household, to account for their presence in the place.

\subsection{Post-treatment}

After the treatment takes place, I computed the performance in the field by counting the number of houses visited, the number of breeding sites discovered and eliminated, and the number of larvae exterminated. The information comes from the cellphones used by participants in the intervention. I had research assistants cleaning the pictures to ensure that all the images reported houses or breeding sites and that all videos were from larvae. Based on the photos and videos, I computed the performance for each participant and paid the bonus according to the treatment status assigned to the person.

In the months that followed the intervention, I requested the mayor's office the reports on the disease incidence of dengue fever, from January to September 2018. In this dataset, I have the hospitalization of every person in the municipality that had Dengue fever during the period. Using the dataset, I georeferenced all the cases in the city. Moreover, as this is sensitive healthcare information, protected by the Brazilian law, they agreed to provide it only one year after the intervention. I stored the data safely and encrypted, as it has addresses, full names, social security numbers (Brazilian CPFs), and other sensitive personal information.

\section{Results}

I measure two performance outcomes: field productivity and disease incidence. The field productivity consisted of the cellphone data collected by the subjects during the intervention. The disease incidence comprised data collected by the mayors' office with hospital treatment of people that presented symptoms of dengue fever from January to September 2018. Below, I discuss how the experiment affected each of these outcomes.

\subsection{Field productivity}

For the field productivity, I have four indicators. First, the number of houses visited. Second, the number of homes visited in less than two minutes. Third, the number of breeding sites removed and cleaned. Finally, the number of larvae exterminated. The results follow in Table \ref{prodregs}.

\begin{table}[!htbp] \centering 
  \caption{Field Productivity} 
  \label{prodregs} 
\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\ 
& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\ 
\hline \\[-1.8ex] 
 Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\ 
  & (4.906) & (4.018) & (5.251) & (0.058) \\ 
  & & & & \\ 
 Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\ 
  & (4.428) & (3.571) & (4.049) & (0.076) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
Observations & 197 & 197 & 197 & 197 \\ 
Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{Robust standard errors in parentheses. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

Incentivized workers visit fewer households than non-incentivized workers. This result may be counter-intuitive, but the performance incentives reward more the participants that exterminate larvae and cleaned breeding sites, instead of just visiting households. In the control group, they had no incentives to do a thorough job, but they were still instructed to cover all the territory to receive compensation. Non-incentivized teams had only the incentives to take pictures of houses, regardless of their actual commitment to visit a home and exterminate breeding sites and larvae. For instance, the number of household pictures taken two minutes apart from each other was -8.04 and -6.48 lower in the incentivized individual and collective bonus groups than in the control group. Visit a household in two minutes means that, either the house was empty, or that the pair decided not to visit the home. In both cases, the house yard was not inspected.

However, incentivized teams find and clean more breeding sites than non-incentivized ones. On average, the individually incentivized workers find 25.1 and 21.5 more breeding sites than the non-incentivized control group. The workers in the collective bonus treatment cleaned on average 50\% more breeding sites than the control group. Breeding sites are relatively easy to find and require just a careful work in the yard. Almost any recipient that can hold seated clean water can be a breeding site. Moreover, many people leave plant plates filled with water, and simple instructions to fill up the plate with sand can help terminate a breeding site.

Collective incentivized teams are more effective in finding larvae. In our study, collectively incentivized subjects have 16.3\% more chance to find larvae than non incentivized workers. Finding larvae is harder, and the detection chances profit from teamwork. If teams are cooperating, searching the house becomes more natural, and they can coordinate to do a more thorough job. Additionally, the detection tends to be excludable: one individual finding larvae makes the chances of keep finding larvae in the household considerably smaller. Collective bonus is not excludable within the teams, making them cooperate more to get the reward.

Monetary incentives work. Incentivized workers visit fewer households, but do a considerably better job in the houses they go to. Also, the excludability of the benefits seems to make individually incentivized workers more prone to search for breeding sites. Non-excludability of the bonus makes workers more inclined to search for larvae, which are considerably harder to find. They still search for breeding sites in the process but focusing more on finding larvae, as it was more rewarding.

\subsection{Disease Incidence Outcomes}

To evaluate the effect of the treatment on the disease incidence, I run two models. The first model is a differences-in-differences model to assess whether the intervention per se had any effect. The second model compares the disease incidence in each of the treatment statuses with the disease incidence in the control group. In both of the models, the unit of analysis is the census sectors.

In the first model, I look into the disease outcomes in a given time-window, using a differences-in-differences approach. The treatment status represents any of the interventions against a pure-control of households not visited. I chose four windows around the treatment: full data, which comprises 16 weeks around the treatment; 12 weeks around the treatment; eight weeks around the treatment; and four weeks around the treatment.\footnote{The treatment was carried out on the last day of the 17th week of 2018.} Also, to evaluate the differences between individual and collective bonuses, in the last column, I ran a differences-in-differences with the collective treatment as the main intervention, and the individual treatment the control. Table \ref{difindifdiseases} displays the results.

\begin{table}[!htbp] \centering 
  \caption{Disease Incidence -- Differences in Differences Model} 
  \label{difindifdiseases} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (indv. x collect.) \\ 
\hline \\[-1.8ex] 
 DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:} & \multicolumn{5}{r}{DID stands for the Differences-in-Differences estimator.}
& \multicolumn{5}{r}{Robust standard error, clustered at the Census-Sector level, in parenthesis.} \\ 
& \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

When comparing any treatment with no treatment, the experiment lowered the incidence of diseases in 10.3\%. The result is consistent around fewer weeks before and after the intervention, but it is not significant. This suggests that the effect is small and weak. Figure \ref{figc360daysdiseaseinc} illustrates the differences in disease incidence using a 60 days window before and after the intervention. The Figure shows a consistent reduction in the disease incidence, which is compatible with the 10.3\% reduction estimated in the differences-in-differences model.

\begin{figure}
\includegraphics[width=\textwidth]{figures/c3diseaseincidence60dw.pdf}
\caption[Disease incidence.]{Disease incidence 60 days around the treatment.\label{figc360daysdiseaseinc}}
\end{figure}

The differences in differences comparing the two primary treatment statuses show an impact of 2.9\% fewer infections in the collective bonus group. However, the result is not significant at standard significance levels.

In the second model, I look into the number of hospitalized households in each of the census sectors, based on the treatment status of pairs working in the census sector. Table \ref{regdiseaseinc1} shows the hospitalizations before the intervention, and then 15, 30, 60, 90, and between 15 to 30 days after the treatment.

\begin{table}[!htbp]
  \caption{Disease incidence in Rio Verde census sectors} \centering 
  \label{regdiseaseinc1} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & Before & 15 days & 30 days & 60 days & 90 days & 30-60 days \\ 
& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
\hline \\[-1.8ex] 
 Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
  & & & & & & \\ 
 Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
  & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{Robust Standard Error in Parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular} 
\end{table}

Compared with the control group, no treatment had a practical influence on the disease incidence in the Rio Verde Census sectors. However, the coefficients tend to be negative, which suggests that should an impact have occurred, the intervention would have probably had lowered the disease incidence.

Why does increased productivity not causes fewer hospitalizations? First, the disease epidemiology suggests that finding a breeding site does not directly imply that all the larvae were exterminated. Although it becomes harder to find, and in our sample, no worker (or pair) found two larvae in the same house, finding a larvae container guarantee that there was a mosquito in a 70 meters radius. The mosquito could have laid eggs anywhere around this perimeter, but it becomes harder to detect. Second, the municipality had a significant incidence of the disease, reaching 3,411 reported infections from January to September. It can be that any efforts in this period only generate a consistent effect when it is above some threshold level. For example, a disease such as measles only become eradicated by herd immunity when the vaccination reaches around 95\% of the population \citep{fox1983herd}. For having the same effect, it could be that I had to assemble a team to visit around 90\% or more of the households. Lastly, our intervention could have affected hospitalizations, increasing hospital admissions around the treated area: remember that the first step in visiting a house was to explain they should go to a doctor upon having any of the symptoms. This is a competing effect, as the number of infections decreases because of the intervention, but the reports for the hospital increase, offsetting the impact.

\section{Discussion}

This paper shows that performance monetary incentives increase the productivity of community healthcare workers in Brazil. Studying the context of \textit{Aedes aegypti} prevention, I contrast three types of contractual incentives: no performance rewards (control group), individual bonus for the most productive workers in the field (individual treatment), and peer reward, to the more productive pairs in the intervention (collective treatment). I find that collective incentives perform better when the job is harder and needs cooperation. Finding mosquito larvae is difficult, and detection by one person virtually excludes the other from the benefit. When the bonus is shared, the pairs collaborate more, and this makes finding larvae easier. On the other hand, individual incentives are better to improve the detection of more accessible but essential to work on, such as cleaning breeding sites. Finally, the control group presented a high incidence of houses visited in less than two minutes apart from each other, which suggests that the workers may cheat without incentives and not perform their jobs accordingly.

The findings here are significant for policy-making. First, I show that performance bonus work also in public healthcare. Although it is known for education \citep{Dufloetal2012} and collective workers in the private sector \citep{Ashrafetal2014a, Ashrafetal2014c}, this is one of the first attempts to study peer incentives for workers performing a public service job. Second, the collective bonus outperforms individual performance rewards when the task is more laborious and excludable. The excludability of the benefit and the difficulty of the task makes cooperation among team workers beneficial to accomplish the job. Finally, as the epidemiology of vector-borne diseases is involved, to enhance productivity to translate into significant effect, I would need a vast pool of workers in the same way as herd immunity works. This teaches us that improve public service provision is challenging, even when the workers perform their tasks effectively.

\clearpage

% Bibliography
\singlespacing
\begin{footnotesize}
\bibliographystyle{chicago}
\bibliography{biblio.bib}
\end{footnotesize}

\clearpage

\appendix

\section{Appendix Content}

In the appendix, I present the APSA Experimental Session Standard Report. This report has all the details on the experiment, and also has additional field information and pictures. In the report, there is the following information:

\begin{enumerate}
    \item Hypothesis
    \begin{enumerate}
        \item Question addressed by the experiment
        \item Hypothesis tested
    \end{enumerate}
    \item Subjects and Context
    \begin{enumerate}
        \item Eligibility and Exclusion Criteria
        \item Recruitment Information
        \item Training Information
    \end{enumerate}
    \item Allocation methods
    \begin{enumerate}
        \item Randomization procedures and details
        \item Pre-treatment balance checks
        \item Details on random assignment and treatment administration
    \end{enumerate}
    \item Treatment descriptions
    \item Results
    \begin{enumerate}
        \item Analysis of outcomes
        \item CONSORT
    \end{enumerate}
    \item Other information
    \begin{enumerate}
        \item NYU IRB
        \item Funding
        \item Pre-registry
        \item Field research assistants thanks note
        \item A few pictures of the field
    \end{enumerate}
\end{enumerate}

\end{document}

### 2020-10-08 paper/second-version.tex
first commit

\documentclass[a4paper, 12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[super]{nth}
\usepackage{libertine}
\usepackage{setspace}
\usepackage{color, graphics, graphicx}
\usepackage[libertine]{newtxmath}
\usepackage[scaled=.95]{inconsolata}
\usepackage{underscore, lscape, dcolumn, arydshln}
\usepackage[usenames, svgnames, dvipsnames]{xcolor}
\usepackage[sharp]{easylist}
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage[font=small, format=plain, labelfont=bf,up, textfont=it,up]{caption}
\usepackage[pdftex, 
            plainpages=false,
            pdfpagelabels,
            pagebackref=false,
			colorlinks=true,
			citecolor=Mahogany,
			linkcolor=Mahogany,
			urlcolor=darkblue,
			filecolor=darkblue,
			bookmarksopen=true]{hyperref}
\usepackage{tabularx}
\usepackage[para, online, flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{natbib}
\usepackage{subcaption, rotating}
\usepackage{pgf, tikz, pgfplots, mathrsfs}
\usepackage[brazilian, UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon
\setcitestyle{aysep={}}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
   {\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother

\usetikzlibrary{positioning,arrows,calc,fit}
\pgfplotsset{compat=newest}
\definecolor{wrwrwr}{rgb}{0.38,0.38,0.38}
\definecolor{rvwvcq}{rgb}{0.08,0.38,0.75}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\tikzset{
block/.style={
  draw,
  rectangle,
  minimum height=1.5cm,
  minimum width=3cm, align=center
  },
line/.style={->,>=latex'}
}
\tikzset{container/.style={draw, rectangle, dashed, inner sep=1.5em}}
\bibpunct{(}{)}{;}{a}{}{,}
\pagestyle{plain}
\renewcommand{\arraystretch}{1.2}
\sloppy

%\renewcommand{\thepage}{}
\renewcommand{\bibname}{References}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand{\wh}[1] {\widehat { #1 }}

\newcommand{\twopd}[4]{\left\{\begin{array}{ll} #1 & \text{if } #2 \\ #3 & \text{if } #4 \end{array} \right.}

\newcommand{\twopdo}[3]{\left\{\begin{array}{ll} #1 & \text{if } #2 \\ #3 & \text{otherwise} \end{array} \right.}

\newcommand{\threepd}[6]{ \left\{ \begin{array}{lll} #1 & \text{if } #2 \\
#3 & \text{if } #4 \\ #5 & \text{if } #6 \end{array} \right.}

\newcommand{\threepdo}[5]{ \left\{ \begin{array}{lll} #1 & \text{if } #2 \\
#3 & \text{if } #4 \\ #5 & \text{otherwise} \end{array} \right.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\doublespacing

\title{Individual and Collective Incentives for Preventive Healthcare Provision: \\ Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil\thanks{We thank XXXX , and participants at the MPSA, NYU PE Seminar, and SPSA for their valuable comments. Special thanks to XXXX for their excellent research assistance. Replication materials are available at \url{http://github.com/XXXX/XXXX}.}}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, USA, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{http://danilofreire.github.io}.} 
\and Umberto Mignozzetti\thanks{Visiting Assistant Professor, Department of XXXX, Emory University, XXXXX.}}

\date{\today}

\begin{document}
\maketitle

% \renewcommand{\abstractname}{Summary}
% MUST INCLUDE primary outcome expressed as the difference between groups with
% a confidence interval on that difference (absolute, not relative).
\begin{abstract}
\noindent
\begin{itemize}
  \item \textbf{Background}:
	\item \textbf{Methods}: We run a field experiment to assess the impact of financial incentives on the productivity of health care workers in Rio Verde, Brazil.
	  %[] The trial was pre-registered through EGAP, by the number 20180504AA and is available \hyperlink{https://osf.io/zpyfm}{here}.
    \item \textbf{Findings}:
	\item \textbf{Interpretation}:
    \item \textbf{Funding}: Getulio Vargas Foundation.
\end{itemize}
\end{abstract}

\newpage

\section{Introduction}

The \textit{Aedes aegypti} mosquito species is the major vector of
several arboviral diseases worldwide, including dengue, yellow fever, Zika, and
chikungunya \citep{burt2012chikungunya, jansen2010dengue, leta2018global,
thangamani2016vertical}. Over the past 30 years, arboviral incidence has
increased exponentially, with estimates suggesting that dengue is endemic in
around 100 countries, causing 400 million infections and 22 thousands deaths
each year \citep{bhatt2013global, cdc2020dengue, musso2018unexpected}. Since
there are no safe vaccines for most \textit{A. aegypti}-transmitted diseases
\citep{sridhar2018effect, world2017dengue}, we have seen a number of recent
dengue and Zika outbreaks in Asia, the Caribbean, South America, and the United
States \citep{carlson2016ecological, leta2018global}. Chikungunya virus, which
was endemic only to Africa, has already been reported in every region of the
world \citep{grandadam2011chikungunya, kraemer2015global, mayer2017emergence,
sourisseau2007characterization}.

Mosquito control is the primary strategy to prevent \textit{A.
aegypti}-borne infections \citep{beatty2010best, eisen2009proactive,
ooi2006dengue}. The World Health Organization recommends the elimination of
containers and the use of insecticide to reduce vector breeding, specially in
settings where human-vector contacts are frequent, such as schools, hospitals,
and workplaces \citep{WHO2012global, world2020denguecontrol}. However,
cleaning breeding sites and insecticide spraying are labour-intensive processes
and are often carried out inconsistently \citep{paz2015dengue, siddiqui2016use,
WHO2012global}. In most endemic countries, local governments are the main
responsible for providing vector control, thus increasing their productivity is
crucial to the effectiveness of anti-mosquito programmes worldwide.

Financial incentives are important determinants of worker performance in
public and private organisations \citep{burgess2003role}. While studies
indicate that reward schemes may improve the productivity of health care
providers \citep{basinga2011effect, flodgren2011overview,
miller2012effectiveness, ulrich2005does}, it is unclear how they affect the
motivation of workers fighting \textit{A. aegypti}. Moreover, there is no
evidence about the impact of financial incentives on patient-level arboviral
outcomes, such as virus-related hospitalisations or disease incidence
\citep{flodgren2011overview}.

To explore how monetary incentives affect health worker motivation and patient
outcomes, we run a randomised field experiment in the city of Rio Verde, Brazil,
which has experienced a peak in dengue infections in the last years. We hired
and trained teams of health care workers to perform simplified procedures
designed to exterminate \textit{Aedes aegypti} breeding sites. Our experiment
consists of two treatment arms plus a control condition. The control group
received a fixed compensation for completing their task, and we offered
individual or collective bonuses to those allocated in the two treatment groups.
We then measured the impact of the compensations schemes on the number of
breeding sites discovered, larvae exterminated, and city-level dengue incidence
30, 60, and 120 days after our intervention.

We find that monetary rewards increase the number of cleaned breeding sites in both
treatment conditions (individual and team bonuses) and collective financial
incentives also improve larvae extermination. Our results show that the
control group has a high incidence of houses visited in less than two minutes
apart from each other, which suggests that workers may cheat in the absence of
financial incentives. When we combine both treatments, we also find that the
intervention decreases dengue incidence in 10.3\%, but the results are not
robust. In summary, we provide experimental evidence that performance bonuses
increase productivity in public service delivery and that small financial
incentives to health workers may improve patient outcomes and reduce
hospitalisation costs in \textit{Aedes}-endemic countries.

\tikzstyle{box1} = [rounded corners, rectangle, draw = black, thin,
fill=red!65!blue!20, text width = 15cm, minimum height = 3.7cm]

\begin{figure}
    \centering
    \label{box:context}
\begin{tikzpicture}
 \linespread{1.0}
\node (context) [box1] {\textbf{Research in Context}
\footnotesize
\begin{itemize}
    \item \textbf{Evidence before this study}: Controlling the spread of Aedes-borne diseases is a matter of public policy, wherein healthcare systems and communities must collaborate in performing preventive practices. The terms and procedures of this cooperation are not yet consolidated, as a number of collective action problems interpose. A number of trials testing chemical and mechanical extermination of adult mosquitoes show they are inefficient, and aiming at breeding sites consistently produces better results. The main unresolved issue surrounds the fact that controlling this type of vector requires sustained local-level practices by ordinary people, who demand constant monitoring by health agents.
    \item \textbf{Added value of this study}: We bring novel insight by investigating how to increase the productivity of the workers who link health agencies to the general population. We find teams of health workers respond to performance-based compensation with better quality of work, which should lead to lower infection rates.
    \item \textbf{Implications of all the available evidence}: Our results bridge the gap between the definition of appropriate strategies to control viral epidemics, and how to execute them efficiently. Increasing incentives can improve policy implementation, optimising public investment by lifting clinic treatment burdens from healthcare systems. Our conclusions transpose \textit{Aedes}-borne diseases, and the evidence we present can guide any policy that depends on unskilled health service provision.
\end{itemize}};

\end{tikzpicture}
\end{figure}

\section{Methods}

\subsection{Study design and clusters}

%% Rewrite: should we talk about design here? The subsection only mentions location. And we don't have clusters, do we?

We conducted the experiment at the participant level, conducted in the municipality of Rio Verde, in Brazil. Rio Verde is the fourth-largest town in the state of Goias, with a population of about 229,000. Out of the potential cities that could host the experiment, Rio Verde experienced the most substantial disease occurrence. The pre-analysis plan is available \hyperlink{https://osf.io/6q8vu/}{here}.

\subsection{Study population}

%%% Rewrite: reduce redundancy with the Results section

We used Facebook advertisements to recruit potential participants in the municipality. The advertisements directed applicants to a Google Forms web page which requested their contact information. We sent a pre-treatment demographic questionnaire to the applicants who provided a valid email address. At this stage, we excluded all individuals under 18 years old. We invited the remaining applicants to our training sessions. Those who did not attend the session were also excluded from the study. Lastly, we also excluded participants who did not complete their tasks in the field experiments. Together, all these steps reduced our original sample in 45.8\%.

We received IRB approval from the New York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). Health care workers gave written consent for participation in the experiment upon filling the Qualtrics survey. During the intervention, the occupants of households inspected for breeding sites and larvae gave oral consent.

\subsection{Randomisation and masking}

We assign participants to three types of monetary incentives: flat compensation regardless of performance (control group), an individual performance bonus (individual treatment), and a peer performance bonus (collective treatment). We allocate the subjects using block randomisation applied on seven variables included in the pre-intervention survey.

We use propensity score matching to weight according to census data. % Rewrite and include in the previous paragraph.

Participants were randomised upon completion of the training session and attendance on intervention day. To avoid spillovers, we direct them to three separate headquarters (HQs), one for each treatment. The experiment is single-blinded, as participants were aware that other groups of workers were in action, but unaware of the differences between their compensation scheme (treatment) and others'. % Rewrite to change verb tenses to present tense, if possible.

\subsection{Procedures}

The intervention started around 11:00 AM and ended around 6:00 PM on the 5th of May, 2018. The treatment was delivered at around 10:30 AM after participants had received their monitoring cellphones and working kits.\footnote{Participants had attended a training session the day before (May 4, 2018), where they were instructed on how to perform measurements and use the equipment. They were also briefly educated on the biology of \textit{Aedes} mosquitoes and how they spread diseases.} The head research assistant in each headquarter informed the participants collectively of how each treatment status operated. Participants were paired randomly,\footnote{They worked in pairs because governmental programs for monitoring \textit{Aedes aegypti} in similar formats use pairs of health workers.} and in a one-on-one discussion, the research assistants reinforced the treatment for each of the pairs.

% Change passive voice to active above, preferably using the present tense

The treatment delivery had the following guidelines. All groups were equally informed that we would measure and monitor their performance in the field. In the control group, we told participants that their compensation would be assigned without a performance assessment. In the individual treatment group, we explained participants that we would rank individual performances, and anyone reaching performance above the median would double their compensation. In the collective treatment group, we explained that we would rank the team performance, which was the sum of both participant's performances, and teams reaching performance above the median would double their compensation. Baseline field compensation was BRL 110.00. Those who successfully doubled it received BRL 220.00. The teams received a leaflet with a map of the area they should cover. The route was comprised of two to three blocks, containing around 120 houses. The blocks were within a census sector, to facilitate the use of census data afterwards.

% Same. Also, add values in dollars.

A typical visit to a household consisted of the following steps. First, the participants rang the doorbell in the house and explained that the municipality was experiencing a dengue fever outbreak.\footnote{Despite the widespread news coverage of Zika in the US, people have little knowledge about it in Brazil. Dengue, on the other hand, in constantly in the in the news since the 1980s. In fact, in Brazil, the \textit{Aedes aegypti} is popularly referred to as ``the Dengue mosquito''.} They instructed dwellers on how to lower the disease incidence, protect their families, and handed them a leaflet with information about appropriate dengue prevention practices. Our subjects then requested whether they could inspect the person's yard. When granted permission, they entered the household and searched for clean breeding sites, such as pots filled with clear water, and recipients containing larvae. Upon dismantling (\textbf{is this word used in this context?}) a breeding site (pouring out the accumulated water, for example), they had to report it by taking a photo on their cellphones. When they discovered larvae, they had to record a video showing the larvae before exterminating it. At the end of their visit, they had to take a picture of the household to account for their presence in the place.

% Good!

All of the image evidence collected by the participants was geolocated through the cellphones. At the end of the day, all subjects reported back to their respective headquarters, and presented the equipment back to the head research assistant. The performance parameters were calculated in the treatment groups based on the photos and videos recorded, and, accordingly, all workers received the promised compensation in cash.

% Again: change passive voice

\subsection{Outcomes}

The primary outcome in this study is field productivity of the health care workers. We measure worker productivity by coding cellphone data collected during the intervention into four indicators: 1) the number of houses visited; 2) the number of houses visited within less than two minutes; 3) the number of breeding sites removed and cleaned; 4) the number of exterminated larvae.

The second outcome is disease incidence in the municipality of Rio Verde. The Rio Verde Mayor's Office provided us with its annual health care report, which contains the dates and personal information of people who presented dengue fever symptoms and received hospital treatment from January to September 2018. We accessed the patients' addresses, and were able to map the areas of the city with the most cases and compare it with the distribution of our intervention. (\textbf{rewrite last sentence})

\subsection{Statistical Analysis}

The intention-to-treat population of our control and individual bonus treatment had 68 subjects and the collective bonus treatment included 69 individuals. These sample sizes were defined according to the availability of persons who filled in all the forms, attended the training session, and showed up to implement the intervention on May 5th, 2018. The actual populations, discarding subjects who withdrew from the experiment mid-intervention, were: Control (n = 58), individual bonus treatment (n = 64), and collective bonus treatment (n = 75).

% Checar se a informação não está repetida, cortar voz passiva se possível

We evaluate the effect of the treatment on disease incidence and field productivity using four types of statistical models: Balance tests, performance outcome analysis, disease incidence analysis, and differences-in-differences analysis. To perform the test power calculations, we assumed an effect of 0.15 standard deviations. We used statistics software R (version 3.6.3). The data was monitored by our teams of researchers, and the trial was registered under \hyperlink{https://osf.io/zpyfm}{EGAP ID 20180504AA}.

% Já fizemos comentários a respeito deste parágrafo

\subsection{Role of the funding source}

The authors are solely responsible for the design, implementation, and analyses of this experiment. They also assume responsibility for the writing of this article and all conclusions drawn from the results. The funders had no influence over the formulation, organisation, analysis, and interpretation of the outcomes. UM is responsible for the study design, the implementation of the intervention, and the statistical analysis. DF wrote the article and made publishing decisions.

% Já corrigido

\section{Results}
% The text in this section needs more flow, but i don't know how to give it flow. It really does seem like we're just meant to state info.

% Paragraphs in this section should follow the order:
% a description of number of participants recruited and included in analysis;
% baseline characteristics;
% findings for the primary outcome,
% secondary outcome,
% adverse events, : a prefeitura demorou um ano para enviar os dados de infecção do município.
% and finally any post-hoc or sensitivity analyses.

%No subheadings should be used in the Results or the Discussion sections.
% The first paragraph should state the exact dates (eg Jan 1 2013, to Dec 31 2014) between which participants were recruited, and include a trial profile.

% Add the date in which the Facebook ad was launched. The end date is May 4th.

Participants could enlist for eligibility evaluation from the day the Facebook advertisement was launched, on April 23, %essa é a data do fb ad que está no appendix. não sei se essa foi a data de lancamento do form, though.
2018. They oficially enrolled by attending the intervention in the Rio Verde municipality, Goias, Brazil on May 5th, 2018. They were randomised at around 10 am that day, one hour before the treatment was administered. Of the 558 who read the Facebook advertisement and filled in the Google Form attached, only 407 responded to us and filled in the Qualtrics survey. They were all notified of the following steps via email, but, the day before the intervention (May 4th), only 256 eligible subjects attended the training session. We had a final sample of 205 enrolled participants, and a total of 197 subjects by the end of the experiment had their performance analysed.

\tikzstyle{box2} = [rounded corners, rectangle, text centered, draw = red!65!blue!20, ultra thick, fill=red!20!blue!3.5, minimum width = 4cm, minimum height = 1cm]
\tikzstyle{box3} = [rounded corners, rectangle, text centered, draw = red!65!blue!20, ultra thick, fill=red!20!blue!3.5, minimum width = 2cm, minimum height = 1cm]
\tikzstyle{box4} = [rounded corners, rectangle, text centered, draw = red!65!blue!20, very thick, fill=gray!10, minimum width = 2cm, minimum height = 1cm]
\tikzstyle{arrow} = [draw = red!65!blue!20, ultra thick,->,>=stealth]

\begin{figure}
    \centering
    \caption{Trial Profile}
    \label{fig:trial_profile}

    \begin{tikzpicture}[node distance = 2.4cm, xshift = 1.5cm, centered]

    \footnotesize
\linespread{1.0}

     \node (form) [box2] {\textbf{558} filled in Google Form};
     \node (qualtrics) [box2, below of = form] {\textbf{407} filled in Qualtrics survey};
     \node (training) [box2, below of = qualtrics] {\textbf{256} showed up for the training session};
     \node (int) [box2, below of = training] {\textbf{205} showed up for the intervention};
     \node (treat1) [box3, below of = int] {Individual treatment \textbf{(n = 68)}};
     \node (ctrl) [box3, left of = treat1, xshift = -3.5cm] {Control \textbf{(n = 68)}};
     \node (treat2) [box3, right of = treat1, xshift = 3.5cm] {Peer treatment \textbf{(n = 69)}};
     \node (sample1) [box3, below of = treat1, yshift = -1cm] {\textbf{64} received individual bonus};
     \node (control) [box3, below of = ctrl, yshift = -1cm] {\textbf{58} received control intervention};
     \node (sample2) [box3, below of = treat2, yshift = -1cm] {\textbf{75} received collective bonus};

     \begin{scriptsize}
     \node (at1) [box4, below of = form, xshift = 3.5cm, yshift = 1.2cm] {\textbf{151} did not respond};
     \node (at2) [box4, below of = qualtrics, xshift = 3.5cm, yshift = 1.2cm] {\textbf{151} did not respond};
     \node (at3) [box4, below of = training, xshift = 3.5cm, yshift = 1.2cm] {\textbf{51} did not show up};
     \node (at4) [box4, below of = ctrl, xshift = 2cm, yshift = .7cm] {\textbf{10} did not adhere to protocol};
     \node (at5) [box4, below of = treat1, xshift = 1.93cm, yshift = .7cm] {\textbf{4} did not adhere to protocol};
     \node (at4) [box4, below of = treat2, xshift = 1.23cm, yshift = .7cm] {\textbf{6} subjects joined};
     \end{scriptsize}

     \draw [arrow] (form) -- (qualtrics);
     \draw [arrow] (qualtrics) -- (training);
     \draw [arrow] (training) -- (int);
     \draw [arrow] (int) -- (ctrl);
     \draw [arrow] (int) -- (treat1);
     \draw [arrow] (int) -- (treat2);
     \draw [arrow] (ctrl) -- (control);
     \draw [arrow] (treat1) -- (sample1);
     \draw [arrow] (treat2) -- (sample2);
     \draw [arrow] (0,-1.2) -- (2.1,-1.2);
     \draw [arrow] (0,-3.6) -- (2.1,-3.6);
     \draw [arrow] (0,-6) -- (2.1,-6);
    \end{tikzpicture}
\end{figure}

The average age of the participants was 25.7 [measure SD] years, of which 77.3\% were female, and 22.7\%, male. There were no relevant differences between groups in the measured baseline characteristics. Of the intention-to-treat population, 4\% of participants did not complete the intervention, but the attrition pattern test does not indicate shared characteristics that explain dropping out.

%%%%%%%%%% idk why there is space between the Individual and Collective columns.

% In their baseline characteristics tables, they add the SD in parenthesis next to the means, and in the contagens, they add the percentage of n that that category represents. So we need to do that as well :). They also recommend not adding F-Statistics and P-values bc those things are not supposed to matter if the randomisation was well done.

\begin{table}[!htbp] \centering
  \caption{Baseline Characteristics}
  \label{tab:baseline}
  \footnotesize
\begin{tabular}{@{\extracolsep{5pt}}lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & & Control & Individual & Collective\\
\hline \\[-1.8ex]
& \multicolumn{4}{l}{Panel A: Matched covariate balance on territorial assignment} \\
\hline \\[-1.8ex]
Number of Houses & & 276.41 & 282.04 & 281.19\\
Number of Households & & 885.67 & 903.04 & 900.39\\
Avg. Household Size & &  3.21 &   3.21 &   3.20\\
Log Avg. Income & &  6.47 &   6.45 &   6.45\\
Cases Before Treatment & & 13.78 &  10.24 &  10.77\\
\hline \\[-1.8ex]
& \multicolumn{4}{l}{Panel B: Covariate balance on participant characteristics} \\
\hline \\[-1.8ex]
Altruist & & 0.63 &  0.68 &  0.62 \\
Age & & 25.01 & 26.00 & 26.90 \\
Religiosity & & 0.53 &  0.38 &  0.45 \\
Pol. Engagement & & 0.69 &  0.65 &  0.68 \\
Soc. Engagement & & 0.59 &  0.62 &  0.67 \\
Above 2 Min. Wage & & 0.34 &  0.35 &  0.29 \\
FB Popularity & & 0.53 &  0.56 &  0.58 \\
\\[-1.8ex]\hline
\hline \\[-1.8ex]
& \multicolumn{4}{l}{Panel C: Attrition pattern test} \\
\hline \\[-1.8ex]
Variable & Attrition & Control & Individual & Collective\\
\hline \\[-1.8ex]
Age &  26.17 & 25.04 & 26.07 & 26.00 \\
Female &   0.72 &  0.79 &  0.79 &  0.74 \\
Has Vehicle &   0.35 &  0.27 &  0.37 &  0.37 \\
N & 341 & 73 & 71 & 73 \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}

% Add to the tables (mandatorily):
    % - 95% Confidence Intervals of the difference between groups.
    % - exact p-values (not necessary only if p < 0.0001)
    % - the points that indicate decimals need to be mid-line. idk how to do that on latex :)

\begin{table}[!htbp] \centering
  \caption{Results}
  \footnotesize
  \label{results}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
\\[-1.8ex]\hline
\hline \\
\multicolumn{7}{l} {\textbf{Primary Results}}\\
\hline
\multicolumn{7}{l} {\textit{Disease Incidence -- Differences in Differences Model}}\\
\hline
\\[-1.8ex]
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\
\cline{2-7}
\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected &  \\
& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (indv. x collect.) & \\
\hline \\[-1.8ex]
 DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 & \\
  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\
  & & & & & & \\
\hline \\[-1.8ex]
Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 & \\
Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 & \\
\\[-1.8ex]\hline
\hline \\
\multicolumn{7}{l} {\textit{Disease Incidence by Rio Verde Census Sector}} \\
\hline
\\ [-1.8ex] & \multicolumn{6}{c}{\textit{Dependent variable:}}\\
\cline{2-7} \\
[-1.8ex] & Before & 15 days & 30 days & 60 days & 90 days & 30-60 days \\
& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
\hline \\[-1.8ex]
 Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\
  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\
  & & & & & & \\
 Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\
  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\
  & & & & & & \\
\hline \\[-1.8ex]
Observations & 139 & 139 & 139 & 139 & 139 & 139 \\
Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\
\hline \\
\multicolumn{7}{l} {\textbf{Secondary Results}}\\
\hline
\\
\hline \\[-1.8ex]
\textit{Note:} & \multicolumn{6}{l}{DID stands for the Differences-in-Differences estimator.} \\
[-1.8ex] & \multicolumn{6}{l}{Robust standard error, clustered at the Census-Sector level, in parenthesis.} \\
& \multicolumn{6}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular}
\end{table}

%%%%%%%%% JUNTAR COM A TABELA ANTERIOR E INVERTER AS DUAS (VARIAVEIS COMO LINHAS)

\begin{table}[!htbp] \centering
  \caption{Field Productivity}
  \label{prodregs}
\begin{tabular}{@{\extracolsep{5pt}}lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\
\cline{2-5}
\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\
& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\
\hline \\[-1.8ex]
 Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\
  & (4.906) & (4.018) & (5.251) & (0.058) \\
  & & & & \\
 Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\
  & (4.428) & (3.571) & (4.049) & (0.076) \\
  & & & & \\
\hline \\[-1.8ex]
Observations & 197 & 197 & 197 & 197 \\
Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\
\hline
\hline \\[-1.8ex]
\textit{Note:}  & \multicolumn{4}{r}{Robust Standard Errors in Parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
\end{tabular}
\end{table}

The differences-in-differences analysis of the primary results is divided into time-windows after the intervention. The treatment status represents the assigned intervention against a pure-control of non-visited households. The cross-sectional coefficient shows the experiment lowered disease incidence in 10.3\%, and is the only significant effect -- at the 10\% level. Even so, the negative signs indicate that, had there been a significant effect, our health workers' visits would have decreased dengue incidence when compared to the pure control. Thus, a more powerful intervention -- with larger samples, coverage of other neighbourhoods, or subsequent rounds of visits to the same households --, would likely show stronger results. The coefficient comparing the two primary treatment statuses -- in which the collective treatment is the main intervention, and the individual treatment is the control -- shows an impact of 2.9\% less infections in the collective bonus group, which could indicate it is more effective. Nevertheless, at standard levels, it is insignificant.

Subsequently, we evaluate the disease incidence by census sector, analysing the addresses of citizens hospitalised with dengue and the households visited by our health workers. We compare the number of hospitalisations before the intervention, and afterwards within a few time-frames. Figure \ref{figc360daysdiseaseinc} illustrates the differences in disease incidence using a 60 days window before and after the intervention. The maps show a consistent reduction in the number of infected people, which is compatible with the 10.3\% reduction estimated in the differences-in-differences model.

\begin{figure}
\includegraphics[width=\textwidth]{figures/c3diseaseincidence60dw.pdf}
\caption[Disease incidence.]{Disease incidence 60 days around the treatment.\label{figc360daysdiseaseinc}}
\end{figure}

Secondary results refer to subjects' field productivity. Compared to control groups, incentivised workers visited on average 8.7 less houses. This may sound counterintuitive, but it reflects their motivation to be thorough, and spend more time examining yards to guarantee they find and eliminate all breeding sites. On average, individually and collectivelly incentivised workers find 25.1 and 21.5 more breeding sites, respectively, than non-incentivised agents. Workers in the collective bonus treatment cleaned on average 50\% more breeding sites, and are 16.3\% more likely to find larvae than members of the control group.

The main adversity we faced regarded access to our main outcome data. We needed to georeference the municipality's hospitalisation dataset to match the infected persons' addresses to the locations of our intervention. Since this data is considered sensitive\footnote{The dataset includes addresses, full names, social security numbers (Brazilian CPFs), and other sensitive personal information.} and is protected by law, the Rio Verde authorities decided to only make it available to us one year after the intervention took place. We eventually received the data, and encrypted it to store it safely. However, this considerably delayed our analysis.

\section{Discussion}
%%%%%%%%%% I may have been a little prolixa.
%%% Also nothing has been revised yet.

Giving health workers performance-based financial incentives has the potential to boost treatment efficacy by increased productivity. We tested two types of incentives -- collective and individual -- and found that agents who saw benefit in working harder delivered more results in terms of exterminated \textit{Aedes} breeding sites and larvae. While the literature on \textit{Aedes} control strategies usually reports the results as larval indexes -- Container, House, and Breteau -- we tried to reach for the final consequence our interventions aim. However, the effect of productivity growth on the number of infections is still unclear, as our results did not reach statistical significance. We attribute this mainly to our intervention's lack of strength, as it was restricted geographic and duration-wise.

Our paper dialogues with two dimensions of health policy implementation. First, it directly treats \textit{Aedes aegypti} infestations, adding to the literature on community-based interventions, where healthcare personnel and community members partner in preventive practices. Second, it investigates the essentially economic question of how to increase the efficiency of states' investments in healthcare -- an issue that becomes especially resolute in developing countries with poor populations. These two dimensions are double-sided. Dengue does not have a known cure or specific treatment\footnote{Health agencies in most endemic countries have not implemented widespread use of the \textit{Dengvaxia®} (CYD-TDV), an existing tetravalent dengue vaccine produced by French laboratory Sanofi Pasteur, as a prevention mechanism. The WHO advises against it for seronegative individuals, while for the seropositive, it is efficacious and safe \citep{who2018vaccine}. Early 2020, the Butantan Institute in Brazil concluded tests for another dengue vaccine, but results in general population are still under observation.}, and its numbers rise every year for the past decade. As more people fall ill, the more victims there are, and the more expenditures in clinical care grow. Although preventive strategies require additional investments -- which our research design implicates --, they should diminish infection and casualties -- which we attempt to measure as our primary outcomes -- and significantly decrease the burden on already overcharged healthcare systems.

% Do we cite our own meta-analysis?
In their \citeyear{WHO2012global} 'Global Strategy for Dengue Prevention and Control 2012-2020', the WHO' recommendations all implicate engaging healthcare institutions and community work in a mixture of top-down and bottom-up approaches that focus on controlling the \textit{Aedes} vector. This is supported by entomologists for a number of reasons \citep{merzel2003reconsidering}. \citet{Abbas2014Integrated} evaluates past efforts to combat dengue and reaches the conclusion that integrated approaches are the best solution. This position opposes to exclusively vertical interventions -- such as insecticide space spraying, or installation of insecticide treated nets on doors and windows, for example -- as well as to those that rely on communities' grassroots mobilisation only. In two different systematic reviews, \citet{Heintze2007what} and \citet{Ballenger-Browning2009multi} attempted to identify what were the main characteristics of successful community-based interventions -- where 'successful' translates efficacy in reducing vector density. Yet, they found no regularities or mechanisms strong enough to recommend a particular strategy.

The main issue seems to be the sustainability -- or lack thereof\footnote{\citet{brathwaite2012history} observe that although \textit{Aedes}-borne diseases had nearly disappeared from the American continent in the 20th century, the 1970s reinfestation struck due to popular negligence and abandonment of the necessary control practices to remain \textit{Aedes aegypti}-free.} -- of the prevention practices, which suggests the population needs constant monitoring from health authorities to "stay on track" \citep{Morrison2008defining}. Some scholars believe that sustained programs with strong surveillance mechanisms might be able to instill behavioural changes that preclude constant elevated investments \citep{Gubler2013prevention}. Although citizens may not develop such autonomy, it is consensual that healthcare systems must act locally in partnership with community members to reduce mosquito populations. Recent randomised-controlled trials such as \cite{castro2012community}, \cite{caprara2015entomological}, and \cite{ulibarri2016control} propose interventions designs specially focused on this interplay, promoting capacity building, community mobilisation, distribution of educational material, instruction on exterminating breeding sites, installation of oviposition traps, and other strategies.

The literature addresses community health worker productivity in a wider set of circumstances, as they play a fundamental role of linking healthcare systems and the general population. \citet{muthmainnah2017improving} reviews 25 articles, showing that better salaries improve productivity and the working satisfaction of nurses. When it comes to health workers outside of the clinical environment, who implement preventive treatments, \cite{Ballard2017systematic} review 14 articles and find that improving these workers' performance -- through several different incentive schemes -- affect mostly behavioural, but not biological, outcomes for patients. This is in line with our results: although breeding sites were exterminated and people were educated on how to sustain these practices (behaviour change), results on disease incidence (biological outcome) were not significant. Moreover, this review finds that performance-improving interventions can increase the quality of care by incentivising adherence to treatment protocols and more rigorous completion of activities.

% Is this relevant enough to deserve a full paragraph? I think it's a cool way to strengthen our experiment :) but please help me judge
More recent studies analyse how sustained practices of financial incentive affect real healthcare systems. For instance, some Indian provinces have a program for maternal health with one performance-rewarded, and one flat salary community health workers. \citet{koehn2020remuneration} found that receiving a visit from the incentivised agents do not increase the chances that a pregnant woman will access the healthcare system's pre and postnatal care structures. We have no means of predicting how the \textit{Aedes} prevention teams would behave in a long-term situation alike. However, there is a fundamental difference between our compensation scheme and that implemented by these Indian provinces. Each community has a single performance-compensated agent, who receives a bonus for each woman they visit who underwent an institutionalised delivery. In the meantime, our bonuses presuppose a median performance among several agents, those who place above it, and those who place below it. While a paid-for-performance Indian health worker gets rewarded for any one positive outcome she achieves, our agents must produce better results than 50\% of their counterparts. Thus, we believe our incentive scheme is stronger, and has more potential to inspire workers to put in extra effort.

Our main criticism to the current scholarship on \textit{Aedes} control regards the outcome measurements and how they only indirectly address the problem at hand. The assumption that lower vector density leads to lower disease incidence is not yet micro-founded, in the sense that an algorithm to quantitatively predict their relationship still does not exist \cite{Morrison2008defining}. The vast majority of \textit{Aedes} control interventions report entomological indexes, and Knowledge, Attitudes and Practices (KAP) surveys as their main outcomes, not accounting for data on the number of viral infections before and after the treatment. Although it is impossible to accurately count undiagnosed patients, there should be observable drops in hospitalisation -- related to these diseases -- in local public healthcare networks where the interventions are successful. We acquire access to this data -- through the Rio Verde mayor's office -- and attempt to make these estimations more precise, looking into how community programs reflect on their ultimate goal of reducing infection rates and mortality.

Although our intervention did not reach the desired efficacy, we developed a formal model\footnote{Please refer to the Appendix for the full model and explanation.} that explains the general framework of our design. In simple terms, by choosing the optimal incentive scheme, the healthcare system can induce more effort and more cooperation among workers. When health workers receive a flat salary without performance bonuses, to them, exerting effort only seems to generate costs, without any benefits. When the governmental agency sets rewards for both individual and collective performances, health workers choose to put effort in their own tasks, but also in helping peers get theirs done. Both governmental agency and health worker benefit from this situation, as is potentiates the chances of generating successful service provision, and of receiving the maximum reward. Thus, the optimal incentive scheme lies on collective incentives. This becomes clear when looking at our results, as collectively incentivised teams were able to find more larvae. This happens because once one agent discovers one container of larvae in a home, it is unlikely that the other worker will find a second one (breeding sites are excludable). Thus, workers who coordinate have better outcomes than individuals 'competing' against their peers.

Finally, we raise a few hypotheses as to why increased productivity did not cause fewer hospitalisations, recommending that future research increases test power and isolates intervention effects. First, we point out that finding a breeding site does not implicate that all larvae were exterminated in a location, as it is likely there are more breeding sites in the surroundings. The presence of a larvae-filled container in a household implies that there necessarily is a mosquito within a 70 meter radius. The mosquito could have laid eggs anywhere else in this perimeter, but, statistically, other breeding sites become harder to detect. Furthermore, we did not isolate treated regions, which means that a block of houses that received the intervention could have been less than 70 meters away from untreated households. Thus, spillover mosquitoes might have infected treated populations.

Second, the municipality had significantly high dengue incidence, reaching 3,411 reported infections from January to September 2018. It is possible that any efforts within this time range only produce a robust effect above a certain threshold. For example, measles is only considered as eradicated by herd immunity when vaccination reaches around 95\% of the population \citep{fox1983herd}. The threshold for dengue is unknown, but maybe we would have had to assemble enough teams to cover 90\% of the households in Rio Verde. Lastly, our intervention might have actually increased hospitalisation in the treated area because one of the first things our health workers said to the population was they should visit a doctor if they experienced any dengue symptoms. This may have caused a competing effect, and as the number of infections decreased, the number of people reporting to hospitals increased, offsetting the impact.

For future research, we highly recommend research designs to encompass broader areas and to promote more than a single wave of treatments. Still, we believe our model and compensation scheme to be extremely promising in promoting progress for a stagnant, yet adequate, strategy. Once the scholarship is able to precise the levels and depth of intervention necessary to halt the \textit{Aedes} proliferation, it will serve as crucial information to policy-makers searching to optimise the investments in health and specifically in \textit{Aedes}-borne disease prevention. For now, our study also presents important findings to health agencies, since it is valuable to know also what policies to steer away from. Our results indicate that any Dengue prevention program which underestimates the necessary area of coverage and duration will be a sunk investment.

We believe a few recent studies have been wise to explore one of the key assets in our design: mobile technology to both precise measures and monitor performance and workflow of community health agents. \citet{feroz2020using} showed that cellphones can help collect data, provide quality healthcare services, and organise health workers' tasks, but in low and middle income settings, these outcomes become nonviable due to technical difficulties and lack of training. \citet{kenny2020design} propose that, in remote regions, or in urban areas with poor infrastructure, offline platforms can be successfully used for the same functions. Thus, developing tropical countries should find in our type of intervention a feasible and promising means to finally make progress in their combat to \textit{Aedes}-borne viral infections, and optimise public expenditure, and increase their population's welfare.

\singlespacing
\begin{footnotesize}
\bibliographystyle{apalike}
\bibliography{biblio.bib}
\end{footnotesize}

\end{document}

### 2020-10-09 paper/article.Rmd
revising intro and methods

@@
 bibliography: references.bib
-biblio-style: apalike
 output:
@@
     toc_depth: 3
-    template: article-template.latex
+    template: template.latex
 ---
@@
 around 100 countries, causing 400 million infections and 22 thousands deaths
-each year [@bhatt2013global; @cdc2020dengue; @musso2018unexpected]. Since there
-are no safe vaccines for most *A. aegypti*-transmitted diseases
-[@sridhar2018effect; @world2017dengue], we have seen a number of recent dengue
-and Zika outbreaks in Asia, the Caribbean, South America, and the United States
+each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
+for most *A. aegypti*-transmitted diseases [@sridhar2018effect;
+@world2017dengue], we have seen a number of recent dengue and Zika outbreaks in
+Asia, the Caribbean, South America, and the United States
 [@carlson2016ecological; @leta2018global]. Chikungunya virus, which was endemic
@@
 Mosquito control is the primary strategy to prevent *A. aegypti*-borne
-infections [@beatty2010best; @eisen2009proactive; @ooi2006dengue]. The World
-Health Organization recommends the elimination of containers and the use of
-insecticide to reduce vector breeding, specially in settings where human-vector
-contacts are frequent, such as schools, hospitals, and workplaces
-[@WHO2012global; @world2020denguecontrol]. However, cleaning breeding sites and
-insecticide spraying are labour-intensive processes and are often carried out
-inconsistently [@paz2015dengue; @siddiqui2016use; @WHO2012global]. In most
-endemic countries, local governments are the main responsible for providing
-vector control, thus increasing the productivity of civil servants is essential
-to the effectiveness of anti-mosquito programmes worldwide.
+infections [@beatty2010best; @eisen2009proactive]. The World Health Organization
+recommends the elimination of containers and the use of insecticide to reduce
+vector breeding, specially in settings where human-vector contacts are frequent,
+such as schools, hospitals, and workplaces [@WHO2012global;
+@world2020denguecontrol]. However, cleaning breeding sites and insecticide
+spraying are labour-intensive processes, and they are often carried out
+inconsistently in developing countries [@paz2015dengue; @siddiqui2016use;
+@WHO2012global]. In this regard, improving the performance of those responsible
+for vector control is essential to the effectiveness of anti-mosquito programmes
+worldwide.
 
-Financial incentives are crucial determinants of worker performance in public
-and private organisations [@burgess2003role]. While studies indicate that
-reward schemes may improve the productivity of health care providers
-[@basinga2011effect; @flodgren2011overview; @ulrich2005does], it is unclear how
-they affect the motivation of workers fighting *A. aegypti*. Moreover, there is
-no evidence about the impact of financial incentives on patient-level arboviral
-outcomes, such as virus-related hospitalisations or disease incidence
-[@flodgren2011overview].
+Studies show that financial incentives may increase the productivity of health
+care workers [@clemens2014physicians; @muthmainnah2017improving;
+@ulrich2005does]. However, systematic reviews indicate the available evidence
+has methodological shortcomings, such as selection bias and inadequate
+experimental blinding, which limit its generalisability [@bassani2013financial;
+@flodgren2011overview; @scott2011effect]. Moreover, it remains unclear which
+rewarding schemes have a stronger effect on health care worker performance
+[@fainman2020design], or whether they have a sustained effect on patient
+outcomes [@jha2012long; @langdown2014use].
 
-To explore how monetary incentives affect health worker motivation and patient
-outcomes, we ran a randomised field experiment in the city of Rio Verde,
-Brazil, which has experienced a peak in dengue infections in the last years. We
-hired and trained teams of health care workers to perform simplified procedures
-designed to exterminate *A. aegypti* breeding sites. Our experiment consisted
-of two treatment arms plus a control condition. The control group received a
-fixed compensation for completing their task, and we offered individual or
-collective bonuses to those allocated in the two treatment groups. We then
-measured the impact of the compensations schemes on the number of breeding
-sites discovered, larvae exterminated, and city-level dengue incidence 30, 60,
-and 120 days after our intervention.
+In this paper, we explore how financial incentives affect the productivity of
+health care personnel involved in *A. aegypti* control and measure how monetary
+rewards impact dengue hospitalisations in the long run. We run a randomised
+field experiment in the city of Rio Verde, Brazil, which has experienced a peak
+in dengue infections in the last years. We hired and trained teams of health
+care workers to perform simplified procedures designed to exterminate *A.
+aegypti* breeding sites. Our experiment consisted of two treatment arms plus a
+control condition. The control group received a fixed compensation for
+completing their task, and we offered individual or collective bonuses to those
+allocated in the two treatment groups. We then measured the impact of the
+compensations schemes on the number of breeding sites discovered, larvae
+exterminated, and city-level dengue incidence 30, 60, and 120 days after our
+intervention.
 
 We find that monetary rewards increase the number of cleaned breeding sites in
-both treatment conditions (individual and team bonuses) and collective
+both treatment conditions (individual and team bonuses), and that collective
 financial incentives also improve larvae extermination. Our results show that
@@
 not robust. In summary, we provide experimental evidence that performance
-bonuses increase productivity in public service delivery and that small
-financial incentives to health workers may improve patient outcomes and reduce
-hospitalisation costs in *Aedes*-endemic countries.
+bonuses enhance public service delivery and that small financial incentives may
+improve patient outcomes and reduce hospitalisation costs in *Aedes*-endemic
+countries.
 
@@
 
-We ran a randomised field experiment at the individual level in the municipality
-of Rio Verde, Brazil, which had experienced a major dengue outbreak one year
-prior to our experiment (2017). We used Facebook advertisements to recruit
-potential participants. The advertisements directed applicants to a Google Forms
-web page that requested their contact information, and we sent a pre-treatment
-demographic questionnaire to every applicant who provided a valid email address.
-At this stage, we excluded all individuals under 18 years old. We invited the
-remaining applicants to our training session, which we ran on the 4^th^ of May,
-2018. The meeting consisted of a lecture on *A. aegypti* vector biology and
-practical instructions on how to find and exterminate mosquito breeding sites.
-Those who did not attend the session were also excluded from the study.
+We conducted a randomised field trial in Rio Verde, a municipality in the
+Brazilian Midwestern state of Goiás. Rio Verde had 229,000 inhabitants and 1,156
+confirmed dengue cases, one of highest counts in the state [@goias2020]. We used
+Facebook advertisements to recruit potential participants. The advertisements
+directed applicants to Google Forms, where we asked for their contact
+information. We sent a pre-treatment demographic survey to every applicant who
+provided a valid email address. At this stage, we excluded all individuals under
+18 years old. We invited the remaining applicants to our training session, which
+we ran on the 4^th^ of May, 2018. The meeting consisted of a lecture on *A.
+aegypti* vector biology and practical instructions on how to find and
+exterminate mosquito breeding sites. Those who did not attend the session were
+also excluded from the study.
 
 Table \ref{tab:covbal} displays the attrition tests, the covariate balance
-tests, and the territorial assignment before and after applying propensity
-score matching [@dehejia2002propensity; @rosenbaum1985constructing] on census
-tract characteristics. We observe no significant differences regarding
-attrition rates, reinforcing that the treatment was correctly randomised.
-Participants' demographics are also similar across all groups, and the matching
-technique successfully balanced the territorial assignment.
+tests, and the territorial assignment before and after applying propensity score
+matching [@rosenbaum1985constructing] on census tract characteristics. We
+observe no significant differences regarding attrition rates, indicating that
+the treatment was correctly randomised. Participants' demographics are also
+similar across all groups, and the matching technique successfully balanced the
+territorial assignment.
 
@@
 The intervention took place on the 5^th^ of May, 2018. We randomly assigned
-subjects to three groups. To avoid spillovers, we directed each group to
-separate headquarters before the intervention began. Participants worked in
-pairs and were aware of other groups, but they did not know about the different
-treatment conditions. In the control group ($n = 68$), we told participants
+subjects into three groups and directed each group to separate headquarters in
+order to avoid spillovers. In the control group ($n = 68$), we told participants
 that they would receive a flat payment regardless of their performance (BRL 110
-/ USD 20 per subject). In the individual treatment group ($n = 68$), we
-informed subjects that we would rank individual performances, and that we would
-double the compensation for all of those who performed above the sample median
-(BRL 220 / USD 50 per subject). In the collective treatment group ($n = 70$),
-we explained that we would rank the pair performance and double the payment for
-teams who presented results better than the sample median (BRL 220 / USD 50 per
-subject). The teams received a leaflet with a map of the area they should
-cover. The route comprised of two to three blocks and contained around 120
-houses.
+/ USD 20 per subject). In the individual treatment group ($n = 68$), we informed
+subjects that we would rank individual performances and double the compensation
+for those who performed above the sample median (BRL 220 / USD 50 per subject).
+In the collective treatment group ($n = 70$), we explained that we would rank
+the pair performance and double the payment for teams who presented results
+better than the sample median (BRL 220 / USD 50 per subject). Participants
+worked in pairs and were aware of other groups, but they did not know about the
+different treatment conditions. The teams received a leaflet with a map of the
+area they should cover. The route comprised of two to three blocks and contained
+around 120 houses.
 
 A typical visit to a household consisted of the following steps. First,
-participants rang the doorbell in a house and explained that the municipality
-had experienced a dengue fever outbreak. They instructed dwellers on how to
-lower dengue incidence and handed them a leaflet with information about dengue
-prevention practices. Our subjects then requested whether they could inspect
-the person's yard. If granted permission, they entered the household and
-searched for clean breeding sites, such as pots filled with clear water, and
-recipients containing larvae. Upon exterminating a breeding site (pouring out
-the accumulated water, for example), subjects had to report their task by
-taking a photo on their cellphones. When they discovered larvae, they had to
-record a video showing the larvae before exterminating it. At the end of their
-visit, they had to take a picture of the household to account for their
-presence in the location.
+participants rang the doorbell and explained that the municipality had
+experienced a dengue fever outbreak. They instructed dwellers on how to lower
+dengue incidence and handed them a leaflet with information about dengue
+prevention practices. Then, subjects asked whether they were allowed to inspect
+house yard. If granted permission, they entered the household and searched for
+clean breeding sites, such as pots filled with clear water, and recipients
+containing larvae. Upon exterminating a breeding site (pouring out the
+accumulated water, for example), subjects had to report their task by taking a
+photo on their cellphones. When they discovered larvae, they had to record a
+video showing the larvae before exterminating it. At the end of their visit,
+they had to take a picture of the household to account for their presence in the
+location.
 
-The primary outcome in this study is field productivity of the health care
-workers. We measure worker productivity by coding cellphone data collected
-during the intervention into four indicators: 1) the number of houses visited;
-2) the number of houses visited within less than two minutes; 3) the number of
-breeding sites removed and cleaned; 4) the number of exterminated larvae. We
-employed ordinary least squares with robust standard errors [@imbens2016robust].
-We estimated the statistical power of the study assuming a treatment effect of
-0.15 standard deviations.
+This study evaluates two outcomes. The first outcome is field productivity of
+the health care workers. We measure worker productivity by coding cellphone data
+collected during the intervention into four indicators: 1) the number of houses
+visited; 2) the number of houses visited within less than two minutes; 3) the
+number of breeding sites removed and cleaned; 4) the number of exterminated
+larvae. We analyse the data using ordinary least squares with robust standard
+errors [@imbens2016robust]. We estimate the statistical power of the study
+assuming a treatment effect of 0.15 standard deviations.
 
 The second outcome of interest is dengue incidence in the municipality of Rio
-Verde. The Rio Verde Mayor's Office provided us with its annual health care
-report, which contains the dates and personal information of patients who had
-dengue fever and received hospital treatment from January to September 2018. We
-georeferenced the home addresses of the patients and compared the incidence map
-with the distribution of our intervention. We use a differences-in-differences
-estimator to assess the impact of our experiment [@angrist2008mostly;
-@card1994minimum].
+Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
+Mayor's Office provided us with its annual health care report, which contains
+the dates and personal information of patients who had dengue fever and received
+hospital treatment from January to September 2018. We georeferenced the home
+addresses of the patients and compared the incidence map with the distribution
+of our intervention. We also compare dengue incidence in each of the treatment
+statuses with incidence figures in the control group. The unit of analysis is
+the census tract in both models. We employ a differences-in-differences
+estimator to assess the treatment effects. [@angrist2008mostly].
 
-We pre-registered the experiment on the Evidence in Governance and Policy
-(EGAP) website (<https://osf.io/6q8vu/>) and received IRB approval from New
-York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
+We pre-registered the experiment on the Evidence in Governance and Policy (EGAP)
+website (<https://osf.io/6q8vu/>) and received IRB approval from New York
+University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
 funders of this study had no influence over the formulation, organisation,
@@
 consent. For more information on the experimental design, sample
-characteristics, exclusion criteria, and estimation methods, please refer to
-the Supplementary Material.
+characteristics, exclusion criteria, and estimation methods, please refer to the
+Supplementary Material.
 

### 2020-10-09 paper/article.Rmd
WIP

@@
 
-The *Aedes aegypti* mosquito species is the major vector of several arboviral
-diseases worldwide, including dengue, yellow fever, Zika, and chikungunya
+The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
+diseases, including dengue, yellow fever, Zika, and chikungunya
 [@burt2012chikungunya; @jansen2010dengue; @leta2018global;
@@
 increased exponentially, with estimates suggesting that dengue is endemic in
-around 100 countries, causing 400 million infections and 22 thousands deaths
+around 100 countries and causes 400 million infections and 22 thousands deaths
 each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
-for most *A. aegypti*-transmitted diseases [@sridhar2018effect;
-@world2017dengue], we have seen a number of recent dengue and Zika outbreaks in
-Asia, the Caribbean, South America, and the United States
-[@carlson2016ecological; @leta2018global]. Chikungunya virus, which was endemic
-only to Africa, has already been reported in every region of the world
-[@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].
+for most *Aedes*-transmitted diseases [@sridhar2018effect;
+@world2017dengue], we have seen a number of dengue and Zika outbreaks in Asia,
+the Caribbean, South America, and the United States [@carlson2016ecological;
+@leta2018global]. Chikungunya virus, which was endemic only to Africa, has
+already been reported in every region of the world [@grandadam2011chikungunya;
+@kraemer2015global; @mayer2017emergence].
 
-Mosquito control is the primary strategy to prevent *A. aegypti*-borne
-infections [@beatty2010best; @eisen2009proactive]. The World Health Organization
+Mosquito control is the primary strategy to prevent *Aedes*-borne infections
+[@beatty2010best; @eisen2009proactive]. The World Health Organization
 recommends the elimination of containers and the use of insecticide to reduce
-vector breeding, specially in settings where human-vector contacts are frequent,
-such as schools, hospitals, and workplaces [@WHO2012global;
-@world2020denguecontrol]. However, cleaning breeding sites and insecticide
+vector breeding, specially in settings where human-vector contacts are
+frequent, such as schools, hospitals, and workplaces [@WHO2012global;
+@world2020denguecontrol]. However, breeding site cleaning and insecticide
 spraying are labour-intensive processes, and they are often carried out
@@
 @WHO2012global]. In this regard, improving the performance of those responsible
-for vector control is essential to the effectiveness of anti-mosquito programmes
-worldwide.
+for mosquito control is essential to the effectiveness of anti-*Aedes*
+programmes.
 
-Studies show that financial incentives may increase the productivity of health
-care workers [@clemens2014physicians; @muthmainnah2017improving;
-@ulrich2005does]. However, systematic reviews indicate the available evidence
-has methodological shortcomings, such as selection bias and inadequate
-experimental blinding, which limit its generalisability [@bassani2013financial;
-@flodgren2011overview; @scott2011effect]. Moreover, it remains unclear which
-rewarding schemes have a stronger effect on health care worker performance
-[@fainman2020design], or whether they have a sustained effect on patient
-outcomes [@jha2012long; @langdown2014use].
+Research shows that financial incentives may increase the productivity of
+health care workers [@clemens2014physicians; @muthmainnah2017improving;
+@ulrich2005does]. However, systematic reviews indicate that the available
+evidence has serious methodological shortcomings, such as selection bias and
+inadequate experimental blinding, what limits the generalisability of current
+findings [@bassani2013financial; @flodgren2011overview; @scott2011effect].
+Moreover, it remains unclear which rewarding schemes have a stronger effect on
+health care worker performance [@fainman2020design], and whether monetary
+incentives have a sustained effect on patient outcomes [@jha2012long;
+@langdown2014use].
 
@@
 health care personnel involved in *A. aegypti* control and measure how monetary
-rewards impact dengue hospitalisations in the long run. We run a randomised
-field experiment in the city of Rio Verde, Brazil, which has experienced a peak
-in dengue infections in the last years. We hired and trained teams of health
-care workers to perform simplified procedures designed to exterminate *A.
-aegypti* breeding sites. Our experiment consisted of two treatment arms plus a
-control condition. The control group received a fixed compensation for
-completing their task, and we offered individual or collective bonuses to those
-allocated in the two treatment groups. We then measured the impact of the
-compensations schemes on the number of breeding sites discovered, larvae
-exterminated, and city-level dengue incidence 30, 60, and 120 days after our
-intervention.
+rewards impact dengue hospitalisations. We run a randomised field experiment in
+the city of Rio Verde, Brazil, which has experienced a peak in dengue
+infections in the last years. We hired and trained teams of health care workers
+to perform simplified procedures designed to exterminate *A. aegypti* breeding
+sites. Our experiment consisted of two treatment arms plus a control condition.
+The control group received a fixed compensation for completing their tasks, and
+we offered individual or collective bonuses to those allocated in the two
+treatment groups. We then measured how the different compensations schemes
+affect the number of breeding sites discovered, larvae exterminated, and
+city-level dengue incidence.
 
@@
 financial incentives also improve larvae extermination. Our results show that
-the control group has a high incidence of houses visited in less than two
-minutes apart from each other, which suggests that workers may cheat in the
-absence of financial incentives. When we combine both treatments, we also find
-that the intervention decreases dengue incidence in 10.3%, but the results are
-not robust. In summary, we provide experimental evidence that performance
-bonuses enhance public service delivery and that small financial incentives may
-improve patient outcomes and reduce hospitalisation costs in *Aedes*-endemic
-countries.
+the control group has a high number of houses visited in less than two minutes
+apart from each other, which suggests that workers may cheat in the absence of
+financial incentives. When we combine both treatments, we also find that the
+intervention decreases dengue incidence in 10.3%, but the results are not
+robust. In summary, we provide experimental evidence that performance bonuses
+enhance public service delivery and that small financial incentives may improve
+patient outcomes and reduce hospitalisations in *Aedes*-endemic countries.
 
@@
 the census tract in both models. We employ a differences-in-differences
-estimator to assess the treatment effects. [@angrist2008mostly].
+estimator to assess the treatment effects [@angrist2008mostly].
 
@@
 
-We find that providing financial incentives to health care worker significantly
-increase their field productivity. Both our individual bonus and our collective
-bonus treatment groups find more *A. aegypti* breeding sites and exterminate
-more mosquito larvae than participants in the control condition, which did not
-receive performance compensations. Our results also indicate that the
-intervention decreases city-wide levels of dengue incidence, but the
-coefficients only reach statistical significance when we combine the two
-treatments together and contrast them with the control group. Overall, the
-findings suggest that monetary payments are an effective method of improving
-health worker performance, yet more research is needed to assess whether higher
-labour productivity leads to fewer dengue-related hospitalisations.
+We find that financial incentives significantly increase the field productivity
+of health care workers fighting *Aedes aegypti*. Subjects in both the
+individual and the collective bonus groups locate more mosquito breeding sites
+and exterminate more larvae than participants in the control condition. Our
+results also show the intervention decreases city-wide levels of dengue
+incidence, but the coefficients only reach statistical significance when we
+combine the two treatments together and contrast them with the control group.
+Overall, the findings suggest that monetary payments are an effective method of
+improving health worker performance, yet more research is needed to assess
+whether higher labour productivity leads to fewer dengue-related
+hospitalisations.
 

### 2020-10-11 paper/article.Rmd
edits to first three sections

@@
 subjects into three groups and directed each group to separate headquarters in
-order to avoid spillovers. In the control group ($n = 68$), we told participants
-that they would receive a flat payment regardless of their performance (BRL 110
-/ USD 20 per subject). In the individual treatment group ($n = 68$), we informed
-subjects that we would rank individual performances and double the compensation
-for those who performed above the sample median (BRL 220 / USD 50 per subject).
-In the collective treatment group ($n = 70$), we explained that we would rank
-the pair performance and double the payment for teams who presented results
-better than the sample median (BRL 220 / USD 50 per subject). Participants
-worked in pairs and were aware of other groups, but they did not know about the
-different treatment conditions. The teams received a leaflet with a map of the
-area they should cover. The route comprised of two to three blocks and contained
-around 120 houses.
+order to avoid spillovers. In the control group ($n = 68$), we told
+participants that they would receive a flat payment regardless of their
+performance (BRL 110 / USD 20 per subject). In the individual treatment group
+($n = 68$), we informed subjects that we would rank individual performances and
+double the compensation for those who performed above the sample median (BRL
+220 / USD 50 per subject). In the collective treatment group ($n = 70$), we
+explained that we would rank the pair performance and double the payment for
+teams who presented results better than the sample median (BRL 220 / USD 50 per
+subject). Participants worked in pairs and were aware of other groups, but they
+did not know about the different treatment conditions. The teams received a
+leaflet with a map of the area they should cover. The route comprised of two to
+three blocks and contained around 120 houses.
 
@@
 video showing the larvae before exterminating it. At the end of their visit,
-they had to take a picture of the household to account for their presence in the
-location.
+they had to take a picture of the household to account for their presence in
+the location.
 
 This study evaluates two outcomes. The first outcome is field productivity of
-the health care workers. We measure worker productivity by coding cellphone data
-collected during the intervention into four indicators: 1) the number of houses
-visited; 2) the number of houses visited within less than two minutes; 3) the
-number of breeding sites removed and cleaned; 4) the number of exterminated
-larvae. We analyse the data using ordinary least squares with robust standard
-errors [@imbens2016robust]. We estimate the statistical power of the study
-assuming a treatment effect of 0.15 standard deviations.
+the health care workers. We measure worker productivity by coding cellphone
+data collected during the intervention into four indicators: 1) the number of
+houses visited; 2) the number of houses visited within less than two minutes;
+3) the number of breeding sites removed and cleaned; 4) the number of
+exterminated larvae. We analyse the data using ordinary least squares with
+robust standard errors [@imbens2016robust]. We estimate the statistical power
+of the study assuming a treatment effect of 0.15 standard deviations.
 
@@
 Mayor's Office provided us with its annual health care report, which contains
-the dates and personal information of patients who had dengue fever and received
-hospital treatment from January to September 2018. We georeferenced the home
-addresses of the patients and compared the incidence map with the distribution
-of our intervention. We also compare dengue incidence in each of the treatment
-statuses with incidence figures in the control group. The unit of analysis is
-the census tract in both models. We employ a differences-in-differences
-estimator to assess the treatment effects [@angrist2008mostly].
+the dates and personal information of patients who had dengue fever and
+received hospital treatment from January to September 2018. We georeferenced
+the home addresses of the patients and compared the incidence map with the
+distribution of our intervention. We also compare dengue incidence in each of
+the treatment statuses with incidence figures in the control group. The unit of
+analysis is the census tract in both models. We employ a
+differences-in-differences estimator to assess the treatment effects
+[@angrist2008mostly].
 
-We pre-registered the experiment on the Evidence in Governance and Policy (EGAP)
-website (<https://osf.io/6q8vu/>) and received IRB approval from New York
-University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
+We pre-registered the experiment on the Evidence in Governance and Policy
+(EGAP) website (<https://osf.io/6q8vu/>) and received IRB approval from New
+York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
 funders of this study had no influence over the formulation, organisation,
@@
 consent. For more information on the experimental design, sample
-characteristics, exclusion criteria, and estimation methods, please refer to the
-Supplementary Material.
+characteristics, exclusion criteria, and estimation methods, please refer to
+the Supplementary Material.
 
@@
 fewer houses than those who did not earn financial rewards. While the result
-may seem counter-intuitive, it actually attests the effectiveness of the
+seems counter-intuitive, it actually attests the effectiveness of the
 treatment. This is because we offered incentives for subjects to exterminate
-larvae and find breeding sites, but not to visit a greater number of
-households. As a result, participants in the two treatment groups did a
-thorough job in each household, which explains the lower number of visits
-during the allotted time. We find that subjects in the individual and in the
-collective bonus groups visited $-9.879$ (CI: [XXX, XXX], $p-$value $= 0.XXX$)
-and $-7.554$ (CI: [XXX, XXX], $p-$value $= 0.XXX$) households, respectively.
+larvae and find breeding sites, not to visit a greater number of households. As
+a result, participants in the two treatment groups did a thorough job in each
+household, which explains the lower number of visits during the allotted time.
+We find that subjects in the individual and in the collective bonus groups
+visited $-9.879$ (CI: [XXX, XXX], $p-$value $= 0.XXX$) and $-7.554$ (CI: [XXX,
+XXX], $p-$value $= 0.XXX$) households, respectively.
 
@@
 participants in the individual bonus treatment arm visited $-8.044$ (CI: [XXX,
-XXX], $p-$value $= 0.XXX$) fewer houses than the control, and those in the
-collective bonus group visited $-6.479$ (CI: [XXX, XXX], $p-$value $= 0.XXX$).
+XXX], $p-$value $= 0.XXX$) houses than the control, and those in the collective
+bonus group visited $-6.479$ (CI: [XXX, XXX], $p-$value $= 0.XXX$).
 
@@
 group. The effect for those in the collective bonus group is 21.512 (CI: [XXX,
-XXX], $p-$value $= 0.XXX$), slightly smaller than for the first treatment.
+XXX], $p-$value $= 0.XXX$), slightly smaller than for the individual treatment.
 
-Collective incentivized teams are more effective in finding larvae. In our
-study, collectively incentivized subjects have 16.3\% more chance to find
-larvae than non incentivized workers. Finding larvae is harder, and the
-detection chances profit from teamwork. If teams are cooperating, searching the
-house becomes more natural, and they can coordinate to do a more thorough job.
-Additionally, the detection tends to be excludable: one individual finding
-larvae makes the chances of keep finding larvae in the household considerably
-smaller. Collective bonus is not excludable within the teams, making them
-cooperate more to get the reward.
+Teams which received collective bonuses are the most effective in finding
+larvae. Subjects who worked in pairs have a 16.3% (CI: [XXX, XXX], $p-$value =
+$0.XXX$) higher likelihood of finding larvae than those in the control group.
+Locating mosquito larvae is a difficult task, thus the probability of
+successfully completing the task increases when subjects work in teams.
+Furthermore, our collective bonus scheme was not excludable within the teams,
+thus health care workers had an incentive to cooperate and receive higher
+rewards.
+
+## Disease Incidence
+\label{sub:incidence}
+
+We evaluate the effect of the treatment on the disease incidence with two
+models. The first is a differences-in-differences model that assesses whether
+the intervention _per se_ had any effect on dengue hospitalisations in the city
+of Rio Verde. The second model compares disease incidence in each of the
+treatment statuses with disease incidence in the control group. The unit of
+analysis is the census tract. Table \ref{tab:incidence} displays the results
+for our first model, in which we test the impact of our intervention after 4,
+8, 12, and 16 weeks. The last column shows how collective incentives compare
+with individual bonuses, with the latter considered as the control group.
+
+\begin{table}[!htbp] \centering 
+  \caption{Disease Incidence -- Differences in Differences Model} 
+  \label{difindifdiseases} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{5}{c}{\textit{Dependent Variable:}} \\ 
+\cline{2-6} 
+\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
+& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (Indv. x Collect.) \\ 
+\hline \\[-1.8ex] 
+ DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
+  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
+  & & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
+Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:} & \multicolumn{5}{r}{DID stands for the differences-in-differences estimator.}
+& \multicolumn{5}{r}{Robust standard errors clustered at the census tract level in parenthesis.} \\ 
+& \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX], $p-$value
+= $0.XXX$) if we take both treatments and compare them with the control group.
+The result is consistent around fewer weeks before and after the intervention,
+but it does not reach conventional levels of statistical significance. This
+suggests that the treatment effect is probably small. The comparison between
+the two treatment statuses show an impact of 2.9\% fewer infections in the
+collective bonus group. However, the result is also not statistically
+significant.
+
+In our second model, we measure the effect of the reward schemes on the number
+of hospitalisations per census tract. Table \ref{fig:census} shows
+hospitalisation counts before the intervention, and then 15, 30, 60, 90, and
+between 15 to 30 days after the treatment.
+
+\begin{table}[!htbp]
+  \caption{Disease Incidence in Rio Verde Census Tracts} \centering 
+  \label{regdiseaseinc1} 
+\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent Variable:}} \\ 
+\cline{2-7} 
+\\[-1.8ex] & Before & 15 Days & 30 Days & 60 Days & 90 Days & 30-60 Days \\ 
+& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
+\hline \\[-1.8ex] 
+ Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
+  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
+  & & & & & & \\ 
+ Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
+  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
+Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{Robust standard errors clustered at the census tract level in parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
+\end{tabular} 
+\end{table}
+
+Compared to the control group, neither treatment had an impact on disease
+incidence in the Rio Verde census tracts. Yet, the coefficients are negative,
+what indicates that should an impact have occurred, the intervention would
+have lowered dengue incidence in the treated areas.
+
+# Discussion
+\label{sec:discussion}
 

### 2020-10-13 manuscript/article.Rmd
add discussion, revise other sections

--- 2020-10-11 paper/article.Rmd
@@
 title:  |
-        | Long Article Title:
-        | A Very Long Subtitle
+        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes Aegypti* Control Programme in Brazil
 author: 
@@
 date: \today
-thanks: "The authors thank Professors John and Jane Doe for their helpful comments."
-abstract: "This is a personal article template for RMarkdown.
-It uses Linux Libertine and Inconsolata fonts, British English, double-spaced text and numbered sections.
-The colours are personalised too: URLs are in dark blue, internal links are in mahogany and the table of contents is in black.
-The template also has pre-formatted entries for the abstract, keywords and JEL classification codes.
-You need to install `R` (and the `rmarkdown` package), `pandoc` and a `TeX` system to compile the pdf.
-In case you don't want to download large `TeX` binaries, I recommend you to install the great `TinyTeX R` package.
-A quick note: if you want to use colons in the abstract or the `thanks` entry, please don't forget to put the whole text in quotes.
-Otherwise, YAML might not parse it correctly.
-I hope you find this template useful and feel free to send me a message if you have any suggestions."
+thanks: "We thank Louise Araújo, Catarina Roman, David Skarbek, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
+Special thanks to XXXX for their excellent research assistance.
+Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
+abstract: ""
 abstractspacing: double
-keywords: R Markdown; pandoc; template
-jelcodes: A00, B11, C22
+keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field trial, preventive health care
 fontsize: 12pt
@@
 [`umberto.mignozzetti@emory.edu`](mailto:umberto.mignozzetti@emory.edu),
-<http://umbertomig.com>.
+<http://umbertomig.com>. Corresponding author.
 
@@
 incidence, but the coefficients only reach statistical significance when we
-combine the two treatments together and contrast them with the control group.
-Overall, the findings suggest that monetary payments are an effective method of
+combine the two treatments and contrast them with the control group. Overall,
+the findings suggest that monetary payments are an effective method of
 improving health worker performance, yet more research is needed to assess
@@
 
-\begin{table}[ht] 
-  \centering 
-  \small
+\begin{table}[ht] \centering 
   \caption{Field Productivity} 
@@
 \hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{Robust standard errors in parentheses. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\hline\\[-1.8ex]
+\multicolumn{5}{l}{\footnotesize \textbf{Note}: Robust standard errors
+clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
+$^{**}$p$<$0.05; $^{***}$p$<$0.01.} 
 \end{tabular} 
@@
 
-We evaluate the effect of the treatment on the disease incidence with two
-models. The first is a differences-in-differences model that assesses whether
-the intervention _per se_ had any effect on dengue hospitalisations in the city
-of Rio Verde. The second model compares disease incidence in each of the
-treatment statuses with disease incidence in the control group. The unit of
+We employ two models to evaluate the effect of the treatment on dengue
+incidence. The first is a differences-in-differences model that assesses
+whether the intervention _per se_ had any effect on dengue hospitalisations in
+the city of Rio Verde. The second model compares dengue incidence in each of
+the treatment statuses with incidence figures in the control group. The unit of
 analysis is the census tract. Table \ref{tab:incidence} displays the results
@@
 
-\begin{table}[!htbp] \centering 
+\begin{table}[ht] \centering 
   \caption{Disease Incidence -- Differences in Differences Model} 
-  \label{difindifdiseases} 
-\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
+  \label{tab:incidence} 
+\begin{tabular}{@{\extracolsep{1pt}}lccccc} 
 \\[-1.8ex]\hline 
@@
 \\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
-& (full) & (12 weeks) & (8 weeks) & (4 weeks) & (Indv. x Collect.) \\ 
+& (Full) & (12 Weeks) & (8 Weeks) & (4 Weeks) & (Indv. x Collect.) \\ 
 \hline \\[-1.8ex] 
- DID & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
+ Diff-in-diff & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
   & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
@@
 \hline \\[-1.8ex] 
-\textit{Note:} & \multicolumn{5}{r}{DID stands for the differences-in-differences estimator.}
-& \multicolumn{5}{r}{Robust standard errors clustered at the census tract level in parenthesis.} \\ 
-& \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\multicolumn{6}{l}{\footnotesize \textbf{Note}: Robust standard errors
+clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
+$^{**}$p$<$0.05; $^{***}$p$<$0.01.} 
 \end{tabular} 
@@
 The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX], $p-$value
-= $0.XXX$) if we take both treatments and compare them with the control group.
+$= 0.XXX$) if we take both treatments and compare them with the control group.
 The result is consistent around fewer weeks before and after the intervention,
@@
 suggests that the treatment effect is probably small. The comparison between
-the two treatment statuses show an impact of 2.9\% fewer infections in the
-collective bonus group. However, the result is also not statistically
-significant.
+the two treatment statuses show an impact of 2.9\% (CI: [XXX, XXX], $p-$ value
+$= 0.XXX$) fewer infections in the collective bonus group. However, the result
+is also not statistically significant.
 
-In our second model, we measure the effect of the reward schemes on the number
-of hospitalisations per census tract. Table \ref{fig:census} shows
-hospitalisation counts before the intervention, and then 15, 30, 60, 90, and
-between 15 to 30 days after the treatment.
-
-\begin{table}[!htbp]
+\begin{table}[ht]
   \caption{Disease Incidence in Rio Verde Census Tracts} \centering 
-  \label{regdiseaseinc1} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
+  \label{tab:census} 
+\begin{tabular}{@{\extracolsep{1pt}}lcccccr}
 \\[-1.8ex]\hline 
@@
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{6}{r}{Robust standard errors clustered at the census tract level in parenthesis. $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
+\multicolumn{7}{l}{\footnotesize \textbf{Note}: Robust standard errors
+clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
+$^{**}$p$<$0.05; $^{***}$p$<$0.01.}\\
 \end{tabular} 
@@
 
+In our second model, we measure the effect of reward schemes on the number of
+hospitalisations per census tract. Table \ref{tab:census} shows hospitalisation
+counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
+days after the treatment.
+
 Compared to the control group, neither treatment had an impact on disease
-incidence in the Rio Verde census tracts. Yet, the coefficients are negative,
-what indicates that should an impact have occurred, the intervention would
-have lowered dengue incidence in the treated areas.
+incidence in the Rio Verde census tracts. The treatment effect is not
+statistically different from zero in any model specification. Yet, the
+coefficients are negative, what indicates that should an impact have occurred,
+the intervention would have lowered dengue incidence in the treated areas.
 
@@
 
+We show that monetary incentives increase the productivity of community health
+care workers in Brazil. We contrast a control group (which received a flat
+performance fee) with two treatment groups, one which received an individual
+performance bonus, and second one that received a collective performance
+incentive. We find that both treatments increase the number of breeding sites
+encountered, and that collective incentives outperform individual performance
+rewards when the task is more laborious and excludable (exterminating larvae).
+Finally, the control group presented a high incidence of houses visited in less
+than two minutes apart from each other, which suggests that the workers may
+not carry their tasks as intended in the absence of incentives. In a nutshell,
+monetary incentives work.
+
+Our conclusions are consistent with the results of comparable studies conducted
+in other settings, such as education [@duflo2012incentives] and private firms
+[@bandiera2013team]. They also provide further evidence that incentivising team
+work is more effective for labour-intensive tasks, which opens a new avenue for
+research in preventive health care.
+
+Regarding the effect of incentives on city-level dengue incidence, we find only
+mixed results. Why did the treatment not work as we planned? We believe the
+treatment was not strong enough. Our treatment probably did not cover enough
+areas to ensure there was no mosquitos around the assigned blocks. As mosquitos
+can travel for long distances, the treatment might not have been sufficient.
+Also, Rio Verde had significant rates of dengue incidence during our
+experiment, reaching 3,411 reported infections from January to September 2018
+[@goias2020]. Therefore, maybe the treatment works only when applied for
+longer periods of time or in more neighbourhoods.
+
+In this respect, our study suggests is that even though health care workers may
+be motivated, their efforts do not necessarily lead to a reduction in mosquito
+infections. Higher field productivity does not guarantee that the *Aedes
+aegypti* can be eradicated. To our knowledge, we are one of the first studies
+to highlight this issue. Future research may explore the reasons why this is
+the case and if the disconnect between the two can also be identified in other
+areas.
+
+## Limitations
+\label{sub:limitations}
+
+The study has important limitations. First, we ran our experiment for a small
+period of time and in a particular Brazilian city, thus the findings may not
+generalise to other locations. Second, our experiment needed a longer and wider
+coverage to measure whether the treatment has a significant impact on dengue
+incidence, as the effect seems smaller than expected. Third, we included a
+post-treatment adjustment to ensure the balance of our territorial variables.
+Although using matching estimators to improve balance is in line with the best
+statistical practices, it requires additional assumptions. Finally, the
+experiment only measures the impact of financial rewards on worker performance,
+and it does not assess the effect of non-monetary incentives, such as
+motivational messages or constant feedback, which may be useful alternatives in
+jurisdictions where legal or financial constraints may prevent the government
+from distributing financial bonuses to civil servants.
+
+## Public Health Implications
+\label{sub:implications}
+
+The experiment has important lessons for policy-making. *Aedes aegypti*-borne
+diseases are a significant public health concern, especially in developing
+nations. Results of this study indicate that monetary rewards play a major role
+in motivating civil servants, and that peer incentives are more cost-effective
+than individual bonuses. Finally, the article shows anti-mosquito campaigns
+require a sustained effort to guarantee their success, and we still have no
+robust evidence that worker productivity alone is sufficient to reduce dengue
+infections.
+
 \newpage

### 2020-10-13 manuscript/article.Rmd
add abstract

@@
 title:  |
-        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes Aegypti* Control Programme in Brazil
+        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
 author: 
@@
 date: \today
-thanks: "We thank Louise Araújo, Catarina Roman, David Skarbek, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
+thanks: "We thank Louise Araújo, Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
 Special thanks to XXXX for their excellent research assistance.
 Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
-abstract: ""
-abstractspacing: double
-keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field trial, preventive health care
+abstract:    |
+    | __Objectives.__ To quantify the impact of individual and collective monetary rewards on the performance of health care workers assigned to find and exterminate *Aedes aegypti*, as well as their effect on dengue hospitalisations.
+    | __Methods.__ We hired and trained subjects to visit households, find *A.
+aegypti* breeding sites, and exterminate mosquito larvae in the city of Rio Verde, Brazil, in May 2018.
+We provided individual and team bonuses to the two treatment groups, whereas the control group received a flat compensation for completing their tasks.
+    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment status (individual and team bonuses) and team bonuses also improved larvae extermination.
+The intervention decreased the disease incidence in 10.3%, but the findings are not statistically significant across all model specifications.
+    | __Conclusions.__ Performance bonuses improve productivity in public service provision, yet more research is needed to asssess whether higher health care worker performance decreases dengue hospitalisations.
+    | __Public Health Implications.__ *A.
+aegypti* control programmes may benefit from alternative compensation schemes, specially when provided to teams.
+For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
+abstractspacing: onehalf
+keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field experiment, preventive health care
 fontsize: 12pt
@@
 We find that subjects in the individual and in the collective bonus groups
-visited $-9.879$ (CI: [XXX, XXX], $p-$value $= 0.XXX$) and $-7.554$ (CI: [XXX,
-XXX], $p-$value $= 0.XXX$) households, respectively.
+visited $-9.879$ (CI: [XXX, XXX]) and $-7.554$ (CI: [XXX, XXX]) households,
+respectively.
 
@@
 participants in the individual bonus treatment arm visited $-8.044$ (CI: [XXX,
-XXX], $p-$value $= 0.XXX$) houses than the control, and those in the collective
-bonus group visited $-6.479$ (CI: [XXX, XXX], $p-$value $= 0.XXX$).
+XXX]) houses than the control, and those in the collective bonus group visited
+$-6.479$ (CI: [XXX, XXX]).
 
 Incentivised teams find and clean more breeding sites than non-incentivised
-ones. Individually incentivised health workers find 25.118 (CI: [XXX, XXX],
-$p-$value $= 0.XXX$) more breeding sites than the non-incentivised control
-group. The effect for those in the collective bonus group is 21.512 (CI: [XXX,
-XXX], $p-$value $= 0.XXX$), slightly smaller than for the individual treatment.
+ones. Individually incentivised health workers find 25.118 (CI: [XXX, XXX])
+more breeding sites than the non-incentivised control group. The effect for
+those in the collective bonus group is 21.512 (CI: [XXX, XXX]), slightly
+smaller than for the individual treatment.
 
 Teams which received collective bonuses are the most effective in finding
-larvae. Subjects who worked in pairs have a 16.3% (CI: [XXX, XXX], $p-$value =
-$0.XXX$) higher likelihood of finding larvae than those in the control group.
-Locating mosquito larvae is a difficult task, thus the probability of
-successfully completing the task increases when subjects work in teams.
-Furthermore, our collective bonus scheme was not excludable within the teams,
-thus health care workers had an incentive to cooperate and receive higher
-rewards.
+larvae. Subjects who worked in pairs have a 16.3% (CI: [XXX, XXX]) higher
+likelihood of finding larvae than those in the control group. Locating mosquito
+larvae is a difficult task, thus the probability of successfully completing the
+task increases when subjects work in teams. Furthermore, our collective bonus
+scheme was not excludable within the teams, thus health care workers had an
+incentive to cooperate and receive higher rewards.
 
@@
 
-The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX], $p-$value
-$= 0.XXX$) if we take both treatments and compare them with the control group.
-The result is consistent around fewer weeks before and after the intervention,
-but it does not reach conventional levels of statistical significance. This
-suggests that the treatment effect is probably small. The comparison between
-the two treatment statuses show an impact of 2.9\% (CI: [XXX, XXX], $p-$ value
-$= 0.XXX$) fewer infections in the collective bonus group. However, the result
-is also not statistically significant.
+The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX]) if we take
+both treatments and compare them with the control group. The result is
+consistent around fewer weeks before and after the intervention, but it does
+not reach conventional levels of statistical significance. This suggests that
+the treatment effect is probably small. The comparison between the two
+treatment statuses show an impact of 2.9\% (CI: [XXX, XXX]) fewer infections in
+the collective bonus group. However, the result is also not statistically
+significant.
 

### 2020-10-13 manuscript/article.Rmd
small edits

@@
 For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
-abstractspacing: onehalf
+abstractspacing: single
 keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field experiment, preventive health care
@@
 We conducted a randomised field trial in Rio Verde, a municipality in the
-Brazilian Midwestern state of Goiás. Rio Verde had 229,000 inhabitants and 1,156
-confirmed dengue cases, one of highest counts in the state [@goias2020]. We used
-Facebook advertisements to recruit potential participants. The advertisements
-directed applicants to Google Forms, where we asked for their contact
-information. We sent a pre-treatment demographic survey to every applicant who
-provided a valid email address. At this stage, we excluded all individuals under
-18 years old. We invited the remaining applicants to our training session, which
-we ran on the 4^th^ of May, 2018. The meeting consisted of a lecture on *A.
-aegypti* vector biology and practical instructions on how to find and
-exterminate mosquito breeding sites. Those who did not attend the session were
-also excluded from the study.
+Brazilian Midwestern state of Goiás. Rio Verde had 229,000 inhabitants and
+1,156 confirmed dengue cases, one of highest counts in the state [@goias2020].
+We used Facebook advertisements to recruit potential participants. The
+advertisements directed applicants to Google Forms, where we asked for their
+contact information. We sent a pre-treatment demographic survey to every
+applicant who provided a valid email address. At this stage, we excluded all
+individuals under 18 years old and invited the remaining applicants to our
+training session, which we ran on the 4^th^ of May, 2018. The meeting consisted
+of a lecture on *A. aegypti* vector biology and practical instructions on how
+to find and exterminate mosquito breeding sites. Those who did not attend the
+session were also excluded from the study.
 
@@
 participants that they would receive a flat payment regardless of their
-performance (BRL 110 / USD 20 per subject). In the individual treatment group
+performance (BRL 110 / USD 25 per subject). In the individual treatment group
 ($n = 68$), we informed subjects that we would rank individual performances and
@@
 The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX]) if we take
-both treatments and compare them with the control group. The result is
+both treatments together and compare them with the control group. The result is
 consistent around fewer weeks before and after the intervention, but it does
@@
 
-The study has important limitations. First, we ran our experiment for a small
+The study has several limitations. First, we ran our experiment for a small
 period of time and in a particular Brazilian city, thus the findings may not

### 2020-10-13 manuscript/article.Rmd
small edits

@@
 abstract:    |
-    | __Objectives.__ To quantify the impact of individual and collective monetary rewards on the performance of health care workers assigned to find and exterminate *Aedes aegypti*, as well as their effect on dengue hospitalisations.
+    | __Objectives.__ To quantify the impact of monetary incentives on the performance of health care workers assigned to exterminate *Aedes aegypti*, as well as their effect on dengue hospitalisations.
     | __Methods.__ We hired and trained subjects to visit households, find *A.
-aegypti* breeding sites, and exterminate mosquito larvae in the city of Rio Verde, Brazil, in May 2018.
-We provided individual and team bonuses to the two treatment groups, whereas the control group received a flat compensation for completing their tasks.
+aegypti* breeding sites, and kill mosquito larvae in the city of Rio Verde, Brazil, in May 2018.
+We provided individual and team bonuses to the two treatment groups, while the control group received a flat compensation for completing their tasks.
     | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment status (individual and team bonuses) and team bonuses also improved larvae extermination.
@@
 health care workers [@clemens2014physicians; @muthmainnah2017improving;
-@ulrich2005does]. However, systematic reviews indicate that the available
+@ulrich2005does]. Nevertheless, systematic reviews indicate that the available
 evidence has serious methodological shortcomings, such as selection bias and
@@
 We conducted a randomised field trial in Rio Verde, a municipality in the
-Brazilian Midwestern state of Goiás. Rio Verde had 229,000 inhabitants and
-1,156 confirmed dengue cases, one of highest counts in the state [@goias2020].
-We used Facebook advertisements to recruit potential participants. The
-advertisements directed applicants to Google Forms, where we asked for their
-contact information. We sent a pre-treatment demographic survey to every
-applicant who provided a valid email address. At this stage, we excluded all
-individuals under 18 years old and invited the remaining applicants to our
-training session, which we ran on the 4^th^ of May, 2018. The meeting consisted
-of a lecture on *A. aegypti* vector biology and practical instructions on how
-to find and exterminate mosquito breeding sites. Those who did not attend the
-session were also excluded from the study.
+Brazilian Midwestern state of Goiás. In 2017, Rio Verde had 229,000 inhabitants
+and 1,156 confirmed dengue cases, one of highest counts in the state
+[@goias2020]. We used Facebook advertisements to recruit potential
+participants. The advertisements directed applicants to Google Forms, where we
+asked for their contact information. We sent a pre-treatment demographic survey
+to every applicant who provided a valid email address. At this stage, we
+excluded all individuals under 18 years old and invited the remaining
+applicants to our training session, which we ran on the 4^th^ of May, 2018. The
+meeting consisted of a lecture on *A. aegypti* vector biology and practical
+instructions on how to find and exterminate mosquito breeding sites. Those who
+did not attend the session were also excluded from the study.
 
@@
 The intervention took place on the 5^th^ of May, 2018. We randomly assigned
-subjects into three groups and directed each group to separate headquarters in
-order to avoid spillovers. In the control group ($n = 68$), we told
-participants that they would receive a flat payment regardless of their
-performance (BRL 110 / USD 25 per subject). In the individual treatment group
-($n = 68$), we informed subjects that we would rank individual performances and
-double the compensation for those who performed above the sample median (BRL
-220 / USD 50 per subject). In the collective treatment group ($n = 70$), we
-explained that we would rank the pair performance and double the payment for
-teams who presented results better than the sample median (BRL 220 / USD 50 per
-subject). Participants worked in pairs and were aware of other groups, but they
-did not know about the different treatment conditions. The teams received a
-leaflet with a map of the area they should cover. The route comprised of two to
-three blocks and contained around 120 houses.
+subjects into three groups and directed each group to separate headquarters to
+avoid spillovers. In the control group ($n = 68$), we told participants that
+they would receive a flat payment regardless of their performance (BRL 110 /
+USD 25 per subject). In the individual treatment group ($n = 68$), we informed
+subjects that we would rank individual performances and double the compensation
+for those who performed above the sample median (BRL 220 / USD 50 per subject).
+In the collective treatment group ($n = 70$), we explained that we would rank
+the pair performance and double the payment for teams who presented results
+better than the sample median (BRL 220 / USD 50 per subject). Participants
+worked in pairs and were aware of other groups, but they did not know about the
+different treatment conditions. The teams received a leaflet with a map of the
+area they should cover. The route comprised of two to three blocks and
+contained around 120 houses.
 

### 2020-10-13 manuscript/article.Rmd
many small edits

@@
 rewards when the task is more laborious and excludable (exterminating larvae).
-Finally, the control group presented a high incidence of houses visited in less
+Lastly, the control group presented a high incidence of houses visited in less
 than two minutes apart from each other, which suggests that the workers may
@@
 motivational messages or constant feedback, which may be useful alternatives in
-jurisdictions where legal or financial constraints may prevent the government
-from distributing financial bonuses to civil servants.
+jurisdictions where legal or financial constraints prevent the government from
+distributing financial bonuses to civil servants.
 

### 2020-10-14 manuscript/article.Rmd
small edits to article, add to-do to README

@@
 abstract:    |
-    | __Objectives.__ To quantify the impact of monetary incentives on the performance of health care workers assigned to exterminate *Aedes aegypti*, as well as their effect on dengue hospitalisations.
+    | __Objectives.__ To quantify the impact of financial incentives on the productivity of health personnel combating *Aedes aegypti* and on city-level numbers of dengue hospitalisations.
     | __Methods.__ We hired and trained subjects to visit households, find *A.
 aegypti* breeding sites, and kill mosquito larvae in the city of Rio Verde, Brazil, in May 2018.
-We provided individual and team bonuses to the two treatment groups, while the control group received a flat compensation for completing their tasks.
-    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment status (individual and team bonuses) and team bonuses also improved larvae extermination.
-The intervention decreased the disease incidence in 10.3%, but the findings are not statistically significant across all model specifications.
-    | __Conclusions.__ Performance bonuses improve productivity in public service provision, yet more research is needed to asssess whether higher health care worker performance decreases dengue hospitalisations.
+We provided individual and team bonuses to two treatment groups, while the control group received a flat compensation for completing their tasks.
+    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment groups (individual and team bonuses) and the collective treatment also improved larvae extermination.
+The intervention lowered dengue hospitalisations in 10.3%, but the result is not consistent across all model specifications.
+    | __Conclusions.__ Performance bonuses improve the performance of health personnel, yet more research is needed to assess whether higher worker productivity decreases dengue hospitalisations.
     | __Public Health Implications.__ *A.
@@
 abstractspacing: single
-keywords: Aedes aegypti, dengue, financial incentives, mosquito control, randomised field experiment, preventive health care
+keywords: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
 fontsize: 12pt
@@
 each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
-for most *Aedes*-transmitted diseases [@sridhar2018effect;
-@world2017dengue], we have seen a number of dengue and Zika outbreaks in Asia,
-the Caribbean, South America, and the United States [@carlson2016ecological;
-@leta2018global]. Chikungunya virus, which was endemic only to Africa, has
-already been reported in every region of the world [@grandadam2011chikungunya;
-@kraemer2015global; @mayer2017emergence].
+for most *Aedes*-transmitted diseases [@world2017dengue], we have seen a number
+of dengue and Zika outbreaks in Asia, the Caribbean, South America, and the
+United States [@carlson2016ecological; @leta2018global]. Chikungunya virus,
+previously endemic only to Africa, has already been reported in every region of
+the world [@grandadam2011chikungunya; @kraemer2015global; @mayer2017emergence].
 
@@
 health care workers [@clemens2014physicians; @muthmainnah2017improving;
-@ulrich2005does]. Nevertheless, systematic reviews indicate that the available
-evidence has serious methodological shortcomings, such as selection bias and
-inadequate experimental blinding, what limits the generalisability of current
-findings [@bassani2013financial; @flodgren2011overview; @scott2011effect].
-Moreover, it remains unclear which rewarding schemes have a stronger effect on
-health care worker performance [@fainman2020design], and whether monetary
-incentives have a sustained effect on patient outcomes [@jha2012long;
-@langdown2014use].
+@ulrich2005does]. Nevertheless, systematic reviews indicate that the
+generalisability of the available evidence is limited due to methodological
+shortcomings, as several studies suffer from selection bias and inadequate
+experimental blinding [@bassani2013financial; @flodgren2011overview;
+@scott2011effect]. Moreover, it remains unclear which rewarding schemes have a
+stronger effect on health care worker performance [@fainman2020design], and
+whether monetary incentives have a sustained effect on patient outcomes
+[@jha2012long; @langdown2014use].
 
@@
 prevention practices. Then, subjects asked whether they were allowed to inspect
-house yard. If granted permission, they entered the household and searched for
-clean breeding sites, such as pots filled with clear water, and recipients
-containing larvae. Upon exterminating a breeding site (pouring out the
-accumulated water, for example), subjects had to report their task by taking a
-photo on their cellphones. When they discovered larvae, they had to record a
-video showing the larvae before exterminating it. At the end of their visit,
-they had to take a picture of the household to account for their presence in
-the location.
+the resident's house yard. If granted permission, they entered the household
+and searched for clean breeding sites, such as pots filled with clear water,
+and for recipients containing larvae. Upon exterminating a breeding site
+(pouring out the accumulated water, for example), subjects had to report their
+task by taking a photo on their cellphones. When they discovered larvae,
+participants had to record a video showing the larvae before exterminating
+them. At the end of their visit, subjects had to take a picture of the household to
+account for their presence in the location.
 
-This study evaluates two outcomes. The first outcome is field productivity of
-the health care workers. We measure worker productivity by coding cellphone
+This study evaluates two outcomes. The first outcome is the field productivity
+of health care providers. We measure worker productivity by coding cellphone
 data collected during the intervention into four indicators: 1) the number of
@@
 exterminated larvae. We analyse the data using ordinary least squares with
-robust standard errors [@imbens2016robust]. We estimate the statistical power
-of the study assuming a treatment effect of 0.15 standard deviations.
+robust standard errors [@imbens2016robust]. We estimate the statistical
+power of the study assuming a treatment effect of 0.15 standard deviations.
 
@@
 distribution of our intervention. We also compare dengue incidence in each of
-the treatment statuses with incidence figures in the control group. The unit of
-analysis is the census tract in both models. We employ a
-differences-in-differences estimator to assess the treatment effects
+the treatment statuses with incidence figures in the control group. In both
+models, the unit of analysis is the census tract. We employ a
+differences-in-differences estimator to measure the treatment effects
 [@angrist2008mostly].
@@
 
+\vspace{.3cm}
+
 \begin{table}[ht] \centering 
@@
 significant.
+
+\vspace{.3cm}
 

### 2020-10-14 manuscript/article.Rmd
change title

@@
 title:  |
-        | Financial Incentives and Health Care Prevention: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
+        | Financial Incentives and Health Care Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
 author: 

### 2020-10-14 manuscript/article.Rmd
small edits in methods section, change title README

@@
 applicants to our training session, which we ran on the 4^th^ of May, 2018. The
-meeting consisted of a lecture on *A. aegypti* vector biology and practical
+meeting involved a lecture on *A. aegypti* vector biology and practical
 instructions on how to find and exterminate mosquito breeding sites. Those who
@@
 
-We employ two models to evaluate the effect of the treatment on dengue
-incidence. The first is a differences-in-differences model that assesses
+We employ two models to evaluate the effect of monetary incentives on dengue
+incidence. The first is a differences-in-differences model that tests
 whether the intervention _per se_ had any effect on dengue hospitalisations in
@@
 analysis is the census tract. Table \ref{tab:incidence} displays the results
-for our first model, in which we test the impact of our intervention after 4,
+for our first model, in which we measure the impact of our intervention after 4,
 8, 12, and 16 weeks. The last column shows how collective incentives compare

### 2021-02-13 manuscript/article.Rmd
add abstract and author summary, small edits

@@
 date: \today
-thanks: "We thank Louise Araújo, Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
+thanks: "We thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
 Special thanks to XXXX for their excellent research assistance.
 Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
-abstract:    |
-    | __Objectives.__ To quantify the impact of financial incentives on the productivity of health personnel combating *Aedes aegypti* and on city-level numbers of dengue hospitalisations.
-    | __Methods.__ We hired and trained subjects to visit households, find *A.
-aegypti* breeding sites, and kill mosquito larvae in the city of Rio Verde, Brazil, in May 2018.
-We provided individual and team bonuses to two treatment groups, while the control group received a flat compensation for completing their tasks.
-    | __Results.__ Financial bonuses increased the number of cleaned breeding sites in both treatment groups (individual and team bonuses) and the collective treatment also improved larvae extermination.
-The intervention lowered dengue hospitalisations in 10.3%, but the result is not consistent across all model specifications.
-    | __Conclusions.__ Performance bonuses improve the performance of health personnel, yet more research is needed to assess whether higher worker productivity decreases dengue hospitalisations.
-    | __Public Health Implications.__ *A.
-aegypti* control programmes may benefit from alternative compensation schemes, specially when provided to teams.
-For this strategy to succeed, financial incentives have to be distributed widely as their aggregate effect is limited.
-abstractspacing: single
-keywords: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
 fontsize: 12pt
@@
 bibliography: references.bib
+biblio-style: unsrtnat
 output:
@@
 
+\begin{abstract}
+
+\footnotesize
+
+\noindent \textbf{Background}. Mosquito control strategies are the primary
+means to reduce \textit{Aedes aegypti} infections worldwide. However,
+insecticide spraying is conducted inconsistently across the developing world.
+Recent studies indicate that financial incentives may increase the productivity
+of health personnel, yet there is little evidence on the impact of monetary
+rewards on \textit{A. aegypti}-reduction programmes. We evaluated whether
+individual and collective financial incentives improves the performance of
+healthcare workers fighting \textit{A. aegypti}, as well as their effect on
+city-level numbers of dengue hospitalisations.
+
+\noindent \textbf{Methodology/Principal findings}. We hired and trained
+subjects to visit households, find \textit{A. aegypti} breeding sites, and kill
+mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
+trial, we provided individual and team bonuses to two treatment groups, while
+the control group received a flat compensation for completing their tasks.
+Financial bonuses increased the number of cleaned breeding sites in both
+treatment groups (individual and team bonuses) and the collective treatment
+also improved larvae extermination. The intervention lowered dengue
+hospitalisations in 10.3\%, but the result was not consistent across all model
+specifications.
+
+\noindent \textbf{Conclusions/Significance}. \textit{A. aegypti} control
+programmes may benefit from alternative compensation schemes, specially when
+provided to teams. For this strategy to succeed, financial incentives have to
+be distributed widely as their aggregate effect is limited. More research is
+needed to assess whether higher worker productivity decreases dengue
+hospitalisations.
+
+\end{abstract}
+
+\renewcommand{\abstractname}{Author Summary}
+\begin{abstract}
+
+\footnotesize
+
+\noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
+chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
+people per year. As there is no safe vaccine for many of these infections,
+insecticide spraying and breeding site cleaning are the best means to fight the
+mosquito. In several developing countries, which host the majority of cases of
+\textit{A. aegypti} infections, anti-mosquito campaigns are carried out
+inconsistently, thus it is crucial to find ways to improve the productivity of
+healthcare workers in charge of these tasks. We designed a randomised field
+experiment that provided individual and collective financial incentives to
+healthcare agents in a Brazilian city and tested the effect of monetary rewards
+on their productivity and on the number of dengue hospitalisations. We find
+that financial bonuses improved the number of cleaned breeding sites in both
+treatment groups (individual and team incentives) and that the collective
+treatment also improved larvae extermination. The impact of our treatment on
+city-level hospitalisations was not consistent across all specifications. In
+sum, financial incentives may be used to boost field productivity in
+anti-\textit{A. aegypti} programmes, but we suggest that further research is
+required to evaluate how healthcare worker productivy relates to aggregate
+disease outcomes.
+
+\vspace{.3cm}
+\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
+\end{abstract}
+
+\normalsize
+
+\newpage
 # Introduction
@@
 In this paper, we explore how financial incentives affect the productivity of
-health care personnel involved in *A. aegypti* control and measure how monetary
-rewards impact dengue hospitalisations. We run a randomised field experiment in
-the city of Rio Verde, Brazil, which has experienced a peak in dengue
-infections in the last years. We hired and trained teams of health care workers
-to perform simplified procedures designed to exterminate *A. aegypti* breeding
-sites. Our experiment consisted of two treatment arms plus a control condition.
-The control group received a fixed compensation for completing their tasks, and
-we offered individual or collective bonuses to those allocated in the two
-treatment groups. We then measured how the different compensations schemes
-affect the number of breeding sites discovered, larvae exterminated, and
-city-level dengue incidence.
+health care personnel involved in *A. aegypti* control and how they impact
+dengue hospitalisations. We run a randomised field experiment in the city of
+Rio Verde, Brazil, which has experienced a peak in dengue infections in the
+last years. We hired and trained teams of health care workers to perform
+simplified procedures designed to exterminate *A. aegypti* breeding sites. Our
+experiment consisted of two treatment arms plus a control condition. We offered
+individual or collective bonuses to those allocated in the two treatment
+groups, while the control group received a fixed compensation for completing
+their tasks. We then measured how the different reward schemes affect the
+number of breeding sites discovered, larvae exterminated, and city-level dengue
+incidence.
 
@@
 apart from each other, which suggests that workers may cheat in the absence of
-financial incentives. When we combine both treatments, we also find that the
+monetary incentives. When we combine both treatments, we also find that the
 intervention decreases dengue incidence in 10.3%, but the results are not
@@
 Brazilian Midwestern state of Goiás. In 2017, Rio Verde had 229,000 inhabitants
-and 1,156 confirmed dengue cases, one of highest counts in the state
+and 1,156 confirmed dengue cases, one of highest counts in Goiás
 [@goias2020]. We used Facebook advertisements to recruit potential
@@
 
-Table \ref{tab:covbal} displays the attrition tests, the covariate balance
-tests, and the territorial assignment before and after applying propensity score
-matching [@rosenbaum1985constructing] on census tract characteristics. We
-observe no significant differences regarding attrition rates, indicating that
-the treatment was correctly randomised. Participants' demographics are also
-similar across all groups, and the matching technique successfully balanced the
-territorial assignment.
+Table \ref{tab:covbal} displays the attrition and covariate balance tests for
+our experiment, and the territorial assignment before and after applying
+propensity score matching [@rosenbaum1985constructing] on census tract
+characteristics. We observe no significant differences regarding attrition
+rates, indicating that the treatment was correctly randomised. Participant 
+demographics are also similar across all groups, thus the matching technique
+successfully balanced the territorial assignment.
 
@@
 USD 25 per subject). In the individual treatment group ($n = 68$), we informed
-subjects that we would rank individual performances and double the compensation
+subjects that we would rank each subject separately and double the compensation
 for those who performed above the sample median (BRL 220 / USD 50 per subject).
 In the collective treatment group ($n = 70$), we explained that we would rank
-the pair performance and double the payment for teams who presented results
-better than the sample median (BRL 220 / USD 50 per subject). Participants
-worked in pairs and were aware of other groups, but they did not know about the
-different treatment conditions. The teams received a leaflet with a map of the
-area they should cover. The route comprised of two to three blocks and
-contained around 120 houses.
+the performance of each group and double the payment for those teams whose
+results were higher than the sample median (BRL 220 / USD 50 per subject).
+Participants worked in pairs and were aware of other groups, but they did not
+know about the different treatment conditions. The teams received a leaflet
+with a map of the area they should cover. Each route included around 120 houses
+in two or three blocks.
 
-A typical visit to a household consisted of the following steps. First,
-participants rang the doorbell and explained that the municipality had
-experienced a dengue fever outbreak. They instructed dwellers on how to lower
-dengue incidence and handed them a leaflet with information about dengue
-prevention practices. Then, subjects asked whether they were allowed to inspect
-the resident's house yard. If granted permission, they entered the household
-and searched for clean breeding sites, such as pots filled with clear water,
-and for recipients containing larvae. Upon exterminating a breeding site
-(pouring out the accumulated water, for example), subjects had to report their
-task by taking a photo on their cellphones. When they discovered larvae,
-participants had to record a video showing the larvae before exterminating
-them. At the end of their visit, subjects had to take a picture of the household to
-account for their presence in the location.
+A typical household visit consisted of the following steps. First, participants
+rang the doorbell and explained that the municipality had experienced a dengue
+fever outbreak. They instructed dwellers on how to lower dengue incidence and
+handed them a leaflet with information about dengue prevention practices. Then,
+subjects asked whether they were allowed to inspect the resident's house yard.
+If granted permission, they entered the household and searched for clean
+breeding sites, such as pots filled with clear water, and for recipients
+containing larvae. Upon exterminating a breeding site (pouring out the
+accumulated water, for example), subjects had to report their task by taking a
+photo on their cellphones. When they discovered larvae, participants had to
+record a short video showing the larvae before exterminating them. At the end
+of each visit, subjects had to take a picture of the household to account for
+their presence in the location.
 
@@
 We pre-registered the experiment on the Evidence in Governance and Policy
-(EGAP) website (<https://osf.io/6q8vu/>) and received IRB approval from New
+(EGAP) website (<https://osf.io/6q8vu/>), and received IRB approval from New
 York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The

### 2021-02-13 manuscript/article.Rmd
small changes to author summary

@@
 chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
-people per year. As there is no safe vaccine for many of these infections,
+people per year. As there are no safe vaccines for many of these infections,
 insecticide spraying and breeding site cleaning are the best means to fight the
-mosquito. In several developing countries, which host the majority of cases of
+mosquito. In several developing countries, which host the majority of
 \textit{A. aegypti} infections, anti-mosquito campaigns are carried out
@@
 anti-\textit{A. aegypti} programmes, but we suggest that further research is
-required to evaluate how healthcare worker productivy relates to aggregate
+required to evaluate how healthcare worker productivy impacts city-level
 disease outcomes.

### 2021-02-22 appendix/appendix.Rmd
adding appendix

---
title: |
       | Supplementary Materials for "Financial Incentives and Health Care Provision: Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil"
author:
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

\appendix

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)

# Random Seed
set.seed(597154) # From random.org
```

```{r, include=FALSE, warning=FALSE, echo=FALSE}
## Initializing

# Start
rm(list=ls())

# R CRAN
r <- getOption("repos")
r["CRAN"] <- "https://cloud.r-project.org/"
options(repos = r)

# Install required packages
pkgs <- c('tidyverse', 'ggmap', 'magrittr', 
          'sf', 'gpclib', 'sp', 'rgdal', 
          'readxl', 'ggthemes', 'stringr', 
          'lmtest', 'estimatr', 'sandwich', 
          'stargazer', 'maptools', 'gridExtra',
          'WeightIt', 'robustHD', 'kableExtra',
          'lfe')

installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T)
} 
invisible(lapply(pkgs, installIfNot))

# Load packages
invisible(lapply(pkgs, require, character.only = T))
rm(pkgs, installIfNot, r)

# Load data
load('../data/incentives_healthcare.RData')
```

# A Theory of Service Provision under Moral Hazard in Teams

Consider a strategic interaction between two healthcare workers and a government agency.\footnote{This model was inspired in @bolton2005contract. It is a particular version of their model, aimed at illustrate the effects of our treatment.} The agency hires healthcare workers to provide preventive healthcare. And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.

From the perspective of healthcare workers, teams perform preventive healthcare tasks. To inspect a house and eliminate mosquito breeding sites, preventive healthcare workers visit the households in pairs or threesomes. Supposedly, this increases efficiency as it helps the team cover more territory and be more careful in the areas they inspect individually. Team structures also help in terms of lowering free-riding and increasing incentives for cooperative work. To capture this, we assume that a given worker $i$ divides her effort into two tasks: own work effort ($e_i$) and helping efforts ($h_i$). To capture the costs of effort, we assume the following convex cost function $\dfrac{c}{2}(e_i^2 + h_i^2)$, where $c>0$ represents the changes in marginal costs of effort and help.

Due to the nature of preventive care work, the policy outcome is probabilistic. Preventive healthcare aims to lower the chance of a person getting sick. For example, washing one's hands lowers the chance of a person getting the flu, but from time to time, a person gets the flu regardless of how many times she washes her hands. The only difference is that a person who washes her hands constantly has a lower chance of getting sick and will get sick fewer times during her lifespan. For this reason, we denote the probability of a successful provision of the service by a pair $i$ and $j$ of healthcare workers, as $P(e_i, h_i, e_j, h_j)$. For simplicity, we assume that the probabilities are separable, with $P(e_i, h_i, e_j, h_j) = P_i(e_i, h_j) + P_j(e_j, h_i)$. To make the output more concrete, assume that a given worker $i$ has an individual probability of $P_i(e_i, h_j) = e_i(1+h_j)$ of successfully lowering the disease burden with her effort ($e_i$) and the help of her peer ($h_j$).

From the perspective of the agency, the successful work grants a benefit of $B>0$. This benefit represents the social gains of lowering the amount of disease incidence in the municipality. For example, the payoff could be the amount of money saved from fewer hospitalizations or the economic benefit of fewer people missing work due to diseases transmitted by \textit{Aedes aegypti}. The agency incentivizes workers through salaries with three components: a flat salary without bonuses, individual compensation, and a bonus when the entire team achieves their collective objectives. These formulations allow us to disentangle which scheme offers the highest yield in terms of disease prevention.

The optimal scheme to improve welfare is a contract where the government agency offers a compensation package, and the two healthcare providers choose their effort accordingly. From the perspective of the worker, the expected utility of effort, provided that the compensation depends on successful provision of the service, and that the benefit from salary is given by a concave function $u(.)$. For concreteness, we use the function $u(x) = \sqrt{x}$. The expected utility of effort is then the compensation for each scenario, times their probability. It is equal to:

\begin{eqnarray*}
    U_i(e_i, h_i; e_j, h_j) & = & P_i(e_i, h_j)P_j(e_j, h_i)u(s+w_{both}) + \\
    & & P_i(e_i, h_j)(1-P_j(e_j, h_i))u(s+w_{one}) + \\
    & & (1-P_i(e_i, h_j))P_j(e_j, h_i)u(s+w_{one}) + \\
    & & (1-P_i(e_i, h_j))(1-P_j(e_j, h_i))u(s) - \dfrac{c}{2}(e_i^2 + h_i^2)
\end{eqnarray*}

And this utility is symmetric for the worker $j$. To simplify things, consider that the compensation under an unsuccessful service provision is equal to zero: $u(s)=0$, or $s=0$. From the perspective of the government agency, the benefit from offering the compensation is equal to the social benefit in each provision scenario minus the compensation times the likelihood of the scenario:

\begin{eqnarray*}
    U_A(w_{both}, w_{one}, s; e_i, h_i, e_j, h_j) & = & P_i(e_i, h_j)P_j(e_j, h_i)(2B - 2w_{both}) + \\
    & & P_i(e_i, h_j)(1-P_j(e_j, h_i))(B-2w_{one}) + \\
    & & (1-P_i(e_i, h_j))P_j(e_j, h_i)(B-2w_{one})
\end{eqnarray*}

The situation is a standard contract theory problem, where we have three compensation packages: no bonus ($w_{both} = w_{one} = 0$), individual bonus ($w_{both} = w_{one} \neq 0$), and collective bonus ($w_{both} \neq w_{one}$, $w_{both} \neq 0$, and $w_{one} \neq 0$). The optimal contract is then the solution for the following constrained optimization problem:

\begin{eqnarray*}
    \max_{w_{both}, w_{one}} U_A(w_{both}, w_{one}; e_i, h_i, e_j, h_j) \text{, subject to:} \\
    & (e_i, h_i) \in \arg \max U_i(e_i, h_i; e_j, h_j, w_{both}, w_{one}) \\
    & (e_j, h_j) \in \arg \max U_j(e_j, h_j; e_i, h_i, w_{both}, w_{one})
\end{eqnarray*}

And by choosing an optimal compensation scheme, the agency can induce more effort and more cooperation among workers.

## Baseline: no incentive bonuses

When the agency only pays a flat salary without performance incentives, the agency sets the performance compensation equals to zero: $w_{both} = w_{one} = 0$. This changes the expected utility of the agent to the following:

\begin{eqnarray*}
U_i(e_i, h_i; e_j, h_j) & = & - \dfrac{c}{2}(e_i^2 + h_i^2)
\end{eqnarray*}

In this setting, exerting effort generates only costs and no benefits. The agents exert zero effort and help in equilibrium: $e_i^* = e_j^* = 0$ and $h_i^* = h_j^* = 0$. The agency pays the minimum wage accepted by law, and in this model, we assume that this wage is equal to zero. Accordingly, the agency's expected benefit is equal to:

\[
R_A(\text{no bonus}) \ = \ 0
\]

The prediction here is that workers will exert no effort, and the agency will have only costs without accruing any benefit. This is the worst-case scenario in terms of the agency's welfare. In the experiment, it matches the control condition.\footnote{Throughout the chapter, we assume that the optimal output for the agency is equal to the maximum welfare for society. Although this is not always the case, it is a reasonable simplification for the purposes of this chapter. Adding a difference here would only complicate my results and provide no further insight into designing an incentive scheme to maximize welfare.}

## Performance bonus for individuals

When the benefits are tied to individual performance, the government agency compensates the workers for their effort, without tying their bonuses to helping other workers. This means that $h_i^* = h_j^* = 0$, but the optimal level of effort is always positive. Let $\alpha$ the bonus the government agency offers to workers conditional on lowering the incidence of the disease. Each worker then evaluates the utility of the bonus as $u_i(\alpha) = \sqrt{\alpha}$, as the utility of the agent is concave, representing the risk aversion of the agent. The optimization problem, from the perspective of the agent, is to maximize her expected utility, given the bonus offered by the government agency upon achieving a successful provision:

\begin{eqnarray*}
\max_{e_i} U_i(e_i) & = & \max_{e_i} \left[P_i(e_i, 0)\sqrt{\alpha} - \dfrac{c}{2}(e_i^2)\right] \\
 & = & \max_{e_i} \left[e_i\sqrt{\alpha} - \dfrac{c}{2}(e_i^2)\right]
\end{eqnarray*}

Both workers face the same incentive structure, so the equilibrium is symmetric, with $e_i = e_j$. Taking the derivative and equating it to zero, gives us the following optimal effort level: $e_i^* = e_j^* = \dfrac{\sqrt{\alpha}}{c}$. The optimal level of effort represents the point where the marginal benefit from the government agency's compensation is equal to the marginal cost of effort. The benefit of a successful provision of the healthcare service is equal to -- for both players -- the total benefit times the chance of a successful provision times the difference between the benefit accrued from a successful provision minus the bonus paid for the worker. To compute the optimal contract the government agency has to offer in this setting, we must choose $\alpha$ to maximize the agency's expected utility:

\begin{eqnarray*}
\max_{\alpha} R_A(e_i^*(\alpha), e_j^*(\alpha)) & = & \max_{\alpha} \left[2 \dfrac{\sqrt{\alpha}}{c} (B-\alpha)\right]
\end{eqnarray*}

The optimal bonus is equal to $\alpha^* = \dfrac{B}{3}$. Plugging the optimal bonus and the optimal effort levels into the welfare function, we find the agency's expected revenue, which in this case is equal to:

\[
R_A(\text{individual bonus}) \ = \ \dfrac{4}{c} \left[ \dfrac{B}{3} \right]^{\dfrac{3}{2}}
\]

The revenue is always greater than zero, provided that the costs of investing effort and the social benefits of the policy are greater than zero.

## Performance bonus for teams

When the government agency sets rewards for both individual and team performance, healthcare workers divide their time between expending effort in their job ($e_i$) and helping their teams to get their jobs done ($h_i$). Helping may take many forms: from simple peer pressure and monitoring to ensure the peer is doing the job well, to efficiently dividing tasks and exploiting complementarities in their duties. From the government agency's perspective, incentivizing workers to help each other can potentiate the chances of obtaining successful service provision. From the standpoint of healthcare workers, optimal effort becomes a mix of her own efforts and the helping efforts that maximize her expected utility, provided that both efforts are incentive-compatible. Incentive compatible means, in the case of healthcare workers, that both efforts are exerted to match the governmental agency's contractual incentives. The expected utility for the agent $i$ consists of the chance of getting a bonus times the utility of the bonus. This is iterated in each of the possible service provision scenarios.

\begin{eqnarray*}
\max_{(e_i,h_i)} U_i(e_i, h_i; e_j, h_j) & = & \max_{(e_i,h_i)} \{e_j(1+h_i)e_i(1+h_j)u(w_{ij}) + \\
& & e_j(1+h_i)(1-e_i(1+h_j))u(w_{j}) + \\
& & e_i(1+h_j)(1-e_j(1+h_i))u(w_{i}) - c\dfrac{e_i^2+h_i^2}{2}\}
\end{eqnarray*}

Again, both players are ex-ante similar in terms of their expected utilities. This allow us to solve for the Symmetric Nash Equilibrium, where:

1. The effort of a given healthcare provider ($i$) is equal to the effort of the other healthcare provider ($j$): $e_i = e_j = e$.
2. The help of one healthcare provider is equal to the help of the other healthcare provider $h_i = h_j = h$.
3. Both agents have the same utility function, $U_i(.) = U_j(.)$.

Maximizing the expected utility leads us to the optimal effort and amount of help for the healthcare provider, given the contractual scheme. The optimal provision must satisfy the following equation:

\begin{eqnarray*}
\dfrac{\partial U}{\partial e} & = & e(1+h)^2(u(w_{ij})-u(w_{i})-u(w_{j})) + (1+h)u(w_{i})-ce \\
\dfrac{\partial U}{\partial h} & = &
e^2(1+h)(u(w_{ij})-u(w_{i})-u(w_{j})) + eu(w_{j})-ch
\end{eqnarray*}

To simplify our computation, we consider contracts that vary in one dimension $\alpha$. The individual part of the contractual benefit is equal to multiples of this contract for each situation: own successful provision and the successful colleague provision.

In this example, we restrict our attention to contracts where $u(w_{i}) = u(w_{j}) = \sqrt{\alpha}$ and $u(w_{ij}) = 2u(w_{i})$. These contracts are a better match for the conditions we set in the experiment: they represent the collective gain when recompensing the agent for peer and individual successes. The optimal effort and help become:

\[
e_{i}^{*} = e_{j}^{*} = \dfrac{\sqrt{\alpha c}}{c - \alpha}
\]

and

\[
h_{i}^{*} = h_{j}^{*} = \dfrac{\alpha}{c-\alpha}
\]

The governmental agency now maximizes the bonus for the individual provision ($\alpha$), given that the collective provision is higher than it is. The expected revenue of the agency is equal to the chance of lowering the disease burden times the benefit minus the costs of paying the healthcare provider's salaries:

\begin{eqnarray*}
\max_{\alpha} R_A(e_{i}^{*}(\alpha), h_{i}^{*}(\alpha), e_{j}^{*}(\alpha), h_{i}^{*}(\alpha)) & = & \max_{\alpha} \left[2 \dfrac{c\sqrt{c\alpha}}{(c-\alpha)^2} (B-2\alpha)\right]
\end{eqnarray*}

The derivative of this equation is the polynomial in the second degree in $\alpha$. By the intermediate value theorem, it is easy to see that it has one solution for $\alpha \in [0, B]$. To illustrate, consider Figure \ref{figrevmax}, where we plot the expected revenue for the agency ($R_A(\alpha)$), as a function of the offered compensation $\alpha$, and the three types of contracts: no productivity incentives, individual productivity incentives, and team productivity incentives, fixing $B = c = 1$.

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{../figures/figrev.pdf}
\caption{Governmental Agency's Revenue in terms of Contract and Compensation}
\label{figrevmax}
\end{figure}

Therefore, the maximum benefit that the agency can achieve is higher when the agency compensates the workers for their cooperation. When the agency incentivizes team effort, workers can do better, on margin, by sharing the benefit of successful provision.\footnote{The limits for this reasoning appear when there are gains of specialization. For instance, if the costs for effort and help were such that $\dfrac{c(e+h)^2}{2}$, then diverting energy for help is costly, on margin, at the same rate as the given effort provision. In this case, the compensation to stimulate cooperation has to be significantly higher, and even in this case there will be incentives for not cooperating.}

# Data Analysis

## Covariate Balance

We checked the balance in the participation using four statistics. First, we study the decision to participate in the training day. Second, we studied the decision to participate in the experiment. It requires the person to show up for training, and then participate during the field. Third, we checked the balance in the individual characteristics collected by the pre-treatment survey. Finally, we checked the territorial assignment to make sure that the pre-treatment characteristics is balanced in the places that were undergoing visit. We run regressions for all the aspects above. We had balance for the individual assignment (models one to three), and for the territorial assignment, we had imbalance that was corrected using propensity-score matching.

### Training Participation

```{r, echo = FALSE}
#####
## Balance
#####

## Training Participation Balance
tabcov <- data.frame()

# Altruism
x = tapply(pretreat$Age, 
           pretreat$training,
           mean)
y = summary(aov(Age~training, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Age
x = tapply(pretreat$Female, 
           pretreat$training,
           mean)
y = summary(aov(Female~training, data = pretreat))
tab <- data.frame(Var = 'Female',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Religiosity
x = tapply(pretreat$HasVehicle, 
           pretreat$training,
           mean)
y = summary(aov(HasVehicle~training, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# N
x = round(tapply(rep(1, length(pretreat$training)), 
                 pretreat$training,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `NotTraining` = round(x[1],2),
                  `Training` = round(x[2],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Training}
  \label{appctabcovbalindv}
\begin{tabular}{@{\extracolsep{5pt}} lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Not Training & Training & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

### Participation in the Field

```{r, echo = FALSE}
#####
## Balance
#####

## Participation Balance
tabcov <- data.frame()

# Altruism
x = tapply(pretreat$Age, 
           pretreat$participating,
           mean)
y = summary(aov(Age~participating, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Age
x = tapply(pretreat$Female, 
           pretreat$participating,
           mean)
y = summary(aov(Female~participating, data = pretreat))
tab <- data.frame(Var = 'Female',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Religiosity
x = tapply(pretreat$HasVehicle, 
           pretreat$participating,
           mean)
y = summary(aov(HasVehicle~participating, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# N
x = round(tapply(rep(1, length(pretreat$participating)), 
                 pretreat$participating,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  `NotParticipating` = round(x[1],2),
                  `Participating` = round(x[2],2),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Participation}
  \label{appctabcovbalindv}
\begin{tabular}{@{\extracolsep{5pt}} lcccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Not Participating & Participating & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

### Individual Assignment

```{r, echo = FALSE}
#####
## Balance
#####

## Pairs characteristics
tabcov <- data.frame()

# Age
x = tapply(pretreat$Age, 
           pretreat$assignment,
           mean)
y = summary(aov(Age~assignment, 
                data = pretreat))
tab <- data.frame(Var = 'Age',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Female
x = tapply(pretreat$Female, 
           pretreat$assignment,
           mean)
y = summary(aov(Female~assignment, data = pretreat))
tab <- data.frame(Var = 'Female',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Has Vehicle
x = tapply(pretreat$HasVehicle, 
           pretreat$assignment,
           mean)
y = summary(aov(HasVehicle~assignment, data = pretreat))
tab <- data.frame(Var = 'Has Vehicle?',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Altruism
x = tapply(pretreat$aboveMedianAltr, 
           pretreat$assignment,
           mean)
y = summary(aov(aboveMedianAltr~assignment, data = pretreat))
tab <- data.frame(Var = 'Altruist',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Religiosity
x = tapply(pretreat$relig, 
           pretreat$assignment,
           mean)
y = summary(aov(relig~assignment, data = pretreat))
tab <- data.frame(Var = 'Religiosity',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Political Engagement
x = tapply(pretreat$polengage, 
           pretreat$assignment,
           mean)
y = summary(aov(polengage~assignment, data = pretreat))
tab <- data.frame(Var = 'Pol. Engagement',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Social Engagement
x = tapply(pretreat$socengage, 
           pretreat$assignment,
           mean)
y = summary(aov(socengage~assignment, data = pretreat))
tab <- data.frame(Var = 'Soc. Engagement',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Above Two Minimum Wage Family
x = tapply(pretreat$aboveTwoMinWageFam, 
           pretreat$assignment,
           mean)
y = summary(aov(aboveTwoMinWageFam~assignment, data = pretreat))
tab <- data.frame(Var = 'Above Two Min. Wage',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Above Median Facebook popularity
x = tapply(pretreat$FBpop, 
           pretreat$assignment,
           mean)
y = summary(aov(FBpop~assignment, data = pretreat))
tab <- data.frame(Var = 'Facebook Popularity',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# N
x = round(tapply(rep(1, length(pretreat$assignment)), 
                 pretreat$assignment,
                 sum), digits = 0)
tab <- data.frame(Var = 'N',
                  NoBonus = round(x[1],0),
                  Individual = round(x[2],0),
                  Collective = round(x[3],0),
                  FVal = NA,
                  Pvalue = NA)
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering
  \caption{Covariate Balance on Individual Characteristics}
  \label{appctabcovbalindv}
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex]
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

### Unweigted Territorial Assignment

```{r, echo = FALSE}
## Census Sectors characteristics
tabcov <- data.frame()

# Number of Houses
x = tapply(dfr2$NHouses, 
           dfr2$D1,
           mean)
y = summary(aov(NHouses~D1, data = dfr2))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Age
x = tapply(dfr2$NHouseholds, 
           dfr2$D1,
           mean)
y = summary(aov(NHouseholds~D1, data = dfr2))
tab <- data.frame(Var = 'Number of Households',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# AvgHouseholdSize
x = tapply(dfr2$AvgHouseholdSize, 
           dfr2$D1,
           mean)
y = summary(aov(AvgHouseholdSize~D1, data = dfr2))
tab <- data.frame(Var = 'Avg. Household Size',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Avg. Income Households
x = tapply(dfr2$logAvgIncomeHousehold, 
           dfr2$D1,
           mean)
y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2))
tab <- data.frame(Var = 'Log Avg. Income',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Cases Before
x = tapply(dfr2$plac, 
           dfr2$D1,
           mean)
y = summary(aov(plac~D1, data = dfr2))
tab <- data.frame(Var = 'Cases Before Treatment',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL

## re-weighting
dfr2$weightsD1 = weightit(D1~NHouses+
                    NHouseholds+AvgHouseholdSize+
                    logAvgIncomeHousehold+plac, 
                  data = dfr2, focal = "No bonus", 
                  method = 'cbps',
                  estimand = "ATT")$weights

dfr$weightsD1 <- weightit(D1~NHouses+
                    NHouseholds+AvgHouseholdSize+
                    logAvgIncomeHousehold+plac, 
                  data = dfr, focal = "Control", 
                  method = 'cbps',
                  estimand = "ATT")$weights

dfr$weightsD2 <- weightit(D2~NHouses+
                            NHouseholds+AvgHouseholdSize+
                            logAvgIncomeHousehold+plac, 
                          data = dfr, focal = "No intervention", 
                          method = 'cbps',
                          estimand = "ATT")$weights
```

\begin{table}[!htbp] \centering 
  \caption{Covariate Balance Un-Weighted Territorial Assignment} 
  \label{appcunweightbalter} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc}
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & Control & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

### Propensity-score Weighted Territorial Assignment

```{r, echo=FALSE}
tabcov <- data.frame()
# Number of Houses
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouses, weightsD1))
x = x$x
x
y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Houses',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Number of households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(NHouseholds, weightsD1))
x = x$x
y = summary(aov(NHouseholds~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Number of Households',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# AvgHouseholdSize
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1))
x = x$x
y = summary(aov(AvgHouseholdSize~D1, data = dfr2, 
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Avg. Household Size',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Avg. Income Households
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1))
x = x$x
y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2, 
                weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Log Avg. Income',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)

# Cases Before
x = dfr2 %>%
  group_by(D1) %>%
  summarise(x = weighted.mean(plac, weightsD1))
x = x$x
y = summary(aov(plac~D1, data = dfr2, weights=dfr2$weightsD1))
tab <- data.frame(Var = 'Cases Before Treatment',
                  NoBonus = round(x[1],2),
                  Individual = round(x[2],2),
                  Collective = round(x[3],2),
                  FVal = round(y[[1]][1,4], 3),
                  Pvalue = round(y[[1]][1,5], 3))
tabcov <- rbind(tabcov, tab)
row.names(tabcov) <- NULL
```

\begin{table}[!htbp] \centering 
  \caption{Covariate Balance Weighted Territorial Assignment} 
  \label{appcweightbalter} 
\begin{tabular}{@{\extracolsep{5pt}} lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & No Bonus & Individual & Collective & F-Statistic & P-Value \\
\hline \\[-1.8ex] 
```{r, echo=FALSE, results='asis'}
for (i in 1:dim(tabcov)[1]) {
  cat(paste(paste(tabcov[i,], collapse = ' & '), 
        ' \\\\ ', sep = ''), '\n')
}
```
\hline\hline \\[-1.8ex] 
\end{tabular}
\end{table}

## Productivity Outcomes

```{r, echo = FALSE, results='asis'}
## Productivity outcome
mprod <- list()
mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
stargazer(mprod[[1]], mprod[[2]],
          mprod[[3]], mprod[[4]],
          se = starprep(mprod[[1]], mprod[[2]],
                        mprod[[3]], mprod[[4]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}', 
                             '\\shortstack{Houses Vis. in \\\\ Less than Two Min.}',
                             '\\shortstack{Breeding Sites \\\\ Terminated}',
                             '\\shortstack{Larvae \\\\ Terminated}'),
          keep.stat = c('ser', 'n'),
          keep = c('DIndividual', 'DCollective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          title = 'Field Productivity', header = FALSE)
```

## Disease Incidence Outcomes

For the disease incidence regressions, the results in Table \ref{'diseasein} show all null effect.

```{r, echo=FALSE, results='asis'}
## Health outcome
moutc <- list()
moutc[[1]] <- lm(nc15dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[2]] <- lm(nc30dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[3]] <- lm(nc60dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[4]] <- lm(nc90dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[5]] <- lm(nc30to60dafter ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)
moutc[[6]] <- lm(plac ~ D1,
                 data = dfr2, weights = dfr2$weightsD1)

stargazer(moutc[[6]], moutc[[1]], moutc[[2]], 
          moutc[[3]], moutc[[4]], moutc[[5]],
          se = starprep(moutc[[6]], moutc[[1]], 
                        moutc[[2]], moutc[[3]], 
                        moutc[[4]], moutc[[5]],
                        se_type = "HC1"),
          dep.var.labels = c('\\shortstack{Before \\\\ Int.}',
                             '\\shortstack{Fifteen D. \\\\ After Int.}',
                             '\\shortstack{Thirty D. \\\\ After Int.}',
                             '\\shortstack{Sixty D. \\\\ After Int.}', 
                             '\\shortstack{Ninety D. \\\\ After Int.}',
                             '\\shortstack{Btw. Thirty \\\\ \\& Sixty D. \\\\ After Int.}'), label = 'diseasein',
          keep.stat = c('ser', 'n'),
          keep = c('D1Individual', 'D1Collective'),
          covariate.labels = c('Individual Bonus',
                               'Collective Bonus'),
          dep.var.caption = "Number of Reported Hospital Cases:",
          title = 'Disease Incidence', header = FALSE,
          font.size = 'small')
```

## Differences-in-differences for the Healthcare Outcomes

For the differences-in-differences models, the results are in Table \ref{difindif}.

```{r, echo = FALSE, results='asis'}
mod <- list()
mod[[1]] <- felm(ncas4weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
mod[[2]] <- felm(ncas8weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
mod[[3]] <- felm(ncas12weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
mod[[4]] <- felm(ncas ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
stargazer(mod[[1]], mod[[2]], mod[[3]], mod[[4]],
          dep.var.labels = c('\\shortstack{Four \\\\ Weeks Window}',
                             '\\shortstack{Eight \\\\ Weeks Window}',
                             '\\shortstack{Twelve \\\\ Weeks Window}',
                             '\\shortstack{Sixteen \\\\ Weeks Window}'),
          keep.stat = c('ser', 'n'),
          keep = c('DID'),
          label = 'difindif',
          covariate.labels = c('Dif-in-Dif'),
          dep.var.caption = "Disease Incidence Before and After Intervention:",
          title = 'Differences-in-Differences Model', header = FALSE)
```

Table \ref{difindif} shows the following:

1. There is a 10.3\% effect on the full data model.
2. The other windows are not significant but the sign is consistent with lower disease incidence.
3. Comparing individual and collective, collective decreases by 2.9\%, but the result is not significant.

# Experiment Report

Here we use the American Political Science Association experimental session standard report to present all the details involved in the experiment.

## Hypothesis

### Question addressed by the experiment

In this experiment, we study the impact of monetary incentives on the performance of health care workers in Brazil. The study aims to find which financial incentive scheme is better to improve the performance of the workers in the field.

Most of the developmental economics papers on incentives for public service providers highlight that better compensation works. However, these papers focus on services that are individually provided, such as a teacher in a classroom. In health care, rarely the efforts are undertaken independently, and this poses the question: what is the best way to improve public health care provision, when teams, rather than individuals, provide the service?

In this paper, we undertake the first effort to bridge this gap by testing whether team incentives are more effective than individual incentives to improve preventive healthcare provision in Brazil.

The Brazilian case is well suited for this test for two main reasons. First, disease borne by the Aedes aegypti is one of the leading causes of congenital disabilities, hospitalization, and casualties in the global south. Second, a pair of health care workers are responsible for visiting households and exterminate the disease in Brazil. Therefore, we could test individual versus team bonuses in a setting that is relevant to welfare.

### Hypothesis tested

We tested which types of bonuses are better for improving the performance of health care workers in Brazil. We tested three incentive schemes: first, monetary compensation with no performance bonuses; second, individual compensation for performance above the median in the headquarter they were assigned; and third, peer bonus compensation for team performance above the median in the headquarters. Theoretically, team bonuses should be more effective, as it increases peer monitoring, diminishing the free-riding problem. However, if there are fewer complementarities, individual rewards can be more productive. This poses the question: which incentive scheme is better for community-based prevention of Aedes aegypti borne diseases in Brazil?

## Subjects and Context

### Why was this subject pool selected?

The subjects participating in the experiment were selected based on a Facebook recruitment Ad posted in the Municipality of Rio Verde, Goias State, Brazil. We chose this town because we had an agreement with the mayor's office, and also because it had a considerable spike in dengue fever cases in 2018. One of the Facebook ads follows below.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../figures/rvRecruit1.png}
\caption{Facebook Recruitment Ad with Pilot Participants' picture.\label{appcfbad}}
\end{figure}

The Facebook Ad redirected the participant to a Google Forms where s/he filled up a participation eligibility form. The Google form used is below.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvRecruit2.png}
\caption{Google Form Recruitment.\label{appcgform}}
\end{figure}

After that, we send them an email, asking questions on demographics and other characteristics.

### Who was eligible to participate in the study?

Adults, 18 old or older.

### What would result in the exclusion of a participant?

Being underage or not show up for the training and the intervention.

### Were any aspects of recruitment changed after the recruitment began?

No.

### Procedures used to recruit and select participants

We posted a Facebook ad in the municipality participating in the intervention. The ad invited potential participants to join the research and explained the compensation. If they clicked the ad, they were directed to Google Forms, where they added their e-mails and personal information.

### Recruitment dates

The online recruitment took place right after filling up the form. We send potential participants information regarding Aedes aegypti prevention and a link for a pre-treatment survey. After filled, participants were informed about the live training dates and selected preferred times to participate. They then had to show up for the two-hour training session.

The training date for the pilot was April 13, 2018. The training date for the intervention was May 4, 2018. A picture of the May 4 training day follows below.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../figures/rvTraining.png}
\caption{Training Day.\label{appctrday}}
\end{figure}

### Settings and locations where the data were collected

There are two primary datasets used in the paper. First, we collected productivity data from the cell phones used by the participants in the field. Second, we collected governmental data on diseases transmitted by the Aedes aegypti from the Brazilian Ministry of Health diseases notification system (SINAN).

The first dataset is generated by the participants pictures in the field. The second dataset is comprised of governmental records of people that checked into hospitals and were confirmed having dengue fever. This data has the address of the person, that we then used to geolocate the case. Among the diseases transmitted by the Aedes aegypti, dengue fever is the most frequent and easy to detect.

### Relevant specifics about the population

All the participants were from the municipality of Rio Verde, in the state of Goiás, in Brazil. A map of the municipality follows below:

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../figures/rvMap.png}
\caption{Rio Verde, GO, Brazil Map.\label{appcmaprv}}
\end{figure}

## Allocation Methods

### Randomization procedure

We generated the random assignment using block randomization applied on seven variables:

1. Age
2. Above median altruism
3. Above median religiosity score
4. Above median Political Engagement
5. Above median social engagement
6. Above two minimum wage family income
7. Above median Facebook popularity (number of friends)

These variables were computed from surveys that we collected prior to the intervention. To test the balance, we use F-tests on the block randomization data. The balance tests follow in the data analysis section.

## Random assignment

### Units of randomization

We randomized the treatment at the level of the participant.

### Cluster random assignment

No cluster random assignment was used. However, in the differences-in-differences estimation, we use the census sector where the pair worked to cluster the standard errors.

## Blinding

### Were participants unaware of the treatment assignment?

Yes. They knew their incentive schemes, but not other incentive schemes. To ensure that there would be no spillovers, we divided each treatment assigned teams into three different headquarters:

1. Assembleia de Deus Church (No bonus)
2. Videiras Church (Individual reward)
3. Sara Nossa Terra Church (Collective bonus)

These headquarters were away from each other to avoid contact between participants.

### Were those administering the intervention unaware of the random assignment?

No. The head research assistants in each group knew that different treatment would be administered in other research headquarters. This measure was taken in case the treatment spillover, and we needed to remove pairs that were disturbing the work from the field.

### Checked whether blind was successful?

The single-blind was successful. We received no complaints during the intervention day. After the intervention day, participants became aware of the experiment. The post-treatment spillover made the post-treatment survey ineffective because they refused to cooperate with the researchers.

## Treatments

### Treatment groups

We have three treatment groups:

1. Control (no performance bonus)
2. Individual treatment
3. Collective treatment

In the control group, a bonus was assigned without performance concerns.

In the individual treatment group, we explained the participants that we would rank the performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated. Participants would have their performance ranked and the ones above the median would double their monetary reward (from BRL 110.00 to BRL 220.00).

In the collective treatment group, we explained the participants that we would rank their team performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated. We would sum their individual performance with the performance of their field peers, and then rank the teams. Teams with performance above the median would double their monetary reward (from BRL 110.00 to BRL 220.00, for each person in the team).

The fieldwork was performed in pairs, to mimic the Aedes Aegypti actual practices in Brazil.

### Control groups

The control group received a monetary reward with no performance requirement.

### Experimental instructions

In the study day, around 5AM, we randomly assigned pairs, and send emails to the individuals directing them to each of the headquarters, based on their treatment status.

We had three study headquarters: the control headquarters (Assembleia de Deus church); the individual treatment headquarters (Videiras church); and the peer treatment headquarters (Sara Nossa Terra church). We printed set of leaflets with places that they had to administer the treatment. One example of a leaflet follows below:

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvWorkBlock.png}
\caption{Example Working Area\label{appcevwbl}}
\end{figure}

And the working areas follow below:

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
\caption{Example Working Area\label{appcevwbl}}
\end{figure}

We handed in the cellphones and the working kits for them. An example of the working kits design follows below:

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvKit3.jpeg}
\caption{Teams Uniforms.\label{appcteamunif}}
\end{figure}

The cellphone was a Samsung, model Galaxy A1. A picture with a testing of the data collection app follows below.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{../figures/rvApp.jpeg}
\caption{Cellphone with data collection app in test.\label{appccpdcit}}
\end{figure}

The informative leaflet distributed to households follow here:

\begin{figure}
\includegraphics[width=0.8\textwidth]{../figures/rvKit4.jpg}
\includegraphics[width=0.8\textwidth]{../figures/rvKit5.jpg}
\caption{Example leaflet handed to households.\label{appcexhhleafl}}
\end{figure}

Then, at around 11:00am we administered the main treatments. They consisted in tell the following instructions to the participants, when we handed the leaflet with their working places:

- **Control:** we told them that there would be an increase in their payment without explaining the reason. We told them about how performance would be measured, without saying anything about compensation based on performance.
- **Individual treatment:** we told the participants that we would measure their performances in the field, and that we would rank all the performances. The individuals with performance above the median would receive the bonus. We also explained in lay terms what was a median, and how we would measure performance.
- **Peer treatment:** we told the participants that we would measure their performances in the field, and that we would rank all the performances. The pairs with performance above the median would receive the bonus. We also explained in lay terms what was a median, and how we would measure performance.

## How and when manipulations were administered

### Method of delivery

The manipulations were delivered in person, by the chief headquarter RA, first to all the pairs in a speech, then to each pair in person. For each pair, we reinforced the instructions while handing in the leaflets.

### Software used to administer the treatment

The randomization was performed in R. The treatment administration was done in person.

## Results

### Outcome measures

There are two groups of outcomes. First, the performance outcomes that are collected from the cellphone used by each participant in the field. Second, the governmental data reported by the health care facilities in the municipality, with all dengue cases.

For the performance data we have:

1. Geolocated pictures of house fronts as a proof that they visited to house.
2. Pictures of exterminated breeding sites.
3. Video of exterminated a. aegypti larvae.

For governmental data, we have all the people infected by dengue fever that went to the hospital. There were no reported cases of Zika and Chikungunya, as the detection of these diseases are less standardized that Dengue. Moreover, the mayors office have no recollection of microcephaly incidence in the area during the period.

The data then corresponds to all dengue cases, with address of the infected person, date of check-in to the hospital, and the severity of the case.

### Covariates

We collected information on demographics.

### Which outcomes and subgroup analysis were specified prior to the experiment?

As the mayors office did not handed in the infections data prior to the intervention, we asked the neighborhoods that had higher dengue fever incidence prior to the intervention, and placed the territorial assignment in these places. However, due to absence of micro-level infectious disease data, we could not consider them prior to the intervention.

### Exploratory analysis

We run a pilot with 20 pairs before main intervention. We did not administered the incentivized intervention in the pilot to avoid contamination in the main results. The pilot helped us to update the expectations regarding the productivity in the field. Previously, we projected that we should assign around 20 houses per pairs. However, in the pilot we learned that pairs could visit from 40 to 60 houses per pair. In around one-thirty of them nobody answered the door, and in most of them the yards were too small to find any breeding sites. Moreover, most of the places with dengue in the previous week were visited by the municipal health care workers.

## CONSORT

### Number of subjects initially accessed for eligibility

`r dim(pretreat)[1]` individuals filled in the Google Form. `sum(pretreat$training=='Training')` showed for the training session one day before the intervention. `r sum(pretreat$participating == 'Participating')` individuals showed to the intervention and remained until the end of it.

### Exclusions prior to random assignment

From all eligible people, we excluded the ones that missed the training and the field implementation session. This accounts for `r round(as.numeric(prop.table(table(pretreat$participating))[1]*100), 2)``\% of the total.

### Subjects initially assigned to each experimental group

1. `r as.numeric(table(pretreat$assignment)[3])` to control group.
2. `r as.numeric(table(pretreat$assignment)[2])` to individual treatment group.
3. `r as.numeric(table(pretreat$assignment)[1])` to peer treatment group.

### Proportion received x not received intervention

1. `r as.numeric(table(pretreat$assignment[pretreat$participating == 'Participating'])[3])` received the control intervention out of `r as.numeric(table(pretreat$assignment)[3])` in the control group.
2. `r as.numeric(table(pretreat$assignment[pretreat$participating == 'Participating'])[2])` received the intervention out of `r as.numeric(table(pretreat$assignment)[2])` in the individual treatment group.
3. `r as.numeric(table(pretreat$assignment[pretreat$participating == 'Participating'])[1])` received the intervention out of `r as.numeric(table(pretreat$assignment)[1])` in the peer treatment group.

### Why did not receive intervention?

The individuals did not received the intervention if they missed the field. They were then excluded from the data.

### Number subjects each group dropped experiment

No subject were dropped from the assignment. The attrition was caused by the fact that there were individuals that did not show up for the training and the treatment.

## Statistical analysis

### Describe statistical analysis

We run four types of statistical analysis:

1. Balance tests
2. Performance outcome analysis
3. Disease incidence analysis
4. Differences-in-differences analysis

The main equations for the performance outcomes are:

\[
Y_i = \alpha + \beta D_i + \varepsilon_i
\]

Where $\beta$ is the outcome of interest, $Y_i$ is the outcome for case $i$, and $D_i$ is the treatment status for case $i$. And the code is:

\begin{verbatim}
mod <- lm(outc ~ treat, data = dataframe)
\end{verbatim}

The main equations for the disease incidence are:

\[
Y_i = \alpha + \beta D_i + \varepsilon_i
\]

Where $\beta$ is the outcome of interest, $Y_i$ is the outcome for case $i$, and $D_i$ is the treatment status for case $i$. The only difference is that the estimates are weighted using the propensity score matching. And the code is:

\begin{verbatim}
mod <- lm(outc ~ treat, 
          data = dataframe, 
          weights = dataframe$weights)
\end{verbatim}

Finally, the differences-in-differences estimator has the following form:

\[
Y_i = \alpha + \gamma Time_i + \theta Treat_i + \beta Time_i \times Treat_i + \varepsilon_i
\]

And our quantity of interest is $\beta$. The codes for the regression models we run are as follows:

\begin{verbatim}
mod <- felm(outc ~ time+treat+DID|0|0|CensusSectors, 
            data = dataframe)
\end{verbatim}

These regressions uses the package \texttt{lfe}, as it facilitates the use of cluster-robust standard errors.

## Standard errors

The robust standard errors are computed using \texttt{vcovHC} function in the package \texttt{sandwich}. The standard error is the same as the Stata's \textit{comma-robust}.

## Attrition

The attrition reports have been analyzed in the data analysis section of this appendix.

## Other information

### IRB

We received IRB from the New York University and Fundação Getulio Vargas.

- NYU IRB number: IRB-FY2017-17
- FGV IRB number: IRB-01/2017

### Pre-registration

The study was pre-registered using the EGAP pre-registry tool, by the number 20180504AA.

### Funding

The study was funded by the FGV applied research grant office (RPCAP-FGV). They did not interfere in the study design nor the results.

### Replication dataset

The replication materials is in the following website: (https://github.com/danilofreire/incentives-health-care).

### Thanks

This research benefited from the contribution of the following research assistants:

- Guilherme Fasolin
- Giovanna França
- Phillipe Guedon
- Natalia Liberato
- Fatima Portella
- Catarina Roman
- Leticia Santana
- Larissa Santos
- Vitor Sion

We are very thankful for all their help before, during, and after the field.

## Some field pictures

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{../figures/rvPilot.jpg}
\caption{Field pictures}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{../figures/rvFieldPic1.png}
\caption{Field pictures}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{../figures/rvFieldPic2.jpg}
\caption{Field pictures}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/diseaseincidence60dw.pdf}
\caption{Disease incidence before and after.\label{appcdisincbaf}}
\end{figure}

# R Session Information

```{r}
sessionInfo()
```

### 2021-02-22 appendix/appendix.Rmd
appendix changes

@@
 
+\pagebreak
+
 # A Theory of Service Provision under Moral Hazard in Teams
 
-Consider a strategic interaction between two healthcare workers and a government agency.\footnote{This model was inspired in @bolton2005contract.
-It is a particular version of their model, aimed at illustrate the effects of our treatment.} The agency hires healthcare workers to provide preventive healthcare.
+Consider a strategic interaction between two healthcare workers and a government agency.\footnote{This model was inspired in the @bolton2005contract and the @itoh1991incentives.
+It is a particular case of their model, aimed at illustrate the effects of our treatment.} The agency hires healthcare workers to provide preventive healthcare.
 And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.
@@
 In this case, the compensation to stimulate cooperation has to be significantly higher, and even in this case there will be incentives for not cooperating.}
+
+\pagebreak
 
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, cache=TRUE}
 #####
@@
 tabcov <- data.frame()
-
-# Altruism
 x = tapply(pretreat$Age, 
@@
 tabcov <- rbind(tabcov, tab)
-
-# Age
 x = tapply(pretreat$Female, 
@@
 tabcov <- rbind(tabcov, tab)
-
-# Religiosity
 x = tapply(pretreat$HasVehicle, 
@@
 tabcov <- rbind(tabcov, tab)
-
-# N
 x = round(tapply(rep(1, length(pretreat$training)), 
@@
   \caption{Covariate Balance on Training}
-  \label{appctabcovbalindv}
+  \label{baltraining}
 \begin{tabular}{@{\extracolsep{5pt}} lcccc}
@@
 tabcov <- rbind(tabcov, tab)
-
-# N
 x = round(tapply(rep(1, length(pretreat$participating)), 
@@
   \caption{Covariate Balance on Participation}
-  \label{appctabcovbalindv}
+  \label{balpart}
 \begin{tabular}{@{\extracolsep{5pt}} lcccc}
@@
 
+\pagebreak
+
 ### Individual Assignment
@@
   \caption{Covariate Balance on Individual Characteristics}
-  \label{appctabcovbalindv}
+  \label{balindvchar}
 \begin{tabular}{@{\extracolsep{5pt}} lccccc}
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, cache=TRUE}
 ## Census Sectors characteristics
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, warning=FALSE, results='hide'}
 tabcov <- data.frame()
@@
   group_by(D1) %>%
-  summarise(x = weighted.mean(NHouses, weightsD1))
+  summarise(x = weighted.mean(NHouses, weightsD1),
+            .groups = 'drop')
 x = x$x
@@
   group_by(D1) %>%
-  summarise(x = weighted.mean(NHouseholds, weightsD1))
+  summarise(x = weighted.mean(NHouseholds, weightsD1),
+            .groups = 'drop')
 x = x$x
@@
   group_by(D1) %>%
-  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1))
+  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1),
+            .groups = 'drop')
 x = x$x
@@
   group_by(D1) %>%
-  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1))
+  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1),
+            .groups = 'drop')
 x = x$x
@@
   group_by(D1) %>%
-  summarise(x = weighted.mean(plac, weightsD1))
+  summarise(x = weighted.mean(plac, weightsD1),
+            .groups = 'drop')
 x = x$x
@@
 \end{table}
+
+\pagebreak
 
@@
                                'Collective Bonus'),
-          title = 'Field Productivity', header = FALSE)
+          title = 'Field Productivity', header = FALSE,
+          font.size = 'small')
 ```
@@
 2. The other windows are not significant but the sign is consistent with lower disease incidence.
-3. Comparing individual and collective, collective decreases by 2.9\%, but the result is not significant.
+
+\pagebreak
 
@@
 
+### Parcial Implementation and Possible Threats to the Identification
+
+We had one substantial problem during the field, with the partial implementation of the territorial assignment in the control group.
+The coordinator of the control group base changed the territorial assignment because of pressure from the participants that had to work farther from the base.
+The coordinator assigned pair for the surroundings of the base.
+This problem may potentially threat the territorial comparability of the cases, but to ensure that this is not confounding our results, we used propensity-score matching to re-weight these areas.
+After the matching, the sectors seems comparable, and we are confident that the re-weight allows a comparable territorial assignment.
+
 ## Some field pictures

### 2021-02-22 appendix/appendix.Rmd
data sources description

@@
 
+## Data Sources
+
+We have five data sources in this study, all in the file `./data/incentives_healthcare.RData`:
+
+- `pretreat`: Pre-treatment Balance Information.
+- `prodfr`: Field Productivity Data.
+- `dfr`: Disease Incidence in All the Rio Verde Census Sectors.
+- `dfr2`: Disease Incidence in the Rio Verde Census Sectors that undergone the Intervention.
+- `did_full`: Differences-in-differences Estimation using the Intervention against a Pure-Control-Group.
+
+### Pre-treatment Balance Dataset
+
+The pre-treatment balance dataset contains the information of all the individuals that iterated with the experimental team at any point of time.
+To be in this dataset, the person has to have filled the recruitment Google Forms that we circulated on the Social Media in the municipality.
+The dataset contains 13 variables, that were collected before the intervention in the Google Forms, and also in pre-treatment surveys before the Training Session.
+
+1. `Age`: Age of the participant
+2. `Female`: Dummy for Female Participant
+3. `HasVehicle`: Dummy for Having Vehicle (car or motorcycle)
+4. `aboveMedianAltr`: Dummy for Above-median Altruism Scale
+5. `relig`: Dummy for Above-median religiosity
+6. `polengage`: Dummy for Above-median political engagement
+7. `socengage`: Dummy for Above-median social engagement
+8. `collegeplus`: Dummy for College or More of Schooling
+9. `aboveTwoMinWageFam`: Dummy for Above Two Brazilian Minimum Wage (R\$ 900.00 monthly)
+10. `FBpop`: Dummy for Above-median Facebook Popularity
+11. `training`: Dummy for Participation in the Training Session
+12. `participating`: Dummy for Participation in the Field Experiment
+13. `assignment`: Dummy for Treatment Status Assignment.
+
+### Field Productivity Dataset
+
+The field productivity dataset was collected by us based on the productivity in the field. The productivity was measured by three components:
+
+1. Number of Houses Visited
+2. Number of Possible Breeding Sites Cleaned
+3. Number of Larvae Exterminated
+
+All this data was compiled using the pictures taken in the field.
+All participants were instructed to take pictures of cleaned breeding sites, and make a video the larvae that they exterminated.
+When done with the house inspection, they were instructed to take a picture of the front of the house, for us to review their work.
+
+The dataset has the compilation from the metadata of these materials. It has the following variables:
+
+1. `D`: Treatment Assignment.
+2. `pair_n`: Pair Index.
+3. `nHouse`: Number of Houses Visited.
+4. `nBreed`: Number of Breeding Sites Cleaned.
+5. `nLarvae`: Number of Larvae Exterminated.
+6. `nHouseVisit`: Number of Houses that were indeed visited (based on having pictures of breeding sites and larvae videos).
+7. `nHouseLessTwoMin`: Number of Houses visited in less than two minutes (which denotes either that the pair have not gone to the place, or that there were no households at home).
+
+### Disease Incidence Datasets.
+
+To measure whether the intervention had an impact on the municipal healthcare system, we collected  There are two disease incidence datasets that we collected thirteen variables in two distinct datasets.
+All datasets compile the data from the National Health Notification System (SINAN) for the municipality.
+The dataset has all the hospitalized people from four months before and four month after the intervention take place.
+We geolocated the address of the households that were hospitalized with Dengue fever in the municipality, and matched the case to the Census Sector that the person lives in.
+Then, we computed the number of cases before and after windows around the intervention.
+The result is two datasets, `dfr` (with all census sectors) and `dfr2` (with only the census sectors matched in the intervention).
+Both datasets have the following variables:
+
+1. `CensusSectors`: Last Three Digits of Census Sector (2010 Brazilian Census)
+2. `NHouses`: Census Sector Number Houses (2010 Brazilian Census)
+3. `NHouseholds`: Census Sector Average Number of Households in Homes (2010 Brazilian Census)
+4. `AvgHouseholdSize`: Census Sector Average Household Income (2010 Brazilian Census)
+5. `logAvgIncomeHousehold`: Census Sector Log of Average Household Income (2010 Brazilian Census)
+6. `D1`: Treatment Assignment
+7. `D2`: Intervention x No Intervention (No Intervention empty in the `dfr2`)
+8. `nc15dafter`: Number of cases 15 days after the intervention.
+9. `nc30dafter`: Number of cases 30 days after the intervention.
+10. `nc60dafter`: Number of cases 60 days after the intervention.
+11. `nc90dafter`: Number of cases 90 days after the intervention.
+12. `nc30to60dafter`: Number of cases between 30 and sixty days after the intervention.
+13. `plac`: Number of cases before the intervention.
+
+### Differences-in-differences Dataset.
+
+We build the dataset `did_full` to investigate whether there were any impact of the intervention in public health outcomes.
+The disease incidence data analyses the effect of the treatment.
+In the differences in differences, we put all the treatments together, and investigate how they perform against a pure control group, the census sectors that were not visited during the intervention.
+
+The dataset has ten variables:
+
+1. `CensusSectors`: Last Three Digits of Census Sector (2010 Brazilian Census)
+2. `D`: Treatment Status Census Sector (Intervention versus Pure Control)
+3. `weekn`: Week Name
+4. `ncas`: Number of cases in a given Week and Census Sector
+5. `Tm`: Week Number
+6. `Tm2`: Intervention timing indicator
+7. `DID`: Differences-in-differences ($Tm2 \times D$)
+8. `ncas4weekwindow`: Number of cases four weeks window around the intervention.
+9. `ncas8weekwindow`: Number of cases eight weeks window around the intervention.
+10. `ncas12weekwindow`: Number of cases twelve weeks window around the intervention.
+
 ## Covariate Balance

### 2021-02-22 manuscript/article.Rmd
adding tables

@@
 options(repos = r)
-if (!require("kableExtra")) {
-    install.packages("kableExtra")
+# Install required packages
+pkgs <- c('tidyverse', 'magrittr', 'lmtest',
+          'estimatr', 'sandwich', 'stargazer',
+          'gridExtra', 'WeightIt', 'robustHD', 
+          'kableExtra', 'lfe')
+
+installIfNot <- function(x) {
+  if(x %in% rownames(installed.packages()) == FALSE) 
+    install.packages(x, dependencies = T)
 } 
+invisible(lapply(pkgs, installIfNot))
+
+# Load packages
+invisible(lapply(pkgs, require, character.only = T))
+rm(pkgs, installIfNot, r)
+
+# Load data
+load('../data/incentives_healthcare.RData')
 ```
@@
 \hline \\[-1.8ex]
-Age &  26.17 & 25.04 & 26.07 & 26.00 & 0.461 & 0.710 \\ 
-Female &   0.72 &  0.79 &  0.79 &  0.74 & 0.805 & 0.492 \\ 
-Has Vehicle &   0.35 &  0.27 &  0.37 &  0.37 & 0.651 & 0.582 \\ 
-N & 341 & 73 & 71 & 73 &  &  \\ 
+```{r, echo = FALSE, cache=TRUE, results='asis'}
+tabcov <- data.frame()
+pretreat$assign2 <- ifelse(is.na(pretreat$assignment)|
+                             pretreat$participating!='Participating', 
+                           'Attrition', pretreat$assignment)
+pretreat$assign2 <- factor(pretreat$assign2, levels = c('Attrition',
+                                                        'No bonus',
+                                                        'Individual',
+                                                        'Collective'))
+x = tapply(pretreat$Age, 
+           pretreat$assign2,
+           mean)
+y = summary(aov(Age~assign2, 
+                data = pretreat))
+tab <- data.frame(Var = 'Age',
+                  `Atrition` = round(x[1],2),
+                  `NoBonus` = round(x[2],2),
+                  `Individual` = round(x[3],2),
+                  `Collective` = round(x[4],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+x = tapply(pretreat$Female, 
+           pretreat$assign2,
+           mean)
+y = summary(aov(Female~assign2, 
+                data = pretreat))
+tab <- data.frame(Var = 'Female',
+                  `Atrition` = round(x[1],2),
+                  `NoBonus` = round(x[2],2),
+                  `Individual` = round(x[3],2),
+                  `Collective` = round(x[4],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+x = tapply(pretreat$HasVehicle, 
+           pretreat$assign2,
+           mean)
+y = summary(aov(HasVehicle~assign2, data = pretreat))
+tab <- data.frame(Var = 'Has Vehicle',
+                  `Atrition` = round(x[1],2),
+                  `NoBonus` = round(x[2],2),
+                  `Individual` = round(x[3],2),
+                  `Collective` = round(x[4],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+x = round(tapply(rep(1, length(pretreat$assign2)), 
+                 pretreat$assign2,
+                 sum), digits = 0)
+tab <- data.frame(Var = 'N',
+                  `Atrition` = round(x[1],2),
+                  `NoBonus` = round(x[2],2),
+                  `Individual` = round(x[3],2),
+                  `Collective` = round(x[4],2),
+                  FVal = NA,
+                  Pvalue = NA)
+tabcov <- rbind(tabcov, tab)
+row.names(tabcov) <- NULL
+for (i in 1:dim(tabcov)[1]) {
+  s <- paste(tabcov[i,], collapse = ' & ')
+  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
+  cat(paste(s, ' \\\\ ', sep = ''), '\n')
+}
+```
 \hline \\[-1.8ex] 
@@
 \hline \\[-1.8ex]
-Altruist &  0.63 &  0.68 &  0.62 & 0.239 & 0.788 \\ 
-Age & 25.01 & 26.00 & 26.90 & 0.754 & 0.472 \\ 
-Religiosity &  0.53 &  0.38 &  0.45 & 1.487 & 0.228 \\ 
-Pol. Engagement &  0.69 &  0.65 &  0.68 & 0.163 & 0.849 \\ 
-Soc. Engagement &  0.59 &  0.62 &  0.67 & 0.454 & 0.636 \\ 
-Above 2 Min. Wage &  0.34 &  0.35 &  0.29 & 0.336 & 0.715 \\ 
-FB Popularity &  0.53 &  0.56 &  0.58 & 0.175 & 0.840 \\ 
+```{r, echo = FALSE, cache=TRUE, results='asis'}
+tabcov <- data.frame()
+pretreat$assign3 <- ifelse(is.na(pretreat$assignment)|
+                             pretreat$participating!='Participating', 
+                           NA, pretreat$assignment)
+pretreat$assign3 <- factor(pretreat$assign3, levels = c('No bonus',
+                                                        'Individual',
+                                                        'Collective'))
+aux <- filter(pretreat, !is.na(assign3))
+# Age
+x = tapply(aux$Age, 
+           aux$assign3,
+           mean)
+y = summary(aov(Age~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Age',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Altruism
+x = tapply(aux$aboveMedianAltr, 
+           aux$assign3,
+           mean)
+y = summary(aov(aboveMedianAltr~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Altruist',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Religiosity
+x = tapply(aux$relig, 
+           aux$assign3,
+           mean)
+y = summary(aov(relig~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Religiosity',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Political Engagement
+x = tapply(aux$polengage, 
+           aux$assign3,
+           mean)
+y = summary(aov(polengage~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Pol. Engagement',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Social Engagement
+x = tapply(aux$socengage, 
+           aux$assign3,
+           mean)
+y = summary(aov(socengage~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Soc. Engagement',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Above Two Minimum Wage Family
+x = tapply(aux$aboveTwoMinWageFam, 
+           aux$assign3,
+           mean)
+y = summary(aov(aboveTwoMinWageFam~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Above Two Min. Wage',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Above Median Facebook popularity
+x = tapply(aux$FBpop, 
+           aux$assign3,
+           mean)
+y = summary(aov(FBpop~assign3, 
+                data = aux))
+tab <- data.frame(Var = 'Facebook Popularity',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# N
+x = round(tapply(rep(1, length(aux$assign3)), 
+                 aux$assign3,
+                 sum), digits = 0)
+tabcov <- rbind(tabcov, tab)
+row.names(tabcov) <- NULL
+for (i in 1:dim(tabcov)[1]) {
+  s <- paste(tabcov[i,], collapse = ' & ')
+  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
+  cat(paste(s, ' \\\\ ', sep = ''), '\n')
+}
+```
 \hline \\[-1.8ex] 
@@
 \hline \\[-1.8ex] 
-Number of Houses & 276.41 & 243.58 & 255.20 &  2.368 & 0.098 \\ 
-Number of Households & 885.67 & 750.34 & 785.18 &  3.765 & 0.026 \\ 
-Avg. Household Size &   3.21 &   3.07 &   3.07 &  6.566 & 0.002 \\ 
-Log Avg. Income &   6.47 &   6.86 &   6.85 &  9.213 & 0.000 \\ 
-Cases Before Treatment &  13.78 &   5.94 &   4.66 & 15.638 & 0.000 \\ 
+```{r, echo = FALSE, cache=TRUE, results='asis'}
+## Census Sectors characteristics
+tabcov <- data.frame()
+
+# Number of Houses
+x = tapply(dfr2$NHouses, 
+           dfr2$D1,
+           mean)
+y = summary(aov(NHouses~D1, data = dfr2))
+tab <- data.frame(Var = 'Number of Houses',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Age
+x = tapply(dfr2$NHouseholds, 
+           dfr2$D1,
+           mean)
+y = summary(aov(NHouseholds~D1, data = dfr2))
+tab <- data.frame(Var = 'Number of Households',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# AvgHouseholdSize
+x = tapply(dfr2$AvgHouseholdSize, 
+           dfr2$D1,
+           mean)
+y = summary(aov(AvgHouseholdSize~D1, data = dfr2))
+tab <- data.frame(Var = 'Avg. Household Size',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Avg. Income Households
+x = tapply(dfr2$logAvgIncomeHousehold, 
+           dfr2$D1,
+           mean)
+y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2))
+tab <- data.frame(Var = 'Log Avg. Income',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Cases Before
+x = tapply(dfr2$plac, 
+           dfr2$D1,
+           mean)
+y = summary(aov(plac~D1, data = dfr2))
+tab <- data.frame(Var = 'Cases Before Treatment',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+row.names(tabcov) <- NULL
+## re-weighting
+dfr2$weightsD1 = weightit(D1~NHouses+
+                    NHouseholds+AvgHouseholdSize+
+                    logAvgIncomeHousehold+plac, 
+                  data = dfr2, focal = "No bonus", 
+                  method = 'cbps',
+                  estimand = "ATT")$weights
+
+dfr$weightsD1 <- weightit(D1~NHouses+
+                    NHouseholds+AvgHouseholdSize+
+                    logAvgIncomeHousehold+plac, 
+                  data = dfr, focal = "Control", 
+                  method = 'cbps',
+                  estimand = "ATT")$weights
+
+dfr$weightsD2 <- weightit(D2~NHouses+
+                            NHouseholds+AvgHouseholdSize+
+                            logAvgIncomeHousehold+plac, 
+                          data = dfr, focal = "No intervention", 
+                          method = 'cbps',
+                          estimand = "ATT")$weights
+for (i in 1:dim(tabcov)[1]) {
+  s <- paste(tabcov[i,], collapse = ' & ')
+  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
+  cat(paste(s, ' \\\\ ', sep = ''), '\n')
+}
+```
 \hline \\[-1.8ex] 
@@
 \hline \\[-1.8ex] 
-Number of Houses & 276.41 & 282.04 & 281.19 & 0.068 & 0.935 \\ 
-Number of Households & 885.67 & 903.04 & 900.39 & 0.060 & 0.942 \\ 
-Avg. Household Size &   3.21 &   3.21 &   3.20 & 0.008 & 0.992 \\ 
-Log Avg. Income &   6.47 &   6.45 &   6.45 & 0.084 & 0.920 \\ 
-Cases Before Treatment &  13.78 &  10.24 &  10.77 & 1.443 & 0.240 \\ 
+```{r, echo = FALSE, cache=TRUE, results='asis'}
+tabcov <- data.frame()
+# Number of Houses
+x = dfr2 %>%
+  group_by(D1) %>%
+  summarise(x = weighted.mean(NHouses, weightsD1),
+            .groups = 'drop')
+x = x$x
+x
+y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
+tab <- data.frame(Var = 'Number of Houses',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Number of households
+x = dfr2 %>%
+  group_by(D1) %>%
+  summarise(x = weighted.mean(NHouseholds, weightsD1),
+            .groups = 'drop')
+x = x$x
+y = summary(aov(NHouseholds~D1, data = dfr2, weights=dfr2$weightsD1))
+tab <- data.frame(Var = 'Number of Households',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# AvgHouseholdSize
+x = dfr2 %>%
+  group_by(D1) %>%
+  summarise(x = weighted.mean(AvgHouseholdSize, weightsD1),
+            .groups = 'drop')
+x = x$x
+y = summary(aov(AvgHouseholdSize~D1, data = dfr2, 
+                weights=dfr2$weightsD1))
+tab <- data.frame(Var = 'Avg. Household Size',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Avg. Income Households
+x = dfr2 %>%
+  group_by(D1) %>%
+  summarise(x = weighted.mean(logAvgIncomeHousehold, weightsD1),
+            .groups = 'drop')
+x = x$x
+y = summary(aov(logAvgIncomeHousehold~D1, data = dfr2, 
+                weights=dfr2$weightsD1))
+tab <- data.frame(Var = 'Log Avg. Income',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+
+# Cases Before
+x = dfr2 %>%
+  group_by(D1) %>%
+  summarise(x = weighted.mean(plac, weightsD1),
+            .groups = 'drop')
+x = x$x
+y = summary(aov(plac~D1, data = dfr2, weights=dfr2$weightsD1))
+tab <- data.frame(Var = 'Cases Before Treatment',
+                  NoBonus = round(x[1],2),
+                  Individual = round(x[2],2),
+                  Collective = round(x[3],2),
+                  FVal = round(y[[1]][1,4], 3),
+                  Pvalue = round(y[[1]][1,5], 3))
+tabcov <- rbind(tabcov, tab)
+row.names(tabcov) <- NULL
+for (i in 1:dim(tabcov)[1]) {
+  s <- paste(tabcov[i,], collapse = ' & ')
+  s <- gsub('NA', '', paste(tabcov[i,], collapse = ' & '))
+  cat(paste(s, ' \\\\ ', sep = ''), '\n')
+}
+```
 \hline
-Pairs & 34 & 34 & 35 &  &  \\ 
-N & 68 & 68 & 70 &  &  \\
+Pairs & 29 & 32 & 37 &  &  \\ 
+N & 58 & 64 & 74 &  &  \\
 \hline\hline \\[-1.8ex] 
@@
 subjects into three groups and directed each group to separate headquarters to
-avoid spillovers. In the control group ($n = 68$), we told participants that
+avoid spillovers. In the control group ($n = $ `r as.numeric(table(prodfr$D)[1])`), we told participants that
 they would receive a flat payment regardless of their performance (BRL 110 /
-USD 25 per subject). In the individual treatment group ($n = 68$), we informed
+USD 25 per subject). In the individual treatment group ($n = $ `r as.numeric(table(prodfr$D)[2])`), we informed
 subjects that we would rank each subject separately and double the compensation
 for those who performed above the sample median (BRL 220 / USD 50 per subject).
-In the collective treatment group ($n = 70$), we explained that we would rank
+In the collective treatment group ($n = $ `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
 the performance of each group and double the payment for those teams whose
@@
 
-\begin{table}[ht] \centering 
-  \caption{Field Productivity} 
-  \label{tab:productivity} 
-\begin{tabular}{@{\extracolsep{5pt}}lcccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent Variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & Houses & Houses & Breeding & Larvae \\ 
-& Visited & Visited ($<$ 2min.) & Sites & Exterminated \\ 
-\hline \\[-1.8ex] 
- Individual Bonus & $-$9.879$^{**}$ & $-$8.044$^{**}$ & 25.118$^{***}$ & 0.022 \\ 
-  & (4.906) & (4.018) & (5.251) & (0.058) \\ 
-  & & & & \\ 
- Collective Bonus & $-$7.554$^{*}$ & $-$6.479$^{*}$ & 21.512$^{***}$ & 0.163$^{**}$ \\ 
-  & (4.428) & (3.571) & (4.049) & (0.076) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 197 & 197 & 197 & 197 \\ 
-Residual SE & 27.301 & 22.153 & 30.545 & 0.425 \\ 
-\hline 
-\hline\\[-1.8ex]
-\multicolumn{5}{l}{\footnotesize \textbf{Note}: Robust standard errors
-clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
-$^{**}$p$<$0.05; $^{***}$p$<$0.01.} 
-\end{tabular} 
-\end{table}
+```{r, echo = FALSE, results='asis', warning=FALSE}
+## Productivity outcome
+mprod <- list()
+mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
+mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
+mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
+mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
+stargazer(mprod[[1]], mprod[[2]],
+          mprod[[3]], mprod[[4]],
+          se = starprep(mprod[[1]], mprod[[2]],
+                        mprod[[3]], mprod[[4]],
+                        se_type = "HC1"),
+          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}', 
+                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}',
+                             '\\shortstack{Breeding Sites \\\\ Terminated}',
+                             '\\shortstack{Larvae \\\\ Terminated}'),
+          keep.stat = c('ser', 'n'),
+          notes = c('Robust Standard Errors in parenthesis.'),
+          keep = c('DIndividual', 'DCollective'),
+          covariate.labels = c('Individual Bonus',
+                               'Collective Bonus'),
+          title = 'Field Productivity', header = FALSE,
+          label = 'tab:productivity')
+```
 
@@
 We find that subjects in the individual and in the collective bonus groups
-visited $-9.879$ (CI: [XXX, XXX]) and $-7.554$ (CI: [XXX, XXX]) households,
+visited `r round(as.numeric(coef(mprod[[1]])[2]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) and `r round(as.numeric(coef(mprod[[1]])[3]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,2]`]) households,
 respectively.
@@
 significantly lower than those of the control condition. On average,
-participants in the individual bonus treatment arm visited $-8.044$ (CI: [XXX,
-XXX]) houses than the control, and those in the collective bonus group visited
-$-6.479$ (CI: [XXX, XXX]).
+participants in the individual bonus treatment arm visited `r round(as.numeric(coef(mprod[[2]])[2]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,1]`,
+`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) houses than the control, and those in the collective bonus group visited
+`r round(as.numeric(coef(mprod[[2]])[3]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,2]`]).
 
 Incentivised teams find and clean more breeding sites than non-incentivised
-ones. Individually incentivised health workers find 25.118 (CI: [XXX, XXX])
+ones.
+Individually incentivised health workers find `r round(as.numeric(coef(mprod[[3]])[2]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,2]`])
 more breeding sites than the non-incentivised control group. The effect for
-those in the collective bonus group is 21.512 (CI: [XXX, XXX]), slightly
+those in the collective bonus group is `r round(as.numeric(coef(mprod[[3]])[3]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,2]`]), slightly
 smaller than for the individual treatment.
@@
 Teams which received collective bonuses are the most effective in finding
-larvae. Subjects who worked in pairs have a 16.3% (CI: [XXX, XXX]) higher
+larvae.
+Subjects who worked in pairs have a `r round(as.numeric(coef(mprod[[4]])[3]*100),1)`% (CI: [`r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,1]*100`%, `r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,2]*100`%]) higher
 likelihood of finding larvae than those in the control group. Locating mosquito
@@
 
-\begin{table}[ht] \centering 
-  \caption{Disease Incidence -- Differences in Differences Model} 
-  \label{tab:incidence} 
-\begin{tabular}{@{\extracolsep{1pt}}lccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{5}{c}{\textit{Dependent Variable:}} \\ 
-\cline{2-6} 
-\\[-1.8ex] & N Infected & N Infected & N Infected & N Infected & N Infected \\
-& (Full) & (12 Weeks) & (8 Weeks) & (4 Weeks) & (Indv. x Collect.) \\ 
-\hline \\[-1.8ex] 
- Diff-in-diff & $-$0.103$^{*}$ & $-$0.130 & $-$0.167 & $-$0.097 & $-$0.029 \\ 
-  & (0.053) & (0.091) & (0.118) & (0.166) & (0.035) \\ 
-  & & & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 7,452 & 3,312 & 1,656 & 828 & 2,201 \\ 
-Residual SE & 1.004 & 1.319 & 1.442 & 1.513 & 0.381 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\multicolumn{6}{l}{\footnotesize \textbf{Note}: Robust standard errors
-clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
-$^{**}$p$<$0.05; $^{***}$p$<$0.01.} 
-\end{tabular} 
-\end{table}
+```{r, echo = FALSE, results='asis'}
+mod <- list()
+mod[[1]] <- felm(ncas4weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
+mod[[2]] <- felm(ncas8weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
+mod[[3]] <- felm(ncas12weekwindow ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
+mod[[4]] <- felm(ncas ~ Tm2+D+DID|0|0|CensusSectors, data = did_full)
+stargazer(mod[[1]], mod[[2]], mod[[3]], mod[[4]],
+          dep.var.labels = c('\\shortstack{Four \\\\ Weeks Window}',
+                             '\\shortstack{Eight \\\\ Weeks Window}',
+                             '\\shortstack{Twelve \\\\ Weeks Window}',
+                             '\\shortstack{Sixteen \\\\ Weeks Window}'),
+          keep.stat = c('ser', 'n'),
+          keep = c('DID'),
+          notes = c('Robust standard errors clustered at the census tract level in parentheses.'),
+          label = 'tab:incidence',
+          covariate.labels = c('Dif-in-Dif'),
+          dep.var.caption = "Disease Incidence Before and After Intervention:",
+          title = 'Differences-in-Differences Model', header = FALSE)
+```
 
-The intervention lowered dengue incidence in 10.3\% (CI: [XXX, XXX]) if we take
+The intervention lowered dengue incidence in `r round(as.numeric(coef(mod[[4]])[4])*100, 1)`% (CI: [`r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.low[4]*100, 1)`%, `r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.high[4]*100, 1)`%]) if we take
 both treatments together and compare them with the control group. The result is
@@
 not reach conventional levels of statistical significance. This suggests that
-the treatment effect is probably small. The comparison between the two
-treatment statuses show an impact of 2.9\% (CI: [XXX, XXX]) fewer infections in
-the collective bonus group. However, the result is also not statistically
-significant.
+the treatment effect is probably small.
 
@@
 
-\begin{table}[ht]
-  \caption{Disease Incidence in Rio Verde Census Tracts} \centering 
-  \label{tab:census} 
-\begin{tabular}{@{\extracolsep{1pt}}lcccccr}
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{Dependent Variable:}} \\ 
-\cline{2-7} 
-\\[-1.8ex] & Before & 15 Days & 30 Days & 60 Days & 90 Days & 30-60 Days \\ 
-& Intv. & After Intv. & After Intv. & After Intv. & After Intv. & After Intv. \\
-\hline \\[-1.8ex] 
- Individual & $-$3.534 & 0.116 & 0.551 & 1.551 & 1.534 & 0.936 \\ 
-  & (2.919) & (1.338) & (2.193) & (3.260) & (3.258) & (1.188) \\ 
-  & & & & & & \\ 
- Collective & $-$3.008 & $-$1.329 & $-$0.826 & 0.344 & 1.091 & 1.068 \\ 
-  & (4.174) & (1.440) & (1.971) & (3.233) & (3.610) & (1.582) \\ 
-  & & & & & & \\ 
-\hline \\[-1.8ex] 
-Observations & 139 & 139 & 139 & 139 & 139 & 139 \\ 
-Residual Std. Error & 9.442 & 4.076 & 6.095 & 8.896 & 9.341 & 3.536 \\ 
-\hline 
-\hline \\[-1.8ex] 
-\multicolumn{7}{l}{\footnotesize \textbf{Note}: Robust standard errors
-clustered at the census tract level in parentheses. $^{*}$p$<$0.1;
-$^{**}$p$<$0.05; $^{***}$p$<$0.01.}\\
-\end{tabular} 
-\end{table}
+```{r, echo=FALSE, results='asis'}
+## Health outcome
+moutc <- list()
+moutc[[1]] <- lm(nc15dafter ~ D1,
+                 data = dfr2, weights = dfr2$weightsD1)
+moutc[[2]] <- lm(nc30dafter ~ D1,
+                 data = dfr2, weights = dfr2$weightsD1)
+moutc[[3]] <- lm(nc60dafter ~ D1,
+                 data = dfr2, weights = dfr2$weightsD1)
+moutc[[4]] <- lm(nc90dafter ~ D1,
+                 data = dfr2, weights = dfr2$weightsD1)
+moutc[[5]] <- lm(nc30to60dafter ~ D1,
+                 data = dfr2, weights = dfr2$weightsD1)
+moutc[[6]] <- lm(plac ~ D1,
+                 data = dfr2, weights = dfr2$weightsD1)
+
+stargazer(moutc[[6]], moutc[[1]], moutc[[2]], 
+          moutc[[3]], moutc[[4]], moutc[[5]],
+          se = starprep(moutc[[6]], moutc[[1]], 
+                        moutc[[2]], moutc[[3]], 
+                        moutc[[4]], moutc[[5]],
+                        se_type = "HC1"),
+          dep.var.labels = c('\\shortstack{Before \\\\ Int.}',
+                             '\\shortstack{Fifteen \\\\ Days \\\\ After Int.}',
+                             '\\shortstack{Thirty \\\\ Days \\\\ After Int.}',
+                             '\\shortstack{Sixty \\\\ Days \\\\ After Int.}', 
+                             '\\shortstack{Ninety \\\\ Days \\\\ After Int.}',
+                             '\\shortstack{Btw. Thirty \\\\ \\& Sixty Days \\\\ After Int.}'), label = 'tab:census',
+          keep.stat = c('ser', 'n'),
+          keep = c('D1Individual', 'D1Collective'),
+          covariate.labels = c('Individual Bonus',
+                               'Collective Bonus'),
+          dep.var.caption = "Number of Reported Hospital Cases:",
+          title = 'Disease Incidence', header = FALSE,
+          font.size = 'small')
+```
 

### 2021-02-22 manuscript/article.Rmd
change code not working

@@
 
-The intervention lowered dengue incidence in `r round(as.numeric(coef(mod[[4]])[4])*100, 1)`% (CI: [`r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.low[4]*100, 1)`%, `r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.high[4]*100, 1)`%]) if we take
+The intervention lowered dengue incidence in 10.3% (CI: [-18.9%, -1.6%]) if we take
 both treatments together and compare them with the control group. The result is

### 2021-02-22 manuscript/article.Rmd
changes size and footnote

@@
 subjects into three groups and directed each group to separate headquarters to
-avoid spillovers. In the control group ($n = $ `r as.numeric(table(prodfr$D)[1])`), we told participants that
+avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`), we told participants that
 they would receive a flat payment regardless of their performance (BRL 110 /
-USD 25 per subject). In the individual treatment group ($n = $ `r as.numeric(table(prodfr$D)[2])`), we informed
+USD 25 per subject). In the individual treatment group (n = `r as.numeric(table(prodfr$D)[2])`), we informed
 subjects that we would rank each subject separately and double the compensation
 for those who performed above the sample median (BRL 220 / USD 50 per subject).
-In the collective treatment group ($n = $ `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
+In the collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
 the performance of each group and double the payment for those teams whose
@@
 the treatment statuses with incidence figures in the control group. The unit of
-analysis is the census tract. Table \ref{tab:incidence} displays the results
+analysis is the census tract.\footnote{There were 139 Census Tracts analyzed by the 96 pairs.
+This because 43 pairs worked in more than one Census tract at once.} Table \ref{tab:incidence} displays the results
 for our first model, in which we measure the impact of our intervention after 4,

### 2021-02-22 manuscript/article.Rmd
change footnote placement

@@
 the treatment statuses with incidence figures in the control group. The unit of
-analysis is the census tract.\footnote{There were 139 Census Tracts analyzed by the 96 pairs.
-This because 43 pairs worked in more than one Census tract at once.} Table \ref{tab:incidence} displays the results
+analysis is the census tract. Table \ref{tab:incidence} displays the results
 for our first model, in which we measure the impact of our intervention after 4,
@@
 counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
-days after the treatment.
+days after the treatment.\footnote{There were 139 Census Tracts analyzed by the 96 pairs. This because 43 pairs worked in more than one Census tract at once.}
 

### 2021-02-22 manuscript/article.Rmd
changed texts

@@
 larvae.
-Subjects who worked in pairs have a `r round(as.numeric(coef(mprod[[4]])[3]*100),1)`% (CI: [`r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,1]*100`%, `r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,2]*100`%]) higher
+Subjects who worked under this treatment status have a `r round(as.numeric(coef(mprod[[4]])[3]*100),1)`% (CI: [`r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,1]*100`%, `r round(coefci(mprod[[4]], vcov = vcovHC(mprod[[4]], type = "HC1"), level = 0.9), digits=3)[3,2]*100`%]) higher
 likelihood of finding larvae than those in the control group. Locating mosquito
@@
 counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
-days after the treatment.\footnote{There were 139 Census Tracts analyzed by the 96 pairs. This because 43 pairs worked in more than one Census tract at once.}
+days after the treatment.\footnote{The 96 pairs analysed 139 Census Tracts. This because 43 pairs worked in more than one Census tract at once.}
 

### 2021-02-22 manuscript/article.Rmd
WIP

--- 2021-02-22 manuscript/article.Rmd
@@
 options(repos = r)
+
 # Install required packages
-pkgs <- c('tidyverse', 'magrittr', 'lmtest',
-          'estimatr', 'sandwich', 'stargazer',
-          'gridExtra', 'WeightIt', 'robustHD', 
-          'kableExtra', 'lfe')
+pkgs <- c("tidyverse", "magrittr", "lmtest",
+          "estimatr", "sandwich", "stargazer",
+          "gridExtra", "WeightIt", "robustHD",
+          "kableExtra", "lfe", "fixest")
 
@@
 # Load data
-load('../data/incentives_healthcare.RData')
+load("../data/incentives_healthcare.RData")
 ```
@@
 
-\noindent \textbf{Background}. Mosquito control strategies are the primary
-means to reduce \textit{Aedes aegypti} infections worldwide. However,
-insecticide spraying is conducted inconsistently across the developing world.
-Recent studies indicate that financial incentives may increase the productivity
-of health personnel, yet there is little evidence on the impact of monetary
-rewards on \textit{A. aegypti}-reduction programmes. We evaluated whether
-individual and collective financial incentives improves the performance of
-healthcare workers fighting \textit{A. aegypti}, as well as their effect on
-city-level numbers of dengue hospitalisations.
+\noindent \textbf{Background}. Mosquito control is the primary means to reduce
+\textit{Aedes aegypti} infections worldwide. However, programmes such as
+insecticide spraying and elimination of breeding sites are conducted
+inconsistently in many developing nations. Recent studies indicate that
+financial incentives may increase the productivity of health personnel, yet
+there is little evidence about the impact of monetary rewards on \textit{A.
+aegypti}-reduction strategies. We evaluated whether individual and collective
+financial incentives improve the performance of healthcare workers fighting
+\textit{A. aegypti}, as well as their effect on city-level numbers of dengue
+hospitalisations.
 
@@
 mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
-trial, we provided individual and team bonuses to two treatment groups, while
-the control group received a flat compensation for completing their tasks.
-Financial bonuses increased the number of cleaned breeding sites in both
+trial, we provided individual and team bonuses to two treatment groups, and
+offered a flat compensation to the control group for completing their tasks.
+Financial rewards increased the number of cleaned breeding sites in both
 treatment groups (individual and team bonuses) and the collective treatment
@@
 \vspace{.3cm} 
-\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
+\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial
+incentives, mosquito control, preventive health care, randomised field
+experiment, worker productivity 
 \end{abstract}
@@
 subjects into three groups and directed each group to separate headquarters to
-avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`), we told participants that
+avoid spillovers. In the control group ($n = $ `r as.numeric(table(prodfr$D)[1])`), we told participants that
 they would receive a flat payment regardless of their performance (BRL 110 /
-USD 25 per subject). In the individual treatment group (n = `r as.numeric(table(prodfr$D)[2])`), we informed
+USD 25 per subject). In the individual treatment group ($n = $ `r as.numeric(table(prodfr$D)[2])`), we informed
 subjects that we would rank each subject separately and double the compensation
 for those who performed above the sample median (BRL 220 / USD 50 per subject).
-In the collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
+In the collective treatment group ($n = $ `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
 the performance of each group and double the payment for those teams whose
@@
 
-The intervention lowered dengue incidence in 10.3% (CI: [-18.9%, -1.6%]) if we take
+The intervention lowered dengue incidence in `r round(as.numeric(coef(mod[[4]])[4])*100, 1)`% (CI: [`r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.low[4]*100, 1)`%, `r round(tidy(mod[[4]], conf.level = 0.9, conf.int = T)$conf.high[4]*100, 1)`%]) if we take
 both treatments together and compare them with the control group. The result is
@@
 counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
-days after the treatment.\footnote{There were 139 Census Tracts analyzed by the 96 pairs. This because 43 pairs worked in more than one Census tract at once.}
+days after the treatment.
 

### 2021-02-22 appendix/appendix.Rmd

--- 2021-02-22 appendix/appendix.Rmd
@@
 title: |
-       | Supplementary Materials for "Financial Incentives and Health Care Provision: Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil"
+       | Supplementary Materials for "Financial Incentives and Healthcare Provision: Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil"
 author:
@@
 
-[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
+[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
 
@@
 # Knitr options
-knitr::opts_chunk$set(fig.pos = "H") # holds figure position
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-Consider a strategic interaction between two healthcare workers and a government agency.\footnote{This model was inspired in the @bolton2005contract and the @itoh1991incentives.
-It is a particular case of their model, aimed at illustrate the effects of our treatment.} The agency hires healthcare workers to provide preventive healthcare.
+Consider the following interaction between healthcare workers and a government agency.\footnote{This model was inspired by @bolton2005contract and @itoh1991incentives.
+Here we present a particular case of their model to illustrate the effects of our treatment.} The agency hires the workers to provide preventive healthcare.
 And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.
 
-From the perspective of healthcare workers, teams perform preventive healthcare tasks.
-To inspect a house and eliminate mosquito breeding sites, preventive healthcare workers visit the households in pairs or threesomes.
+Workers perform preventive healthcare tasks.
+To inspect a house and eliminate mosquito breeding sites, healthcare workers visit the households in pairs or in groups of three.
 Supposedly, this increases efficiency as it helps the team cover more territory and be more careful in the areas they inspect individually.
 Team structures also help in terms of lowering free-riding and increasing incentives for cooperative work.
-To capture this, we assume that a given worker $i$ divides her effort into two tasks: own work effort ($e_i$) and helping efforts ($h_i$).
+To capture this, we assume that a given worker $i$ divides her work effort into two tasks: those which she accomplishes with her own effort ($e_i$) and helping efforts ($h_i$).
 To capture the costs of effort, we assume the following convex cost function $\dfrac{c}{2}(e_i^2 + h_i^2)$, where $c>0$ represents the changes in marginal costs of effort and help.
@@
 Preventive healthcare aims to lower the chance of a person getting sick.
-For example, washing one's hands lowers the chance of a person getting the flu, but from time to time, a person gets the flu regardless of how many times she washes her hands.
+For example, washing one's hands lowers the chance of flu infections, but from time to time a person gets the flu regardless of how many times she washes her hands.
 The only difference is that a person who washes her hands constantly has a lower chance of getting sick and will get sick fewer times during her lifespan.
@@
 For simplicity, we assume that the probabilities are separable, with $P(e_i, h_i, e_j, h_j) = P_i(e_i, h_j) + P_j(e_j, h_i)$.
-To make the output more concrete, assume that a given worker $i$ has an individual probability of $P_i(e_i, h_j) = e_i(1+h_j)$ of successfully lowering the disease burden with her effort ($e_i$) and the help of her peer ($h_j$).
-
-From the perspective of the agency, the successful work grants a benefit of $B>0$.
-This benefit represents the social gains of lowering the amount of disease incidence in the municipality.
-For example, the payoff could be the amount of money saved from fewer hospitalizations or the economic benefit of fewer people missing work due to diseases transmitted by \textit{Aedes aegypti}.
-The agency incentivizes workers through salaries with three components: a flat salary without bonuses, individual compensation, and a bonus when the entire team achieves their collective objectives.
+To make the output more concrete, assume that a given worker $i$ has an individual probability of $P_i(e_i, h_j) = e_i(1+h_j)$ of successfully lowering the disease burden with her effort ($e_i$) and with the help of her peer ($h_j$).
+
+From the perspective of the agency, successful work grants a benefit of $B>0$.
+This benefit represents the social gains of lowering disease incidence in the municipality.
+For example, the payoff could be the amount of money saved from fewer hospitalisations or the economic benefit of fewer people missing work due to \textit{A.
+aegypti}-transmitted diseases.
+The agency incentivises workers via three types of salaries: a flat salary without bonuses, an individual compensation, and a bonus when the entire team achieves their collective objectives.
 These formulations allow us to disentangle which scheme offers the highest yield in terms of disease prevention.
 
-The optimal scheme to improve welfare is a contract where the government agency offers a compensation package, and the two healthcare providers choose their effort accordingly.
+The optimal scheme to improve welfare is a contract where the government agency offers a compensation package, and the healthcare providers choose their effort accordingly.
 From the perspective of the worker, the expected utility of effort, provided that the compensation depends on successful provision of the service, and that the benefit from salary is given by a concave function $u(.)$.
@@
 
-The situation is a standard contract theory problem, where we have three compensation packages: no bonus ($w_{both} = w_{one} = 0$), individual bonus ($w_{both} = w_{one} \neq 0$), and collective bonus ($w_{both} \neq w_{one}$, $w_{both} \neq 0$, and $w_{one} \neq 0$).
-The optimal contract is then the solution for the following constrained optimization problem:
+The situation is a standard contract theory problem, in which we have three compensation packages: no bonus ($w_{both} = w_{one} = 0$), individual bonus ($w_{both} = w_{one} \neq 0$), and collective bonus ($w_{both} \neq w_{one}$, $w_{both} \neq 0$, and $w_{one} \neq 0$).
+The optimal contract is then the solution for the following constrained optimisation problem:
 
@@
 
-## Baseline: no incentive bonuses
-
-When the agency only pays a flat salary without performance incentives, the agency sets the performance compensation equals to zero: $w_{both} = w_{one} = 0$.
+## Baseline: No Incentive Bonuses
+
+When the agency only pays a flat salary without performance incentives, the agency sets the performance compensation equal to zero: $w_{both} = w_{one} = 0$.
 This changes the expected utility of the agent to the following:
@@
 
-The prediction here is that workers will exert no effort, and the agency will have only costs without accruing any benefit.
+The prediction here is that workers will exert no effort, and that the agency will have only costs without accruing any benefit.
 This is the worst-case scenario in terms of the agency's welfare.
 In the experiment, it matches the control condition.\footnote{Throughout the chapter, we assume that the optimal output for the agency is equal to the maximum welfare for society.
-Although this is not always the case, it is a reasonable simplification for the purposes of this chapter.
-Adding a difference here would only complicate my results and provide no further insight into designing an incentive scheme to maximize welfare.}
-
-## Performance bonus for individuals
+Although this is not always the case, it is a reasonable simplification for the purposes of this article.
+Adding a difference here would only complicate our results and provide no further insight into designing an incentive scheme to maximise welfare.}
+
+## Performance Bonus for Individuals
 
@@
 Each worker then evaluates the utility of the bonus as $u_i(\alpha) = \sqrt{\alpha}$, as the utility of the agent is concave, representing the risk aversion of the agent.
-The optimization problem, from the perspective of the agent, is to maximize her expected utility, given the bonus offered by the government agency upon achieving a successful provision:
+The optimisation problem, from the perspective of the agent, is to maximise her expected utility, given the bonus offered by the government agency upon achieving a successful provision:
 
@@
 Both workers face the same incentive structure, so the equilibrium is symmetric, with $e_i = e_j$.
-Taking the derivative and equating it to zero, gives us the following optimal effort level: $e_i^* = e_j^* = \dfrac{\sqrt{\alpha}}{c}$.
+Taking the derivative and equating it to zero, we find the following optimal effort level: $e_i^* = e_j^* = \dfrac{\sqrt{\alpha}}{c}$.
 The optimal level of effort represents the point where the marginal benefit from the government agency's compensation is equal to the marginal cost of effort.
 The benefit of a successful provision of the healthcare service is equal to -- for both players -- the total benefit times the chance of a successful provision times the difference between the benefit accrued from a successful provision minus the bonus paid for the worker.
-To compute the optimal contract the government agency has to offer in this setting, we must choose $\alpha$ to maximize the agency's expected utility:
+To compute the optimal contract the government agency has to offer in this setting, we must choose $\alpha$ to maximise the agency's expected utility:
 
@@
 
-## Performance bonus for teams
+## Performance Bonus for Teams
 
 When the government agency sets rewards for both individual and team performance, healthcare workers divide their time between expending effort in their job ($e_i$) and helping their teams to get their jobs done ($h_i$).
-Helping may take many forms: from simple peer pressure and monitoring to ensure the peer is doing the job well, to efficiently dividing tasks and exploiting complementarities in their duties.
-From the government agency's perspective, incentivizing workers to help each other can potentiate the chances of obtaining successful service provision.
-From the standpoint of healthcare workers, optimal effort becomes a mix of her own efforts and the helping efforts that maximize her expected utility, provided that both efforts are incentive-compatible.
+Helping may take many forms: from simple peer pressure and monitoring to ensure the peer is doing the job well, to efficiently dividing tasks and exploiting synergies in their duties.
+From the government agency's perspective, incentivising workers to help each other can increase the chances of obtaining successful service provision.
+From the standpoint of healthcare workers, optimal effort becomes a mix of her own efforts and the helping efforts that maximise her expected utility, provided that both efforts are incentive compatible.
 Incentive compatible means, in the case of healthcare workers, that both efforts are exerted to match the governmental agency's contractual incentives.
@@
 
-Again, both players are ex-ante similar in terms of their expected utilities. This allow us to solve for the Symmetric Nash Equilibrium, where:
+Again, both players are *ex-ante* similar in terms of their expected utilities. This allow us to solve for the Symmetric Nash Equilibrium, where:
 
@@
 
-Maximizing the expected utility leads us to the optimal effort and amount of help for the healthcare provider, given the contractual scheme. The optimal provision must satisfy the following equation:
+Maximising the expected utility leads us to the optimal effort and amount of help for the healthcare provider, given the contractual scheme. The optimal provision must satisfy the following equation:
 
@@
 
-The governmental agency now maximizes the bonus for the individual provision ($\alpha$), given that the collective provision is higher than it is.
-The expected revenue of the agency is equal to the chance of lowering the disease burden times the benefit minus the costs of paying the healthcare provider's salaries:
+The governmental agency now maximises the bonus for the individual provision ($\alpha$), given that the collective provision is higher than it is.
+The expected revenue of the agency is equal to the chance of lowering the disease burden times the benefit minus the costs of paying the salaries of the healthcare providers:
 
@@
 Therefore, the maximum benefit that the agency can achieve is higher when the agency compensates the workers for their cooperation.
-When the agency incentivizes team effort, workers can do better, on margin, by sharing the benefit of successful provision.\footnote{The limits for this reasoning appear when there are gains of specialization.
+When the agency incentivises team effort, workers can do better, on margin, by sharing the benefit of successful provision.\footnote{The limits for this reasoning appear when there are gains of specialisation.
 For instance, if the costs for effort and help were such that $\dfrac{c(e+h)^2}{2}$, then diverting energy for help is costly, on margin, at the same rate as the given effort provision.
@@
 
+## Data Sources
+
+We have five data sources in this study, all of them are included in `./data/incentives_healthcare.RData`:
+
+- `pretreat`: Pre-treatment balance information.
+- `prodfr`: Field productivity data.
+- `dfr`: Disease incidence in every Rio Verde census sector.
+- `dfr2`: Disease incidence in every Rio Verde census sector that received the intervention.
+- `did_full`: Differences-in-differences estimator that measures the effect of our intervention against a pure control group.
+
+### Pre-Treatment Balance Dataset
+
+The pre-treatment balance dataset contains information about every individuals who interacted with the experimental team at any point of time.
+To be included in this dataset, the person has to have filled the recruitment form we had circulated on Facebook as part of our campaign.
+The dataset contains 13 variables that we collected before the intervention.
+We gathered these data either via Google Forms, or in pre-treatment surveys before the training session.
+
+1. `Age`: Age of the participant.
+2. `Female`: Dummy for female participant.
+3. `HasVehicle`: Dummy for having a vehicle (car or motorcycle).
+4. `aboveMedianAltr`: Dummy for ranking above the sample median in our altruism scale.
+5. `relig`: Dummy for ranking above the sample median in our religiosity scale.
+6. `polengage`: Dummy for ranking above sample median in political engagement.
+7. `socengage`: Dummy for ranking above the sample median in social engagement.
+8. `collegeplus`: Dummy for having college degree or higher.
+9. `aboveTwoMinWageFam`: Dummy for earning more than two Brazilian minimum wages (R\$ 900.00 per month).
+10. `FBpop`: Dummy for having above median Facebook popularity.
+11. `training`: Dummy for having joined the training session.
+12. `participating`: Dummy for having participated in the field experiment.
+13. `assignment`: Dummy for treatment status assignment.
+
+### Field Productivity Dataset
+
+We collected field productivity data based on the subjects' performance during the experiment. We measured productivity using three indicators:
+
+1. Number of houses visited.
+2. Number of possible breeding sites exterminated.
+3. Number of larvae exterminated.
+
+We compiled these data using pictures taken in the field.
+All participants were instructed to take pictures of clean breeding sites, and to make videos showing the larvae they exterminated.
+After finishing the inspection of each household, subjects had to take a last picture of the house to prove that they had been there.
+
+The final dataset has the following variables:
+
+1. `D`: Treatment assignment.
+2. `pair_n`: Pair index ID.
+3. `nHouse`: Number of houses visited.
+4. `nBreed`: Number of breeding sites cleaned.
+5. `nLarvae`: Number of larvae exterminated.
+6. `nHouseVisit`: Number of houses that were indeed visited (based on having pictures of breeding sites and larvae videos).
+7. `nHouseLessTwoMin`: Number of houses visited in less than two minutes (which denotes either that the pair did not go to the place, or that there were no residents at home).
+
+### Disease Incidence Datasets
+
+To assess whether the intervention had an impact on the municipal healthcare system, we collected thirteen variables in two distinct datasets.
+All datasets compile data from the National Health Notification System (SINAN) for the  Rio Verde municipality.
+The dataset has the complete records of all individuals who had been hospitalised between four months before and four month after the intervention.
+We geolocated the household addresses of those individuals who were hospitalised with dengue fever, then we matched the case to the census sector where that person lives.
+Finally, we computed the number of cases before and after a few time windows around the intervention.
+The result is two datasets, `dfr` (with all census sectors) and `dfr2` (with only the census sectors matched in the intervention).
+Both datasets have the following variables:
+
+1. `CensusSectors`: Last three digits of census sector (2010 Brazilian census).
+2. `NHouses`: Number of houses in each census sector (2010 Brazilian census).
+3. `NHouseholds`: Average Number of households in each house/building and in each census sector (2010 Brazilian Census).
+4. `AvgHouseholdSize`: Average household income per census sector (2010 Brazilian Census).
+5. `logAvgIncomeHousehold`: Log of average household income per census sector (2010 Brazilian Census).
+6. `D1`: Treatment assignment.
+7. `D2`: Intervention x no intervention (no Intervention empty in `dfr2`).
+8. `nc15dafter`: Number of cases 15 days after the intervention.
+9. `nc30dafter`: Number of cases 30 days after the intervention.
+10. `nc60dafter`: Number of cases 60 days after the intervention.
+11. `nc90dafter`: Number of cases 90 days after the intervention.
+12. `nc30to60dafter`: Number of cases between 30 and 60 days after the intervention.
+13. `plac`: Number of cases before the intervention.
+
+### Differences-in-Differences Dataset
+
+We build `did_full` dataset to investigate whether the intervention had any impact on public health outcomes.
+The disease incidence data describes the treatment effect.
+In the differences-in-differences models, we combine all treatments and investigate how they perform against a pure control group, which are the census sectors that were not visited during the intervention.
+
+The dataset has ten variables:
+
+1. `CensusSectors`: Last three digits of census sector (2010 Brazilian Census).
+2. `D`: Treatment status census sector (intervention versus pure control).
+3. `weekn`: Week name.
+4. `ncas`: Number of cases in a given week and census sector.
+5. `Tm`: Week number.
+6. `Tm2`: Intervention timing indicator.
+7. `DID`: Differences-in-differences ($Tm2 \times D$).
+8. `ncas4weekwindow`: Number of cases four weeks window around the intervention.
+9. `ncas8weekwindow`: Number of cases eight weeks window around the intervention.
+10. `ncas12weekwindow`: Number of cases twelve weeks window around the intervention.
+
 ## Covariate Balance
 
-We checked the balance in the participation using four statistics.
-First, we study the decision to participate in the training day.
-Second, we studied the decision to participate in the experiment.
-It requires the person to show up for training, and then participate during the field.
-Third, we checked the balance in the individual characteristics collected by the pre-treatment survey.
-Finally, we checked the territorial assignment to make sure that the pre-treatment characteristics is balanced in the places that were undergoing visit.
-We run regressions for all the aspects above.
-We had balance for the individual assignment (models one to three), and for the territorial assignment, we had imbalance that was corrected using propensity-score matching.
+We measure covariate balance using four statistics.
+First, we check whether subjects decided to join us for the training day.
+Second, we assess their decision to participate in the experiment.
+Subjects had to take part in the training process and then participate in the fieldwork.
+Third, we checked if individual characteristics are balanced across our treatment groups.
+We collected that information via Google Forms and using a pre-treatment survey.
+Finally, we checked the territorial assignment to make sure that the pre-treatment characteristics are balanced in the places that subjects visited.
+We find a good level of balance for the individual assignment (models 1 to 3), and we corrected eventual imbalances in the territorial assignment using propensity-score matching [@rosenbaum1985constructing].
 
@@
 
-### Propensity-score Weighted Territorial Assignment
+### Propensity-Score Weighted Territorial Assignment
 
@@
 
-For the disease incidence regressions, the results in Table \ref{'diseasein} show all null effect.
+Table \ref{diseasein} shows that no treatment effect reaches conventional levels of statistical significance.
 
@@
 
-## Differences-in-differences for the Healthcare Outcomes
-
-For the differences-in-differences models, the results are in Table \ref{difindif}.
+## Differences-in-Differences Estimation for Healthcare Outcomes
+
+The results for the differences-in-differences estimations are available in Table \ref{difindif}.
 
@@
 
-Table \ref{difindif} shows the following:
+The results suggest the following:
 
 1. There is a 10.3\% effect on the full data model.
-2. The other windows are not significant but the sign is consistent with lower disease incidence.
+2. The coefficient for the other windows are not significant but the signs are consistent with lower disease incidence.
 
@@
 
-Here we use the American Political Science Association experimental session standard report to present all the details involved in the experiment.
+Here we follow the American Political Science Association Experimental Session Report Guidelines [@gerber2014reporting] and present a detailed discussion of our sample and research design.
 
@@
 
-### Question addressed by the experiment
-
-In this experiment, we study the impact of monetary incentives on the performance of health care workers in Brazil.
-The study aims to find which financial incentive scheme is better to improve the performance of the workers in the field.
-
-Most of the developmental economics papers on incentives for public service providers highlight that better compensation works.
-However, these papers focus on services that are individually provided, such as a teacher in a classroom.
-In health care, rarely the efforts are undertaken independently, and this poses the question: what is the best way to improve public health care provision, when teams, rather than individuals, provide the service?
-
-In this paper, we undertake the first effort to bridge this gap by testing whether team incentives are more effective than individual incentives to improve preventive healthcare provision in Brazil.
+### Question Addressed by the Experiment
+
+We study the impact of monetary incentives on the performance of healthcare workers in Brazil. Our goal is to find which financial incentive scheme improves healthcare worker productivity the most.
+
+Several articles highlight that higher payments improve public service provision [e.g., @doran2017impact; @duflo2012incentives; @langdown2014use].
+However, these papers focus on services that are provided individually, such as by a single a teacher in a classroom.
+In public health, it is rare that employees work independently.
+This, in turn, poses the question: what is the best way to improve public healthcare provision, when the services are delivered by teams rather than by individuals?
+
+Here we try to bridge this gap by testing whether team incentives are more effective than individual incentives to improve preventive healthcare provision in Brazil.
 
 The Brazilian case is well suited for this test for two main reasons.
-First, disease borne by the Aedes aegypti is one of the leading causes of congenital disabilities, hospitalization, and casualties in the global south.
-Second, a pair of health care workers are responsible for visiting households and exterminate the disease in Brazil.
+First, *A.
+aegypti*-borne diseases are some of the leading causes of congenital disabilities, hospitalisation, and casualties in the Global South.
+Second, Brazilian healthcare agents work in pairs when they are allocated to visit households and exterminate mosquito breeding sites.
 Therefore, we could test individual versus team bonuses in a setting that is relevant to welfare.
 
-### Hypothesis tested
-
-We tested which types of bonuses are better for improving the performance of health care workers in Brazil.
-We tested three incentive schemes: first, monetary compensation with no performance bonuses; second, individual compensation for performance above the median in the headquarter they were assigned; and third, peer bonus compensation for team performance above the median in the headquarters.
-Theoretically, team bonuses should be more effective, as it increases peer monitoring, diminishing the free-riding problem.
-However, if there are fewer complementarities, individual rewards can be more productive.
-This poses the question: which incentive scheme is better for community-based prevention of Aedes aegypti borne diseases in Brazil?
+### Hypothesis Tested
+
+We tested which types of monetary bonus improves the performance of healthcare workers in Brazil.
+We tested three incentive schemes: first, monetary compensation with no performance bonuses; second, individual compensation for performances above the median of the headquarter they were assigned; and third, peer bonus compensation for team performances above the median of their headquarters.
+Theoretically, team bonuses should be more effective, as they increase peer monitoring and reduce the free-rider problem.
+However, if there are few gains from synergies among workers, individual rewards can be more useful.
 
@@
 
-### Why was this subject pool selected?
-
-The subjects participating in the experiment were selected based on a Facebook recruitment Ad posted in the Municipality of Rio Verde, Goias State, Brazil.
-We chose this town because we had an agreement with the mayor's office, and also because it had a considerable spike in dengue fever cases in 2018.
-One of the Facebook ads follows below.
+### Why Was This Subject Pool Selected?
+
+We selected participants via Facebook recruitment advertisements, which we posted to citizens of the Municipality of Rio Verde, Goiás State, Brazil.
+We chose that city because it had a considerable spike in dengue fever cases in 2017 and 2008, what lead us to establish a partnership with the Mayor's Office especially to run the experiment we describe here.
+One of our Facebook ads is available below.
 
@@
 \includegraphics[width=\textwidth]{../figures/rvRecruit1.png}
-\caption{Facebook Recruitment Ad with Pilot Participants' picture.\label{appcfbad}}
+\caption{Facebook recruitment advertisement.\label{appcfbad}}
 \end{figure}
 
-The Facebook Ad redirected the participant to a Google Forms where s/he filled up a participation eligibility form. The Google form used is below.
+The Facebook Ad redirected the participant to a Google Forms where he or she filled up a participation eligibility form. The Google Form we employed is shown below.
 
@@
 \includegraphics[width=0.8\textwidth]{../figures/rvRecruit2.png}
-\caption{Google Form Recruitment.\label{appcgform}}
+\caption{Google form.\label{appcgform}}
 \end{figure}
 
-After that, we send them an email, asking questions on demographics and other characteristics.
-
-### Who was eligible to participate in the study?
-
-Adults, 18 old or older.
-
-### What would result in the exclusion of a participant?
-
-Being underage or not show up for the training and the intervention.
-
-### Were any aspects of recruitment changed after the recruitment began?
+We sent an email to participants and asked a few questions on demographics and other characteristics.
+
+### Who Was Eligible to Participate in the Study?
+
+Adults who were 18 years of age or older.
+
+### What Would Result in the Exclusion of a Participant?
+
+Being under-age or not participating in the training lessons or the intervention.
+
+### Were Any Aspects of Recruitment Changed after the Recruitment Began?
 
@@
 
-### Procedures used to recruit and select participants
+### Procedures Used to Recruit and Select Participants
 
 We posted a Facebook ad in the municipality participating in the intervention.
-The ad invited potential participants to join the research and explained the compensation.
-If they clicked the ad, they were directed to Google Forms, where they added their e-mails and personal information.
-
-### Recruitment dates
-
-The online recruitment took place right after filling up the form.
-We send potential participants information regarding Aedes aegypti prevention and a link for a pre-treatment survey.
-After filled, participants were informed about the live training dates and selected preferred times to participate.
-They then had to show up for the two-hour training session.
-
-The training date for the pilot was April 13, 2018. The training date for the intervention was May 4, 2018. A picture of the May 4 training day follows below.
+The ad invited potential participants to join the research and explained the payment scheme.
+If they clicked on the ad, they were directed to a Google Form, where they added their e-mail address and contact information.
+
+### Recruitment Dates
+
+The online recruitment took place right after respondents filled up the form.
+We sent a link containing a pre-treatment survey and some information about the *A.
+aegypti* mosquito to potential participants.
+After respondents completed the survey, we informed them about the in-person training dates and asked them to select their preferred times to participate.
+They had to join us for a two-hour training session.
+
+The training date for the pilot was the 13^th^ of April, 2018. The training date for the intervention was 4^th^ of May, 2018. A picture taken on the 4^th^ of May training day follows below.
 
@@
 
-### Settings and locations where the data were collected
-
-There are two primary datasets used in the paper.
+### Settings and Locations Where the Data Were Collected
+
+We use two primary datasets in the paper.
 First, we collected productivity data from the cell phones used by the participants in the field.
-Second, we collected governmental data on diseases transmitted by the Aedes aegypti from the Brazilian Ministry of Health diseases notification system (SINAN).
-
-The first dataset is generated by the participants pictures in the field.
-The second dataset is comprised of governmental records of people that checked into hospitals and were confirmed having dengue fever.
-This data has the address of the person, that we then used to geolocate the case.
-Among the diseases transmitted by the Aedes aegypti, dengue fever is the most frequent and easy to detect.
-
-### Relevant specifics about the population
-
-All the participants were from the municipality of Rio Verde, in the state of Goiás, in Brazil. A map of the municipality follows below:
+Second, we collected governmental data on *A.
+aegypti*-borne diseases from the Brazilian Ministry of Health diseases notification system (SINAN).
+
+The first dataset was generated by participants themselves and included the pictures taken during their fieldwork.
+The second dataset is comprised of governmental records of individuals that checked into hospitals and diagnosed with dengue fever.
+These data include the individual's home address, which we used to geolocate his or her household.
+Among the diseases transmitted by *A.
+aegypti*, dengue fever is the most prevalent and the easiest one to detect.
+
+### Relevant Information about the Population
+
+All participants were from the municipality of Rio Verde, in the state of Goiás, Brazil. A map of the municipality follows below:
 
@@
 \includegraphics[width=\textwidth]{../figures/rvMap.png}
-\caption{Rio Verde, GO, Brazil Map.\label{appcmaprv}}
+\caption{Map of Rio Verde, GO, Brazil.\label{appcmaprv}}
 \end{figure}
@@
 
-### Randomization procedure
-
-We generated the random assignment using block randomization applied on seven variables:
+### Randomisation procedure
+
+We generated the treatment assignment using block randomisation applied on seven variables:
 
 1. Age
-2. Above median altruism
-3. Above median religiosity score
-4. Above median Political Engagement
-5. Above median social engagement
-6. Above two minimum wage family income
-7. Above median Facebook popularity (number of friends)
-
-These variables were computed from surveys that we collected prior to the intervention.
-To test the balance, we use F-tests on the block randomization data.
+2. Altruism.
+3. Religiosity score.
+4. Political engagement.
+5. Social engagement.
+6. Family income higher than two minimum wages.
+7. Facebook popularity (number of friends).
+
+We computed these variables from our pre-treatment survey and Google Forms.
+To test the covariate balance, we used F-tests on the block randomisation data.
 The balance tests follow in the data analysis section.
 
-## Random assignment
-
-### Units of randomization
-
-We randomized the treatment at the level of the participant.
-
-### Cluster random assignment
-
-No cluster random assignment was used. However, in the differences-in-differences estimation, we use the census sector where the pair worked to cluster the standard errors.
+## Random Assignment
+
+### Units of Randomisation
+
+We randomised the treatment at the participant level.
+
+### Cluster Random Assignment
+
+We did not employ cluster random assignment. However, in the differences-in-differences estimation, we use the census sector where the pair worked to cluster the standard errors.
 
@@
 
-### Were participants unaware of the treatment assignment?
-
-Yes. They knew their incentive schemes, but not other incentive schemes. To ensure that there would be no spillovers, we divided each treatment assigned teams into three different headquarters:
+### Were Participants Unaware of the Treatment Assignment?
+
+Yes.
+They knew about their incentive schemes, but not about the other incentive schemes we implemented in our experiment.
+To ensure that there would be no spillovers, we divided each treatment assigned teams into three different headquarters:
 
@@
 
-### Were those administering the intervention unaware of the random assignment?
+### Were Those Administering the Intervention Unaware of the Random Assignment?
 
@@
 The head research assistants in each group knew that different treatment would be administered in other research headquarters.
-This measure was taken in case the treatment spillover, and we needed to remove pairs that were disturbing the work from the field.
-
-### Checked whether blind was successful?
+We took this measure because in case of treatment spillover we would have to quickly remove the pairs who knew about the treatment conditions.
+
+### Checked Whether Blind was Successful?
 
@@
 
-### Treatment groups
-
-We have three treatment groups:
+### Treatment Groups
+
+We have one control and two treatment groups in our experiment:
 
@@
 
-In the control group, a bonus was assigned without performance concerns.
-
-In the individual treatment group, we explained the participants that we would rank the performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated.
+In the individual treatment group, we explained to participants that we would rank their individual performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated.
 Participants would have their performance ranked and the ones above the median would double their monetary reward (from BRL 110.00 to BRL 220.00).
 
-In the collective treatment group, we explained the participants that we would rank their team performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated.
+In the collective treatment group, we informed participants that we would rank their team performance based on number of visited houses, number of breeding sites removed and cleaned, and number of larvae exterminated.
 We would sum their individual performance with the performance of their field peers, and then rank the teams.
-Teams with performance above the median would double their monetary reward (from BRL 110.00 to BRL 220.00, for each person in the team).
-
-The fieldwork was performed in pairs, to mimic the Aedes Aegypti actual practices in Brazil.
-
-### Control groups
+Teams with performance above the median would double their monetary reward (from BRL 110.00 to BRL 220.00 for each person in the team).
+
+The fieldwork was performed in pairs, to mimic the implementation of existing mosquito control strategies in the area.
+
+### Control Group
 
@@
 
-### Experimental instructions
-
-In the study day, around 5AM, we randomly assigned pairs, and send emails to the individuals directing them to each of the headquarters, based on their treatment status.
-
-We had three study headquarters: the control headquarters (Assembleia de Deus church); the individual treatment headquarters (Videiras church); and the peer treatment headquarters (Sara Nossa Terra church).
-We printed set of leaflets with places that they had to administer the treatment.
-One example of a leaflet follows below:
+### Experimental Instructions
+
+At 5:00 on intervention day, we randomly assigned pairs and sent emails to the individuals directing them to each of the headquarters, based on their treatment status.
+
+We had three headquarters: the headquarters for the control group (Assembleia de Deus church); the headquarters for the individual treatment group (Videiras church); and the headquarters for the peer treatment group (Sara Nossa Terra church).
+We printed set of leaflets with places that they had to visit in order to administer the treatment.
+One example leaflet follows below:
 
@@
 \includegraphics[width=0.8\textwidth]{../figures/rvWorkBlock.png}
-\caption{Example Working Area\label{appcevwbl}}
+\caption{Example Leaflet.\label{appcevwbl}}
 \end{figure}
@@
 \includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
-\caption{Example Working Area\label{appcevwbl}}
+\caption{Example Working Area.\label{appcevwbl}}
 \end{figure}
 
-We handed in the cellphones and the working kits for them. An example of the working kits design follows below:
+We handed in the cellphones and the working kits to subjects. An example of the working kit design follows below:
 
@@
 \includegraphics[width=0.8\textwidth]{../figures/rvKit3.jpeg}
-\caption{Teams Uniforms.\label{appcteamunif}}
+\caption{Teams Uniforms\label{appcteamunif}}
 \end{figure}
 
-The cellphone was a Samsung, model Galaxy A1. A picture with a testing of the data collection app follows below.
+The cellphone was a Samsung Galaxy A1. A screenshot of the data collection app follows below.
 
@@
 \includegraphics[width=0.4\textwidth]{../figures/rvApp.jpeg}
-\caption{Cellphone with data collection app in test.\label{appccpdcit}}
+\caption{Cellphone with Data Collection App.\label{appccpdcit}}
 \end{figure}
@@
 \includegraphics[width=0.8\textwidth]{../figures/rvKit5.jpg}
-\caption{Example leaflet handed to households.\label{appcexhhleafl}}
+\caption{Example Leaflet Handed to Households.\label{appcexhhleafl}}
 \end{figure}
 
-Then, at around 11:00am we administered the main treatments. They consisted in tell the following instructions to the participants, when we handed the leaflet with their working places:
+We administered the main treatments at 11:00. They consisted in telling the following instructions to participants after we handed the leaflet with their working places:
 
 - **Control:** we told them that there would be an increase in their payment without explaining the reason.
-We told them about how performance would be measured, without saying anything about compensation based on performance.
-- **Individual treatment:** we told the participants that we would measure their performances in the field, and that we would rank all the performances.
+We told them about how their performance would be measured, without saying anything about compensation based on performance.
+- **Individual treatment:** we told participants that we would measure their performances in the field, and that we would rank all performances.
 The individuals with performance above the median would receive the bonus.
-We also explained in lay terms what was a median, and how we would measure performance.
-- **Peer treatment:** we told the participants that we would measure their performances in the field, and that we would rank all the performances.
+We also explained in lay terms what a median is and how we would measure their performance.
+- **Peer treatment:** we told participants that we would measure their performances in the field, and that we would rank all performances.
 The pairs with performance above the median would receive the bonus.
-We also explained in lay terms what was a median, and how we would measure performance.
-
-## How and when manipulations were administered
-
-### Method of delivery
-
-The manipulations were delivered in person, by the chief headquarter RA, first to all the pairs in a speech, then to each pair in person.
-For each pair, we reinforced the instructions while handing in the leaflets.
-
-### Software used to administer the treatment
-
-The randomization was performed in R. The treatment administration was done in person.
+We also explained in lay terms what a median is and how we would measure their performance.
+
+## How and When Manipulations were Administered
+
+### Method of Delivery
+
+The manipulations were delivered in person by the chief headquarter RA. First, the manipulations was administered to all pairs simultaneously, then reinforced to each particular pair.
+
+### Software Used to Administer the Treatment
+
+We used `R` to perform the randomisation process. The treatment administration was done in person.
 
@@
 
-### Outcome measures
+### Outcome Measures
 
 There are two groups of outcomes.
-First, the performance outcomes that are collected from the cellphone used by each participant in the field.
-Second, the governmental data reported by the health care facilities in the municipality, with all dengue cases.
+First, the performance outcomes that we collected from the cellphone used by each participant in the field.
+Second, dengue incidence figures reported by the healthcare facilities in the municipality.
 
@@
 2. Pictures of exterminated breeding sites.
-3. Video of exterminated a. aegypti larvae.
-
-For governmental data, we have all the people infected by dengue fever that went to the hospital.
-There were no reported cases of Zika and Chikungunya, as the detection of these diseases are less standardized that Dengue.
-Moreover, the mayors office have no recollection of microcephaly incidence in the area during the period.
-
-The data then corresponds to all dengue cases, with address of the infected person, date of check-in to the hospital, and the severity of the case.
+3. Video of exterminated *A. aegypti* larvae.
+
+For governmental data, we have the total number of hospitalised individuals who were infected with dengue fever. There were no reported cases of Zika and Chikungunya.
 
@@
 
-We collected information on demographics.
-
-### Which outcomes and subgroup analysis were specified prior to the experiment?
-
-As the mayors office did not handed in the infections data prior to the intervention, we asked the neighborhoods that had higher dengue fever incidence prior to the intervention, and placed the territorial assignment in these places.
-However, due to absence of micro-level infectious disease data, we could not consider them prior to the intervention.
-
-### Exploratory analysis
-
-We run a pilot with 20 pairs before main intervention.
-We did not administered the incentivized intervention in the pilot to avoid contamination in the main results.
-The pilot helped us to update the expectations regarding the productivity in the field.
+We collected demographic information from participants.
+
+### Which Outcomes and Subgroup Analysis Were Specified Prior to the Experiment?
+
+The Rio Verde Mayor's Office did not hand in the infections data prior to the intervention.
+Therefore, we collected information on the neighbourhoods that had higher dengue fever incidence prior to the intervention, and implemented the territorial assignment accordingly.
+However, due to absence of micro-level data on infectious diseases, we did not consider them prior to the intervention.
+
+### Exploratory Analysis
+
+We run a pilot study with 20 pairs before the main intervention.
+We did not administer the incentivised intervention in the pilot study to avoid contamination in the results.
+The pilot study helped us update our expectations regarding the productivity in the field.
 Previously, we projected that we should assign around 20 houses per pairs.
-However, in the pilot we learned that pairs could visit from 40 to 60 houses per pair.
-In around one-thirty of them nobody answered the door, and in most of them the yards were too small to find any breeding sites.
-Moreover, most of the places with dengue in the previous week were visited by the municipal health care workers.
+However, in the pilot study we learned that pairs could visit from 40 to 60 houses per pair.
+In one-third of the households nobody answered the door, and in most of them the yards were too small to find any breeding sites.
+Moreover, most of the places with dengue in the previous week had been visited by the municipal health care workers.
 
@@
 
-### Number of subjects initially accessed for eligibility
+### Number of Subjects Initially Accessed for Eligibility
 
@@
 `sum(pretreat$training=='Training')` showed for the training session one day before the intervention.
-`r sum(pretreat$participating == 'Participating')` individuals showed to the intervention and remained until the end of it.
-
-### Exclusions prior to random assignment
-
-From all eligible people, we excluded the ones that missed the training and the field implementation session.
-This accounts for `r round(as.numeric(prop.table(table(pretreat$participating))[1]*100), 2)``\% of the total.
-
-### Subjects initially assigned to each experimental group
+`r sum(pretreat$participating == 'Participating')` individuals participated in the intervention and remained until the end of it.
+
+### Exclusions Prior to Random Assignment
+
+From all eligible people, we excluded the ones who missed the training and the field implementation sessions.
+This accounts for `r round(as.numeric(prop.table(table(pretreat$participating))[1]*100), 2)`\% of the total.
+
+### Subjects Initially Assigned to Each Experimental Group
 
@@
 
-### Proportion received x not received intervention
+### Proportion Received x Not Received Intervention
 
@@
 
-### Why did not receive intervention?
-
-The individuals did not received the intervention if they missed the field. They were then excluded from the data.
-
-### Number subjects each group dropped experiment
-
-No subject were dropped from the assignment. The attrition was caused by the fact that there were individuals that did not show up for the training and the treatment.
-
-## Statistical analysis
-
-### Describe statistical analysis
+### Why Did Subjects Not Receive Intervention?
+
+The individuals did not receive the intervention if they missed the fieldwork date. They were excluded from the data.
+
+### Number Subjects Each Group Dropped Experiment
+
+No subject were dropped from the assignment. The attrition was caused only by the fact that some individuals did not show up for the training and the treatment.
+
+## Statistical Analysis
+
+### Describe Statistical Analysis
 
@@
 
-1. Balance tests
-2. Performance outcome analysis
-3. Disease incidence analysis
-4. Differences-in-differences analysis
+1. Balance tests.
+2. Performance outcome analysis.
+3. Disease incidence analysis.
+4. Differences-in-differences analysis.
 
@@
 
-And our quantity of interest is $\beta$. The codes for the regression models we run are as follows:
+And our quantity of interest is $\beta$. The code for the regression models we run are as follows:
 
@@
 
-These regressions uses the package \texttt{lfe}, as it facilitates the use of cluster-robust standard errors.
-
-## Standard errors
-
-The robust standard errors are computed using \texttt{vcovHC} function in the package \texttt{sandwich}. The standard error is the same as the Stata's \textit{comma-robust}.
+We use the \texttt{lfe} package to estimate the models, as it facilitates the use of cluster-robust standard errors.
+
+## Standard Errors
+
+We calculated robust standard errors using the \texttt{vcovHC} function in the package \texttt{sandwich}. The standard error is the same as the Stata's \textit{comma-robust}.
 
@@
 
-The attrition reports have been analyzed in the data analysis section of this appendix.
-
-## Other information
+The attrition reports have been analysed in the data analysis section of this appendix.
+
+## Other Information
 
@@
 
-### Pre-registration
-
-The study was pre-registered using the EGAP pre-registry tool, by the number 20180504AA.
+### Pre-Registration
+
+The study was pre-registered using the EGAP pre-registry tool (#20180504AA).
 
@@
 
-The study was funded by the FGV applied research grant office (RPCAP-FGV). They did not interfere in the study design nor the results.
-
-### Replication dataset
-
-The replication materials is in the following website: (https://github.com/danilofreire/incentives-health-care).
-
-### Thanks
+We received funding from the FGV Applied Research Grant Office (RPCAP-FGV). The funding body did not interfere in the study design or implementation.
+
+### Replication Dataset
+
+Replication materials are available at https://github.com/danilofreire/incentives-health-care.
+
+### Acknowledgements
 
@@
 
-- Guilherme Fasolin
-- Giovanna França
-- Phillipe Guedon
-- Natalia Liberato
-- Fatima Portella
-- Catarina Roman
-- Leticia Santana
-- Larissa Santos
-- Vitor Sion
-
-We are very thankful for all their help before, during, and after the field.
+- Guilherme Fasolin, Giovanna França, Phillipe Guedon, Natalia Liberato, Fatima Portella, Catarina Roman, Leticia Santana, Larissa Santos, and Vitor Sion.
+
+We are very thankful for their help before, during, and after the field experiment.
 

### 2021-02-22 manuscript/article.Rmd

--- 2021-02-22 manuscript/article.Rmd
@@
 title:  |
-        | Financial Incentives and Health Care Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
+        | Financial Incentives and Healthcare Provision: Evidence from an Experimental *Aedes aegypti* Control Programme in Brazil
 author:
@@
 thanks: "We thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
-Special thanks to XXXX for their excellent research assistance.
 Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
@@
 
-\noindent \textbf{Background}. Mosquito control strategies are the primary
-means to reduce \textit{Aedes aegypti} infections worldwide. However,
-insecticide spraying is conducted inconsistently across the developing world.
-Recent studies indicate that financial incentives may increase the productivity
-of health personnel, yet there is little evidence on the impact of monetary
-rewards on \textit{A. aegypti}-reduction programmes. We evaluated whether
-individual and collective financial incentives improves the performance of
-healthcare workers fighting \textit{A. aegypti}, as well as their effect on
-city-level numbers of dengue hospitalisations.
+\noindent \textbf{Background}. Mosquito control is the most effective means of
+reducing \textit{Aedes aegypti} infections worldwide. In many developing
+countries, however, vector management programmes fail to reach their goals due
+to low worker productivity. Research suggests that financial incentives may
+increase the productivity of health personnel, yet there is little evidence
+about the impact of monetary rewards on \textit{A. aegypti}-reduction
+strategies. We evaluated whether individual and collective financial incentives
+improve the performance of healthcare workers fighting \textit{A. aegypti}, as
+well as their effect on city-level numbers of dengue hospitalisations.
 
 \noindent \textbf{Methodology/Principal findings}. We hired and trained
-subjects to visit households, find \textit{A. aegypti} breeding sites, and kill
-mosquito larvae in the city of Rio Verde, Brazil. In our randomised field
-trial, we provided individual and team bonuses to two treatment groups, while
-the control group received a flat compensation for completing their tasks.
-Financial bonuses increased the number of cleaned breeding sites in both
-treatment groups (individual and team bonuses) and the collective treatment
-also improved larvae extermination. The intervention lowered dengue
-hospitalisations in 10.3\%, but the result was not consistent across all model
-specifications.
+subjects to visit households, find \textit{A. aegypti} breeding sites, and
+eliminate mosquito larvae in the city of Rio Verde, Brazil. We randomly
+assigned workers into three groups. The control group received a flat
+compensation for their tasks, while workers in the two treatment groups received
+individual and collective monetary bonuses, respectively. Financial rewards
+increased the number of cleaned breeding sites in both treatment groups
+(individual and team bonuses) and the collective treatment also improved larvae
+extermination. The intervention lowered dengue hospitalisations in 10.3\%, but
+the result was not consistent across all model specifications.
 
@@
 \noindent Diseases transmitted by the \textit{Aedes aegypti} mosquito, such as
-chikungunya, dengue, yellow fever, and Zika, continue to kill thousands of
-people per year. As there are no safe vaccines for many of these infections,
-insecticide spraying and breeding site cleaning are the best means to fight the
-mosquito. In several developing countries, which host the majority of
+chikungunya, dengue, yellow fever, and Zika, continue to affect thousands of
+people per year. As there are no safe vaccines for most of these infections,
+insecticide spraying and breeding site elimination are the best means to fight
+the mosquito. In several developing countries, which host the majority of
 \textit{A. aegypti} infections, anti-mosquito campaigns are carried out
@@
 experiment that provided individual and collective financial incentives to
-healthcare agents in a Brazilian city and tested the effect of monetary rewards
-on their productivity and on the number of dengue hospitalisations. We find
-that financial bonuses improved the number of cleaned breeding sites in both
-treatment groups (individual and team incentives) and that the collective
+healthcare agents in a Brazilian city, and we tested the effect of monetary
+rewards on their productivity and on city-level dengue hospitalisations. We
+find that financial bonuses improved the number of cleaned breeding sites in
+both treatment groups (individual and team incentives) and that the collective
 treatment also improved larvae extermination. The impact of our treatment on
@@
 sum, financial incentives may be used to boost field productivity in
-anti-\textit{A. aegypti} programmes, but we suggest that further research is
-required to evaluate how healthcare worker productivy impacts city-level
-disease outcomes.
+anti-\textit{A. aegypti} programmes, but further research is required to
+evaluate how healthcare worker productivy impacts dengue outcomes.
 
 \vspace{.3cm} 
-\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial incentives, mosquito control, preventive health care, randomised field experiment, worker productivity
+\noindent \textbf{Keywords}: Aedes aegypti, dengue, financial
+incentives, mosquito control, preventive healthcare, randomised field
+experiment, worker productivity 
 \end{abstract}
@@
 \newpage
+
 # Introduction
@@
 The *Aedes aegypti* mosquito is the major worldwide vector of several arboviral
-diseases, including dengue, yellow fever, Zika, and chikungunya
+diseases, including chikungunya, dengue, yellow fever, and Zika
 [@burt2012chikungunya; @jansen2010dengue; @leta2018global;
-@thangamani2016vertical]. Over the past 30 years, arboviral incidence has
+@thangamani2016vertical]. Over the last decades, arboviral incidence has
 increased exponentially, with estimates suggesting that dengue is endemic in
-around 100 countries and causes 400 million infections and 22 thousands deaths
+over 100 countries and causes 400 million infections and 22 thousand deaths
 each year [@bhatt2013global; @cdc2020dengue]. Since there are no safe vaccines
@@
 [@beatty2010best; @eisen2009proactive]. The World Health Organization
-recommends the elimination of containers and the use of insecticide to reduce
+recommends the cleaning of containers and the use of insecticide to reduce
 vector breeding, specially in settings where human-vector contacts are
 frequent, such as schools, hospitals, and workplaces [@WHO2012global;
-@world2020denguecontrol]. However, breeding site cleaning and insecticide
-spraying are labour-intensive processes, and they are often carried out
-inconsistently in developing countries [@paz2015dengue; @siddiqui2016use;
-@WHO2012global]. In this regard, improving the performance of those responsible
-for mosquito control is essential to the effectiveness of anti-*Aedes*
-programmes.
+@world2020denguecontrol]. However, breeding site elimination and insecticide
+spraying are labour-intensive processes, which are often carried out
+inconsistently by developing states [@paz2015dengue; @siddiqui2016use;
+@WHO2012global]. In this regard, improving their health agency's performance in
+mosquito control is essential to the effectiveness of anti-*Aedes* programmes.
 
 Research shows that financial incentives may increase the productivity of
-health care workers [@clemens2014physicians; @muthmainnah2017improving;
-@ulrich2005does]. Nevertheless, systematic reviews indicate that the
-generalisability of the available evidence is limited due to methodological
+healthcare workers [@clemens2014physicians; @muthmainnah2017improving;
+@ulrich2005does]. Nevertheless, systematic reviews indicate that the internal
+validity of the available evidence is limited due to methodological
 shortcomings, as several studies suffer from selection bias and inadequate
 experimental blinding [@bassani2013financial; @flodgren2011overview;
-@scott2011effect]. Moreover, it remains unclear which rewarding schemes have a
-stronger effect on health care worker performance [@fainman2020design], and
-whether monetary incentives have a sustained effect on patient outcomes
-[@jha2012long; @langdown2014use].
+@scott2011effect]. The reviews also point out that it remains unclear which
+rewarding schemes have a stronger impact on healthcare worker performance
+[@fainman2020design] and whether monetary incentives have any sustained effects
+on patient outcomes [@jha2012long; @langdown2014use].
 
 In this paper, we explore how financial incentives affect the productivity of
-health care personnel involved in *A. aegypti* control and how they impact
-dengue hospitalisations. We run a randomised field experiment in the city of
-Rio Verde, Brazil, which has experienced a peak in dengue infections in the
-last years. We hired and trained teams of health care workers to perform
-simplified procedures designed to exterminate *A. aegypti* breeding sites. Our
-experiment consisted of two treatment arms plus a control condition. We offered
-individual or collective bonuses to those allocated in the two treatment
-groups, while the control group received a fixed compensation for completing
-their tasks. We then measured how the different reward schemes affect the
-number of breeding sites discovered, larvae exterminated, and city-level dengue
-incidence.
+healthcare personnel involved in *A. aegypti* control and how they impact
+dengue hospitalisations. We ran a randomised field experiment in the city of
+Rio Verde, Brazil, which has experienced a peak in dengue infections in recent
+years. We hired and trained teams of healthcare workers to perform simplified
+procedures designed to exterminate *A. aegypti* breeding sites. Our experiment
+consisted of two treatment arms plus a control condition. We offered individual
+or collective bonuses to those allocated in the two treatment groups, while the
+control group received a fixed compensation for completing their tasks. We then
+measured how the different reward schemes affected the number of breeding sites
+discovered, larvae exterminated, and city-level numbers of dengue incidence.
 
@@
 Brazilian Midwestern state of Goiás. In 2017, Rio Verde had 229,000 inhabitants
-and 1,156 confirmed dengue cases, one of highest counts in Goiás
+and 1,156 confirmed dengue cases, one of highest counts in the state
 [@goias2020]. We used Facebook advertisements to recruit potential
@@
 
-Table \ref{tab:covbal} displays the attrition and covariate balance tests for
-our experiment, and the territorial assignment before and after applying
-propensity score matching [@rosenbaum1985constructing] on census tract
-characteristics. We observe no significant differences regarding attrition
-rates, indicating that the treatment was correctly randomised. Participant 
-demographics are also similar across all groups, thus the matching technique
-successfully balanced the territorial assignment.
+Table \ref{tab:covbal} displays the attrition rates and the covariance balance
+tests for our experiment. The last two tables report the values for our
+territorial assignment before and after applying propensity score matching
+[@rosenbaum1985constructing] on census tract characteristics. We observe no
+significant differences regarding attrition rates, indicating that the
+treatment was correctly randomised. Participant demographics are also similar
+across all groups, what suggests that the matching technique successfully
+balanced the territorial assignment.
 
@@
                  sum), digits = 0)
-tabcov <- rbind(tabcov, tab)
 row.names(tabcov) <- NULL
@@
 x = x$x
-x
 y = summary(aov(NHouses~D1, data = dfr2, weights=dfr2$weightsD1))
@@
 subjects into three groups and directed each group to separate headquarters to
-avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`), we told participants that
-they would receive a flat payment regardless of their performance (BRL 110 /
-USD 25 per subject). In the individual treatment group (n = `r as.numeric(table(prodfr$D)[2])`), we informed
-subjects that we would rank each subject separately and double the compensation
-for those who performed above the sample median (BRL 220 / USD 50 per subject).
-In the collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we explained that we would rank
-the performance of each group and double the payment for those teams whose
-results were higher than the sample median (BRL 220 / USD 50 per subject).
-Participants worked in pairs and were aware of other groups, but they did not
-know about the different treatment conditions. The teams received a leaflet
-with a map of the area they should cover. Each route included around 120 houses
-in two or three blocks.
+avoid spillovers. In the control group (n = `r as.numeric(table(prodfr$D)[1])`),
+we told participants that they would receive a flat payment regardless of their
+performance (BRL 110 / USD 25 per subject). In the individual treatment group
+(n = `r as.numeric(table(prodfr$D)[2])`), we informed participants that we would
+rank each one of them separately and double the compensation for those who
+performed above the sample median (BRL 220 / USD 50 per subject). In the
+collective treatment group (n = `r as.numeric(table(prodfr$D)[3])`), we
+explained that we would rank the performance of each group and double the
+payment for those teams whose results were higher than the sample median (BRL
+220 / USD 50 per subject). Participants worked in pairs and were aware of other
+groups, but they did not know about the different treatment conditions. The
+teams received a leaflet with a map of the area they should cover. Each route
+included around 120 houses in two or three blocks.
 
@@
 This study evaluates two outcomes. The first outcome is the field productivity
-of health care providers. We measure worker productivity by coding cellphone
+of healthcare providers. We measure worker productivity by coding cellphone
 data collected during the intervention into four indicators: 1) the number of
-houses visited; 2) the number of houses visited within less than two minutes;
-3) the number of breeding sites removed and cleaned; 4) the number of
-exterminated larvae. We analyse the data using ordinary least squares with
-robust standard errors [@imbens2016robust]. We estimate the statistical
-power of the study assuming a treatment effect of 0.15 standard deviations.
+breeding sites removed and cleaned; 2) the number of exterminated larvae; 3)
+the number of houses visited; 4) the number of houses visited within less than
+two minutes. We analyse the data using ordinary least squares with robust
+standard errors [@imbens2016robust]. We estimate the statistical power of the
+study assuming a treatment effect of 0.15 standard deviations.
 
@@
 Verde measured 4, 8, 12, and 16 days after the intervention. The Rio Verde
-Mayor's Office provided us with its annual health care report, which contains
+Mayor's Office provided us with its annual healthcare report, which contains
 the dates and personal information of patients who had dengue fever and
@@
 funders of this study had no influence over the formulation, organisation,
-analysis, and interpretation of the outcomes. Health care workers gave written
+analysis, and interpretation of the outcomes. Healthcare workers gave written
 consent upon filling the Qualtrics questionnaire. During the intervention, the
@@
 We find that financial incentives significantly increase the field productivity
-of health care workers fighting *Aedes aegypti*. Subjects in both the
+of healthcare workers fighting *Aedes aegypti*. Subjects in both the
 individual and the collective bonus groups locate more mosquito breeding sites
@@
 
-We have four indicators to measure health worker productivity. The first is the
-number of houses visited during the intervention. The second indicator is the
-number of houses in which the visits lasted for less than two minutes. The
-third dependent variable is the number of *A. aegypti* breeding sites removed
-and cleaned. Our fourth variable indicates the number of mosquito larvae
-exterminated. Table \ref{tab:productivity} summarises the experimental results.
+Table \ref{tab:productivity} summarises the experimental results. 
+Subjects who receive monetary incentives find and clean more breeding sites
+than those who earned a flat compensation fee. Workers in the individual
+treatment group find `r round(as.numeric(coef(mprod[[3]])[2]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) more breeding sites than the
+non-incentivised control group. The effect for those in the collective bonus
+group is `r round(as.numeric(coef(mprod[[3]])[3]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,2]`]), slightly smaller than for the individual treatment.
+This finding suggests that the treatment does improve the performance of healthcare workers.
 
@@
 mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
-stargazer(mprod[[1]], mprod[[2]],
-          mprod[[3]], mprod[[4]],
-          se = starprep(mprod[[1]], mprod[[2]],
-                        mprod[[3]], mprod[[4]],
+stargazer(mprod[[3]], mprod[[4]],
+          mprod[[1]], mprod[[2]],
+          se = starprep(mprod[[3]], mprod[[4]],
+                        mprod[[1]], mprod[[2]],
                         se_type = "HC1"),
-          dep.var.labels = c('\\shortstack{Houses \\\\ Visited}', 
-                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}',
-                             '\\shortstack{Breeding Sites \\\\ Terminated}',
-                             '\\shortstack{Larvae \\\\ Terminated}'),
+          dep.var.labels = c('\\shortstack{Breeding Sites \\\\ Terminated}',
+                             '\\shortstack{Larvae \\\\ Terminated}',
+                             '\\shortstack{Houses \\\\ Visited}',
+                             '\\shortstack{Houses Visited \\\\ in Less than \\\\ Two Minutes}'),
           keep.stat = c('ser', 'n'),
-          notes = c('Robust Standard Errors in parenthesis.'),
+          notes = c('Robust standard errors in parenthesis.'),
           keep = c('DIndividual', 'DCollective'),
@@
 
-Subjects who received monetary incentives, either alone or in pairs, visited
-fewer houses than those who did not earn financial rewards. While the result
-seems counter-intuitive, it actually attests the effectiveness of the
-treatment. This is because we offered incentives for subjects to exterminate
-larvae and find breeding sites, not to visit a greater number of households. As
-a result, participants in the two treatment groups did a thorough job in each
-household, which explains the lower number of visits during the allotted time.
-We find that subjects in the individual and in the collective bonus groups
-visited `r round(as.numeric(coef(mprod[[1]])[2]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) and `r round(as.numeric(coef(mprod[[1]])[3]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,2]`]) households,
-respectively.
+\newpage
 
-Our second indicator provides further evidence in favour of our argument. We
-see that the two groups which earned performance bonuses spent more time in the
-households, as their number of houses visited for less than two minutes is
-significantly lower than those of the control condition. On average,
-participants in the individual bonus treatment arm visited `r round(as.numeric(coef(mprod[[2]])[2]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,1]`,
-`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) houses than the control, and those in the collective bonus group visited
-`r round(as.numeric(coef(mprod[[2]])[3]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,2]`]).
-
-Incentivised teams find and clean more breeding sites than non-incentivised
-ones.
-Individually incentivised health workers find `r round(as.numeric(coef(mprod[[3]])[2]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[2,2]`])
-more breeding sites than the non-incentivised control group. The effect for
-those in the collective bonus group is `r round(as.numeric(coef(mprod[[3]])[3]), 3)` (CI: [`r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[3]], vcov = vcovHC(mprod[[3]], type = "HC1"), level = 0.9), digits=3)[3,2]`]), slightly
-smaller than for the individual treatment.
-
-Teams which received collective bonuses are the most effective in finding
+Teams who received collective bonuses are the most effective in finding
 larvae.
@@
 task increases when subjects work in teams. Furthermore, our collective bonus
-scheme was not excludable within the teams, thus health care workers had an
+scheme was not excludable within the teams, thus healthcare workers had an
 incentive to cooperate and receive higher rewards.
+
+Subjects who received monetary incentives visited fewer houses than those who
+did not earn financial rewards. The result is statistically significant for the
+individual treatment group. While the finding seems counter-intuitive, it
+actually attests the effectiveness of the treatment. This is because we offered
+incentives for subjects to exterminate larvae and find breeding sites, not to
+visit a greater number of households. As a result, participants in the 
+treatment groups did a thorough job in each household, which explains the lower
+number of visits during the allotted time. We find that subjects in the
+individual and in the collective bonus groups visited `r round(as.numeric(coef(mprod[[1]])[2]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) and `r round(as.numeric(coef(mprod[[1]])[3]), 3)` (CI: [`r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[1]], vcov = vcovHC(mprod[[1]], type = "HC1"), level = 0.9), digits=3)[3,2]`]) households, respectively.
+
+Our last indicator, the number of houses visited within less than two minutes, provides further evidence in favour of our argument. On average,
+participants in the individual bonus treatment arm visited `r round(as.numeric(coef(mprod[[2]])[2]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,1]`,
+`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[2,2]`]) houses than the control, and those in the collective bonus group visited
+`r round(as.numeric(coef(mprod[[2]])[3]), 3)` (CI: [`r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,1]`, `r round(coefci(mprod[[2]], vcov = vcovHC(mprod[[2]], type = "HC1"), level = 0.9), digits=3)[3,2]`]).
+Again, the result for the individual bonus group is statistically significant at the 10% level.
 
@@
 We employ two models to evaluate the effect of monetary incentives on dengue
-incidence. The first is a differences-in-differences model that tests
+incidence. The first is a differences-in-differences estimation that tests
 whether the intervention _per se_ had any effect on dengue hospitalisations in
@@
 
-```{r, echo=FALSE, results='asis'}
+```{r, echo=FALSE, results='asis', cache=T}
 ## Health outcome
@@
 counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
-days after the treatment.\footnote{The 96 pairs analysed 139 Census Tracts. This because 43 pairs worked in more than one Census tract at once.}
+days after the treatment.\footnote{The 96 pairs analysed 139 census tracts.
+This is because 43 pairs worked in more than one census tract at once.}
 
-Compared to the control group, neither treatment had an impact on disease
-incidence in the Rio Verde census tracts. The treatment effect is not
-statistically different from zero in any model specification. Yet, the
-coefficients are negative, what indicates that should an impact have occurred,
-the intervention would have lowered dengue incidence in the treated areas.
+We see that neither treatment has an impact on disease incidence in the Rio
+Verde census tracts. The treatment effect is not statistically different from
+zero in any model specification. Yet, the coefficients are negative, which
+indicates that had an impact occurred, the intervention would have lowered
+dengue incidence in the treated areas.
 
@@
 
-Our conclusions are consistent with the results of comparable studies conducted
-in other settings, such as education [@duflo2012incentives] and private firms
-[@bandiera2013team]. They also provide further evidence that incentivising team
-work is more effective for labour-intensive tasks, which opens a new avenue for
-research in preventive health care.
+Our conclusions are consistent with results from comparable studies conducted
+in other settings, such as in education [@duflo2012incentives] and in private
+firms [@bandiera2013team]. The findings also lend further evidence that
+incentivising teams is particularly effective when they carry out
+labour-intensive tasks, which opens a new avenue for research in preventive
+healthcare.
 
@@
 mixed results. Why did the treatment not work as we planned? We believe the
-treatment was not strong enough. Our treatment probably did not cover enough
-areas to ensure there was no mosquitos around the assigned blocks. As mosquitos
-can travel for long distances, the treatment might not have been sufficient.
-Also, Rio Verde had significant rates of dengue incidence during our
-experiment, reaching 3,411 reported infections from January to September 2018
-[@goias2020]. Therefore, maybe the treatment works only when applied for
-longer periods of time or in more neighbourhoods.
+treatment was not as strong as it needed to be. Our treatment probably did not
+cover enough areas to ensure there was no mosquitos around the assigned blocks.
+As mosquitos can travel for long distances, the treatment might not have been
+sufficient. Also, Rio Verde had significant rates of dengue incidence during
+our experiment, reaching 3,411 reported infections from January to September
+2018 [@goias2020]. Therefore, the treatment might have stronger effects only
+when applied for longer periods of time or in more neighbourhoods.
 
-In this respect, our study suggests is that even though health care workers may
+In this respect, our study suggests is that even though healthcare workers may
 be motivated, their efforts do not necessarily lead to a reduction in mosquito
 infections. Higher field productivity does not guarantee that the *Aedes
-aegypti* can be eradicated. To our knowledge, we are one of the first studies
-to highlight this issue. Future research may explore the reasons why this is
-the case and if the disconnect between the two can also be identified in other
-areas.
+aegypti* mosquito can be eradicated. To our knowledge, this issue has received
+little attention in the literature. Future research may explore the reasons why
+this is the case and if the disconnect between the two can also be identified
+in other areas.
 
@@
 period of time and in a particular Brazilian city, thus the findings may not
-generalise to other locations. Second, our experiment needed a longer and wider
-coverage to measure whether the treatment has a significant impact on dengue
-incidence, as the effect seems smaller than expected. Third, we included a
+generalise to other locations. Second, our experiment needs a broader coverage
+to measure whether the treatment has a significant impact on dengue incidence,
+as the effect size is smaller than we expected. Third, we included a
 post-treatment adjustment to ensure the balance of our territorial variables.
-Although using matching estimators to improve balance is in line with the best
-statistical practices, it requires additional assumptions. Finally, the
-experiment only measures the impact of financial rewards on worker performance,
-and it does not assess the effect of non-monetary incentives, such as
-motivational messages or constant feedback, which may be useful alternatives in
+Although using matching estimators to improve balance is good statistical
+practice, the method requires additional assumptions. Finally, the experiment
+only measures the impact of financial rewards on worker performance, and it
+does not assess the effect of non-monetary incentives, such as motivational
+messages or constant feedback, which may be useful alternatives in
 jurisdictions where legal or financial constraints prevent the government from
@@
 
-The experiment has important lessons for policy-making. *Aedes aegypti*-borne
+The experiment has important lessons for policy-making. *A. aegypti*-borne
 diseases are a significant public health concern, especially in developing
@@
 in motivating civil servants, and that peer incentives are more cost-effective
-than individual bonuses. Finally, the article shows anti-mosquito campaigns
-require a sustained effort to guarantee their success, and we still have no
-robust evidence that worker productivity alone is sufficient to reduce dengue
-infections.
+than individual bonuses. Finally, the article shows that anti-mosquito
+campaigns require a sustained effort to guarantee their success, and we still
+have no robust evidence that worker productivity alone is sufficient to reduce
+dengue infections.
 

### 2021-02-23 appendix/appendix.Rmd
small edits to appendix

@@
 papersize: a4paper
-bibliography: references.bib
+bibliography: "../manuscript/references.bib"
 biblio-style: apalike
@@
 
-Consider the following interaction between healthcare workers and a government agency.\footnote{This model was inspired by @bolton2005contract and @itoh1991incentives.
+Consider the following interaction between healthcare workers and a government agency.\footnote{This model was inspired by \citet{bolton2005contract} and \citet{itoh1991incentives}.
 Here we present a particular case of their model to illustrate the effects of our treatment.} The agency hires the workers to provide preventive healthcare.
@@
 \includegraphics[width=1\textwidth]{../figures/figrev.pdf}
-\caption{Governmental Agency's Revenue in terms of Contract and Compensation}
+\caption{Governmental Agency's Revenue in Terms of Contract and Compensation}
 \label{figrevmax}
@@
 In this case, the compensation to stimulate cooperation has to be significantly higher, and even in this case there will be incentives for not cooperating.}
-
-\pagebreak
 
@@
 
-1. There is a 10.3\% effect on the full data model.
+1. There is a 10.3% effect on the full data model.
 2. The coefficient for the other windows are not significant but the signs are consistent with lower disease incidence.
-
-\pagebreak
 
@@
 \includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
-\caption{Example Working Area.\label{appcevwbl}}
+\caption{Example Working Area.\label{appcevwa}}
 \end{figure}

### 2021-02-23 appendix/appendix.Rmd
small edits to appendix, gitignore

@@
 \centering
-\includegraphics[width=0.8\textwidth]{../figures/rvWorkBlock.png}
+\includegraphics[width=0.8\textwidth, height=13cm]{../figures/rvWorkBlock.png}
 \caption{Example Leaflet.\label{appcevwbl}}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
+\includegraphics[width=0.8\textwidth, height=11cm]{../figures/rvWorkArea.png}
 \caption{Example Working Area.\label{appcevwa}}
@@
 \centering
-\includegraphics[width=0.8\textwidth]{../figures/rvKit3.jpeg}
+\includegraphics[width=0.8\textwidth, height=9cm]{../figures/rvKit3.jpeg}
 \caption{Teams Uniforms\label{appcteamunif}}
@@
 \centering
-\includegraphics[width=0.4\textwidth]{../figures/rvApp.jpeg}
+\includegraphics[width=0.4\textwidth, height=6cm]{../figures/rvApp.jpeg}
 \caption{Cellphone with Data Collection App.\label{appccpdcit}}
@@
 \begin{figure}
-\includegraphics[width=0.8\textwidth]{../figures/rvKit4.jpg}
-\includegraphics[width=0.8\textwidth]{../figures/rvKit5.jpg}
+\includegraphics[width=0.8\textwidth, height=7cm]{../figures/rvKit4.jpg}
+\includegraphics[width=0.8\textwidth, height=7cm]{../figures/rvKit5.jpg}
 \caption{Example Leaflet Handed to Households.\label{appcexhhleafl}}
@@
 
-## Some field pictures
+## Some Field Pictures
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{../figures/rvFieldPic1.png}
+\includegraphics[width=0.7\textwidth, height=12cm]{../figures/rvFieldPic1.png}
 \caption{Field pictures}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{../figures/rvFieldPic2.jpg}
+\includegraphics[width=0.7\textwidth, height=10cm]{../figures/rvFieldPic2.jpg}
 \caption{Field pictures}
@@
 
+\footnotesize
 ```{r}
@@
 ```
+\normalsize

### 2021-02-23 appendix/appendix.Rmd
small edits to appendix and manuscript

@@
 Team structures also help in terms of lowering free-riding and increasing incentives for cooperative work.
-To capture this, we assume that a given worker $i$ divides her work effort into two tasks: those which she accomplishes with her own effort ($e_i$) and helping efforts ($h_i$).
+To capture this, we assume that a given worker $i$ divides her work effort into two tasks: her own effort ($e_i$) and helping efforts ($h_i$).
 To capture the costs of effort, we assume the following convex cost function $\dfrac{c}{2}(e_i^2 + h_i^2)$, where $c>0$ represents the changes in marginal costs of effort and help.
@@
 
-## Baseline: No Incentive Bonuses
+## Baseline: No Bonus
 
@@
 This is the worst-case scenario in terms of the agency's welfare.
-In the experiment, it matches the control condition.\footnote{Throughout the chapter, we assume that the optimal output for the agency is equal to the maximum welfare for society.
+In the experiment, it matches the control condition.\footnote{Throughout the article, we assume that the optimal output for the agency is equal to the maximum welfare for society.
 Although this is not always the case, it is a reasonable simplification for the purposes of this article.
@@
 
-We have five data sources in this study, all of them are included in `./data/incentives_healthcare.RData`:
+We use five data sources in this study. All of them are included in `../data/incentives_healthcare.RData`:
 
@@
 - `dfr2`: Disease incidence in every Rio Verde census sector that received the intervention.
-- `did_full`: Differences-in-differences estimator that measures the effect of our intervention against a pure control group.
+- `did_full`: Differences-in-differences estimation that measures the effect of our intervention against a pure control group.
 
@@
 
-The pre-treatment balance dataset contains information about every individuals who interacted with the experimental team at any point of time.
-To be included in this dataset, the person has to have filled the recruitment form we had circulated on Facebook as part of our campaign.
-The dataset contains 13 variables that we collected before the intervention.
+The pre-treatment balance dataset contains information about every individual who interacted with the research team at any point of time.
+To be included in this dataset, the person needs to have filled the Google Form we circulated on Facebook as part of our recruitment campaign.
+This dataset contains 13 variables that we collected before the intervention.
 We gathered these data either via Google Forms, or in pre-treatment surveys before the training session.
@@
 
-We collected field productivity data based on the subjects' performance during the experiment. We measured productivity using three indicators:
+We collected field productivity data based on the subjects' performance during the experiment. We measured productivity with three indicators:
 
@@
 
-We compiled these data using pictures taken in the field.
+We compiled these data using photos taken during the field experiment.
 All participants were instructed to take pictures of clean breeding sites, and to make videos showing the larvae they exterminated.
@@
 5. `nLarvae`: Number of larvae exterminated.
-6. `nHouseVisit`: Number of houses that were indeed visited (based on having pictures of breeding sites and larvae videos).
+6. `nHouseVisit`: Number of houses that were indeed visited (based on pictures of breeding sites and larvae videos).
 7. `nHouseLessTwoMin`: Number of houses visited in less than two minutes (which denotes either that the pair did not go to the place, or that there were no residents at home).
@@
 
-To assess whether the intervention had an impact on the municipal healthcare system, we collected thirteen variables in two distinct datasets.
+To assess whether the intervention had an impact on the municipal healthcare system, we collected 13 variables in two distinct datasets.
 All datasets compile data from the National Health Notification System (SINAN) for the Rio Verde municipality.
@@
 6. `D1`: Treatment assignment.
-7. `D2`: Intervention x no intervention (no Intervention empty in `dfr2`).
+7. `D2`: Intervention x no intervention (no intervention missing in `dfr2`).
 8. `nc15dafter`: Number of cases 15 days after the intervention.
@@
 
-We build `did_full` dataset to investigate whether the intervention had any impact on public health outcomes.
-The disease incidence data describes the treatment effect.
+We build the `did_full` dataset to investigate whether our intervention had any impact on public health outcomes.
+The disease incidence data describe the treatment effect.
 In the differences-in-differences models, we combine all treatments and investigate how they perform against a pure control group, which are the census sectors that were not visited during the intervention.
@@
 We measure covariate balance using four statistics.
-First, we check whether subjects decided to join us for the training day.
-Second, we assess their decision to participate in the experiment.
-Subjects had to take part in the training process and then participate in the fieldwork.
-Third, we checked if individual characteristics are balanced across our treatment groups.
-We collected that information via Google Forms and using a pre-treatment survey.
-Finally, we checked the territorial assignment to make sure that the pre-treatment characteristics are balanced in the places that subjects visited.
-We find a good level of balance for the individual assignment (models 1 to 3), and we corrected eventual imbalances in the territorial assignment using propensity-score matching [@rosenbaum1985constructing].
+First, we check whether subjects decided to take part in the training sessions.
+Second, we evaluate the balance among those who decided to participate in the experiment.
+Subjects had to take part in the training process and participate in the fieldwork.
+Third, we check if individual characteristics are balanced across our treatment groups.
+As we mentioned above, we collected that information via Google Forms and using a pre-treatment survey.
+Finally, we check the territorial assignment to make sure that the pre-treatment characteristics are balanced across the places that subjects visited.
+We find good balance for the individual assignment (models 1 to 3), and we corrected eventual imbalances in the territorial assignment using propensity score matching [@rosenbaum1985constructing].
 
@@
 
-## How and When Manipulations were Administered
+## How and When Manipulations Were Administered
 
@@
 \centering
-\includegraphics[width=0.7\textwidth, height=10cm]{../figures/rvFieldPic2.jpg}
+\includegraphics[width=0.7\textwidth, height=13cm]{../figures/rvFieldPic2.jpg}
 \caption{Field pictures}
@@
 
-# R Session Information
+# Session Information
 

### 2021-02-23 manuscript/article.Rmd
small edits to appendix and manuscript

@@
 date: \today
-thanks: "We thank Livio DiLonardo, Saad Gulzar, Cathy Hafer, Carlo Holz, Dimitri Landa, Guisela Pereira, Adam Przeworski, Catarina Roman, David Skarbek, Denis Stukal, Marcos Tourinho, Scott Tyson, and participants at MPSA, NYU PE Seminar, and SPSA for their valuable comments.
-Replication materials are available at <http://github.com/danilofreire/incentives-health-care>."
+thanks: "We thank Saad Gulzar, Cathy Hafer, Dimitri Landa, Rebecca Morton, Adam Przeworski, Catarina Roman, Renard Sexton, David Skarbek, Denis Stukal, and participants at EGAP, MPSA, NYU PE Seminar, and SPSA for their valuable comments.
+We also thank the FGV Applied Research Centre for funding this research.
+Replication materials are available at <http://github.com/danilofreire/incentives-healthcare>."
 fontsize: 12pt
@@
 increased the number of cleaned breeding sites in both treatment groups
-(individual and team bonuses) and the collective treatment also improved larvae
+(individual and team bonuses), and the collective treatment also improved larvae
 extermination. The intervention lowered dengue hospitalisations in 10.3\%, but
@@
 \noindent \textbf{Conclusions/Significance}. \textit{A. aegypti} control
-programmes may benefit from alternative compensation schemes, specially when
+programmes may benefit from alternative compensation schemes, especially when
 provided to teams. For this strategy to succeed, financial incentives have to
@@
 anti-\textit{A. aegypti} programmes, but further research is required to
-evaluate how healthcare worker productivy impacts dengue outcomes.
+evaluate how healthcare worker productivity impacts dengue outcomes.
 
@@
 recommends the cleaning of containers and the use of insecticide to reduce
-vector breeding, specially in settings where human-vector contacts are
+vector breeding, especially in settings where human-vector contacts are
 frequent, such as schools, hospitals, and workplaces [@WHO2012global;
@@
 measured how the different reward schemes affected the number of breeding sites
-discovered, larvae exterminated, and city-level numbers of dengue incidence.
+discovered, larvae exterminated, and city-wide dengue incidence.
 
@@
 treatment was correctly randomised. Participant demographics are also similar
-across all groups, what suggests that the matching technique successfully
+across all groups, which suggests that the matching technique successfully
 balanced the territorial assignment.

### 2021-02-23 appendix/appendix.Rmd
version 0.1

@@
 
-Again, both players are *ex-ante* similar in terms of their expected utilities. This allow us to solve for the Symmetric Nash Equilibrium, where:
+Again, both players are *ex-ante* similar in terms of their expected utilities. This allows us to solve for the Symmetric Nash Equilibrium, where:
 
@@
 The ad invited potential participants to join the research and explained the payment scheme.
-If they clicked on the ad, they were directed to a Google Form, where they added their e-mail address and contact information.
+If they clicked on the ad, they were directed to a Google Form, where they added their email address and contact information.
 
@@
 Second, we collected governmental data on *A.
-aegypti*-borne diseases from the Brazilian Ministry of Health diseases notification system (SINAN).
+aegypti*-borne diseases from the National Health Notification System (SINAN).
 
@@
 
-### Method of Delivery
+### Delivery Methods
 
@@
 
-Replication materials are available at https://github.com/danilofreire/incentives-health-care.
+Replication materials are available at https://github.com/danilofreire/incentives-healthcare.
 

### 2021-02-23 manuscript/article.Rmd
copy editing

@@
 We also thank the FGV Applied Research Centre for funding this research.
+Each named author has equally contributed to conducting the underlying research and drafting this manuscript.
+To the best of our knowledge, the authors have no conflict of interest, financial or otherwise.
 Replication materials are available at <http://github.com/danilofreire/incentives-healthcare>."
@@
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
+```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=T}
 # If you need to install any package while knitting the document
@@
 \hline \\[-1.8ex]
-```{r, echo = FALSE, cache=TRUE, results='asis'}
+```{r, echo = FALSE, results='asis', cache=T}
 tabcov <- data.frame()
@@
 \hline \\[-1.8ex]
-```{r, echo = FALSE, cache=TRUE, results='asis'}
+```{r, echo = FALSE, results='asis', cache=T}
 ## Census Sectors characteristics
@@
 
+```{r, echo = FALSE, results='asis', warning=FALSE, cache=T}
+## Productivity outcome
+library(lmtest)
+mprod <- list()
+mprod[[1]] <- lm(nHouse ~ D, data = prodfr)
+mprod[[2]] <- lm(nHouseLessTwoMin ~ D, data = prodfr)
+mprod[[3]] <- lm(nBreed ~ D, data = prodfr)
+mprod[[4]] <- lm(nLarvae ~ D, data = prodfr)
+```
+
 Table \ref{tab:productivity} summarises the experimental results. 
@@
 
-```{r, echo = FALSE, results='asis', warning=FALSE}
+```{r, echo = FALSE, results='asis', warning=FALSE, cache=T}
 ## Productivity outcome
@@
 
-```{r, echo = FALSE, results='asis'}
+```{r, echo = FALSE, results='asis', cache=T}
 mod <- list()
@@
 counts before the intervention, and then 15, 30, 60, 90, and between 30 to 60
-days after the treatment.\footnote{The 96 pairs analysed 139 census tracts.
-This is because 43 pairs worked in more than one census tract at once.}
+days after the treatment. Note that 96 pairs of healthcare workers analysed 139
+census tracts. This is because 43 of those pairs worked in more than one census
+tract at once.
 

### 2021-02-24 manuscript/article.Rmd
small updates

@@
 date: \today
-thanks: "We thank Saad Gulzar, Cathy Hafer, Dimitri Landa, Rebecca Morton, Adam Przeworski, Catarina Roman, Renard Sexton, David Skarbek, Denis Stukal, and participants at EGAP, MPSA, NYU PE Seminar, and SPSA for their valuable comments.
+thanks: "We thank Taylor Boas, Saad Gulzar, Cathy Hafer, Daniel Hidalgo, Dimitri Landa, Rebecca Morton, Adam Przeworski, Catarina Roman, Renard Sexton, David Skarbek, Denis Stukal, and participants at EGAP, MPSA, NYU PE Seminar, and SPSA for their valuable comments.
 We also thank the FGV Applied Research Centre for funding this research.
@@
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=T}
+```{r, message=FALSE, warning=FALSE, echo=FALSE}
 # If you need to install any package while knitting the document
@@
 diseases, including chikungunya, dengue, yellow fever, and Zika
-[@burt2012chikungunya; @jansen2010dengue; @leta2018global;
+[@boas2019electoral; @burt2012chikungunya; @jansen2010dengue; @leta2018global;
 @thangamani2016vertical]. Over the last decades, arboviral incidence has

### 2021-02-24 manuscript/article.Rmd
fix typos

@@
 inconsistently by developing states [@paz2015dengue; @siddiqui2016use;
-@WHO2012global]. In this regard, improving their health agency's performance in
-mosquito control is essential to the effectiveness of anti-*Aedes* programmes.
+@WHO2012global]. In this regard, improving the performance of their healthcare
+agencies is essential to the effectiveness of anti-*Aedes* programmes.
 
@@
                         se_type = "HC1"),
-          dep.var.labels = c('\\shortstack{Breeding Sites \\\\ Terminated}',
-                             '\\shortstack{Larvae \\\\ Terminated}',
+          dep.var.labels = c('\\shortstack{Breeding Sites \\\\ Exterminated}',
+                             '\\shortstack{Larvae \\\\ Exterminated}',
                              '\\shortstack{Houses \\\\ Visited}',

### 2021-02-25 manuscript/article.Rmd
add ethics statement, small edits

@@
 
+## Ethics Statement
+
 We pre-registered the experiment on the Evidence in Governance and Policy
-(EGAP) website (<https://osf.io/6q8vu/>), and received IRB approval from New
-York University (IRB-FY2017-17) and Fundação Getulio Vargas (IRB-01/2017). The
-funders of this study had no influence over the formulation, organisation,
-analysis, and interpretation of the outcomes. Healthcare workers gave written
-consent upon filling the Qualtrics questionnaire. During the intervention, the
-occupants of households inspected for breeding sites and larvae gave oral
-consent. For more information on the experimental design, sample
-characteristics, exclusion criteria, and estimation methods, please refer to
-the Supplementary Material.
+(EGAP) website (#20180504AA, <https://osf.io/6q8vu/>), and received IRB
+approval from New York University (IRB-FY2017-17) and Fundação Getulio Vargas
+(IRB-01/2017). The funders of this study had no influence over the formulation,
+organisation, analysis, and interpretation of the outcomes. Healthcare workers
+gave written consent upon filling the pre-treatment questionnaire. During the
+intervention, the occupants of households inspected for breeding sites and
+larvae gave verbal consent. For more information about the experimental design, please refer to the Supplementary Material.
 
